### 2017-09-08 jfm_rapids/manuscript.tex
added jfm tex file to git

% This is file JFM2esam.tex
% first release v1.0, 20th October 1996
%       release v1.01, 29th October 1996
%       release v1.1, 25th June 1997
%       release v2.0, 27th July 2004
%       release v3.0, 16th July 2014
%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
% Copyright (C) 1996, 1997, 2014 Cambridge University Press

\documentclass{jfm}
\usepackage{graphicx}
\usepackage{epstopdf, epsfig}

% My own packages

\usepackage{ dsfont }
\usepackage{amsmath}

% User-defined commands

\newcommand{\ddt}[1]{\frac{d #1}{dt}}
%\newcommand{\hmone}[1]{\|#1\|_{H^{-1}}}
\newcommand{\hmone}[1]{\|\nabla^{-1} #1\|_{L^{2}}}
\newcommand{\ltwo}[1]{\|#1\|_{L^{2}}}
%\newcommand{\hone}[1]{\|#1\|_{H^{1}}}
\newcommand{\hone}[1]{\| \nabla #1\|_{L^{2}}}
\newcommand{\htwo}[1]{\|#1\|_{H^{2}}}
\newcommand{\sint}[1]{\int_{D} #1 \, d^{d}\mathbf{x}}
\newcommand{\tint}[1]{\int_{0}^{T} #1 \, dt}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\linf}[1]{\| #1 \|_{L^{\infty}}}
\newcommand{\tavg}[1]{\langle  #1 \rangle}
\renewcommand{\u}{\mathbf{u}}
%\newcommand{\ppt}[1]{\frac{\partial #1}{\partial t}}
\newcommand{\ppt}[1]{\partial_{t} #1}
\newcommand{\lap}{\Delta }
\newcommand{\invlap}{\Delta^{-1}}
%\newcommand{\lap}{\nabla^{2}}
%\newcommand{\invlap}{\nabla^{-2}}
\newcommand{\pbrac}[1]{\left( #1 \right)}
\newcommand{\sbrac}[1]{\left[ #1 \right]}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\shorttitle{Diffusion effects on optimal mixing and filamentation}
\shortauthor{C. J. Miles and C. R. Doering}

\title{Diffusion effects on optimal mixing and filamentation}

\author{Christopher J. Miles\aff{1,2,3}
  \corresp{\email{cmiless@umich.edu}}
 \and Charles R. Doering\aff{1,2,3}}

\affiliation{\aff{1}Department of Physics, University of Michigan,
Ann Arbor, MI 48104-1040, USA
\aff{2}Department of Mathematics, University of Michigan,
Ann Arbor, MI 48104-1043, USA
\aff{3}Center for the Study of Complex Systems, University of Michigan,
Ann Arbor, MI 48104-1107, USA}

\begin{document}

\maketitle

\begin{abstract}
In this work, we investigate the role of diffusion and its impact on our goals for optimal mixing. We show numerical evidence that diffusion can limit the length scales achievable by a generalized Batchelor length scale [\cite{Batchelor1959a}] for incompressible flows with uniformly bounded energy or rate-of-strain for optimal stirring protocols.  We also show that perfect mixing in finite time is impossible for such constraints by extending the work of \cite{Chi-Cheu1996}.
\end{abstract}

\begin{keywords}
\end{keywords}

\section{Introduction}

Optimal mixing is important to many areas of science and engineering. A question of interest across these domains is ``How can one stir to enhance the rate of mixing?'' We address this question by formulating the problem by considering complete control of an incompressible flow in a periodic domain with mild physical constraints. In particular, we consider a  domain $D=[0,L]^{d}$  where $L$ is the side length and $d$ is the total number of spatial dimensions. All functions defined on $D$ have periodic boundary conditions. Let $\theta(\mathbf{x},t): D \times [0,T] \rightarrow [-1,1]$ be the tracer concentration field that evolves according to the advection-diffusion equation,
\begin{equation}
	\label{eq:PDE_advection}
	\ppt{\theta}+\mathbf{u}\cdot \nabla \theta=\kappa \lap\theta
\end{equation}
where $\kappa$ is the molecular diffusion coefficient and $\mathbf{u}(\mathbf{x},t)$ is an incompressible ($\nabla\cdot \mathbf{u}=0$) velocity field constrained by bounded energy
\begin{equation}
	\label{eq:PDE_energy}
	\linf{\u} \leq U
\end{equation}
or rate-of-strain
\begin{equation}
	\label{eq:PDE_rate-of-strain}
	\linf{\nabla\u} \leq \Gamma.
\end{equation}
We are provided with initial data, $\theta(\mathbf{x},0)=\theta_{0}(\mathbf{x})$. We use the mix-norm throughout to measure homogenization,   $\|\nabla^{-1}\theta(\,\cdot\,,t)\|_{L^{2}}$.
We define the following ratio as a measure of the dominant scalar length scale:
\begin{equation}
\lambda(t)\equiv  \frac{\|\nabla^{-1}\theta(\,\cdot\,,t)\|_{L^{2}}}{\|\theta(\,\cdot\,,t)\|_{L^{2}}}.
\end{equation}

For the energy-bounded flow problem, we non-dimensionalize the system by choosing $L$ as the length scale, $U$ as the velocity scale, and $U/L$ as the time scale. For the enstrophy-bounded flow problem, we choose the same length scale $L$, the velocity scale $L\Gamma $, and  the time scale $1/\Gamma$. Both scaling produce the following form of the advection-diffusion equation,
\begin{equation}
\label{eq:nd_ade}
	\ppt{\theta}+\mathbf{u}\cdot \nabla \theta=\frac{1}{Pe} \lap\theta,
\end{equation}
where $Pe= \frac{UL}{\kappa}$ for the energy-constrained case and  $Pe=  \frac{\Gamma L^2}{\kappa}$ for the enstrophy-constrained case. The constraints on the velocity field become $\linf{\u} \leq 1$ or $\linf{\nabla\u} \leq 1$.

\section{Absolute lower bounds on $\lambda$}

\subsection{Results for $\linf{\nabla \vec{u}} \leq 1$}

Taking the time derivative of $\lambda^2$, we find
%
\begin{equation}
	\ddt{\lambda^2} = \frac{2}{Pe}
		\left[ 
			\frac{\hone{\theta}^2\hmone{\theta}^2}
					{\ltwo{\theta}^4}  
			- 1
		\right]
		+ 2 \frac{\sint{\nabla^{-1}\theta \cdot \nabla\vec{u} \cdot 
							\nabla^{-1}\theta  }}
					  {\ltwo{\theta}^{2}}.
\end{equation}
By H\"older's inequality, we have that
\begin{equation}
\label{eq:length_ineq_rate-of-strain}
	\ddt{\lambda^2} \geq \frac{2}{Pe} \left[ 
			\frac{\hone{\theta}^2\hmone{\theta}^2}
					{\ltwo{\theta}^4}  
			- 1
		\right] - 2  \lambda^2 .
\end{equation}
We can provide a lower bound on $\lambda$ at each instant. By apply Gr\"onwall's inequality and the fact that the bracketed term is greater than or equal to zero, it follows from \eqref{eq:length_ineq_rate-of-strain} that
%
\begin{equation}
\label{eq:exponential_enstrophy}
	\lambda (t) \geq \lambda(0)e^{- t}.
\end{equation}
%
Therefore, perfect mixing in finite time is impossible.

One can show that 
%
\begin{subequations}
\begin{align}
\frac{d}{dt}\left(\frac{\|\nabla\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}\right) &= \frac{\|\theta\|_{L^{2}}^2\frac{d}{dt}\|\nabla\theta\|_{L^{2}}^2-\|\nabla\theta\|_{L^{2}}^2\frac{d}{dt}\|\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^4}\\
&= \frac{-2\int \partial_{i}u_{j}\partial_{i}\theta\partial_{j}\theta - \frac{2}{Pe} \|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}+\frac{2}{Pe}\frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \\
&=-\frac{2}{Pe}\left(\frac{\|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2} - \frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \right) - 2\frac{\sint{\nabla\theta \cdot \nabla\vec{u} \cdot 
							\nabla\theta  }}{\|\theta\|_{L^{2}}^2} 
\\
&\leq 2 \frac{\hone{\theta}^2}{\ltwo{\theta}^2}
\end{align}
\end{subequations}
%
From $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, one finds that 
\begin{equation}
\ltwo{\theta}\geq  \ltwo{\theta_{0}}\exp\left[-\frac{1}{2Pe}\frac{\hone{\theta_{0}}^2}{\ltwo{\theta_{0}}^2}\left(e^{2 t} -1\right)\right]
\end{equation}
Using this with \eqref{eq:exponential_enstrophy}, we find that 
\begin{equation}
\hmone{\theta} \geq  \hmone{\theta_{0}} \exp\left[- t -\frac{1}{2 Pe}\frac{\hone{\theta_{0}}^2}{\ltwo{\theta_{0}}}\left(e^{2 t} -1\right)\right]
\end{equation}

\subsection{Results for $\linf{\u}\leq 1$}
Here we extend the results first introduced by \cite{Chi-Cheu1996}.  It is first useful to express the following quantities as:
%
\begin{eqnarray}
	 \hone{\theta}^2 &=& - 2\sint{\theta \lap \theta} \\
	 							&=& Pe \sint{\theta\left(\ppt{\theta}
	 									-\frac{1}{Pe}\lap \theta\right)} 
	 									-Pe \sint{\theta\left(\ppt{\theta}
	 									+\frac{1}{Pe}\lap \theta\right)} 
\end{eqnarray}
%
\begin{eqnarray}
	\ddt{}\ltwo{\theta}^2 &=& 2\sint{\theta\ppt{\theta}} \\
										 &=&\sint{\theta\left(\ppt{\theta}
	 									-\frac{1}{Pe}\lap \theta\right)} 
										 + \sint{\theta\left(\ppt{\theta}
	 									+\frac{1}{Pe}\lap \theta\right)} 
\end{eqnarray}
%
\begin{eqnarray}
	\ddt{}\hone{\theta}^2 &=& -2\sint{\ppt{\theta}\lap \theta} \\
	 									&=& Pe \sint{\left(\ppt{\theta}
	 									-\frac{1}{Pe}\lap \theta\right)^2} 
	 									-Pe \sint{\left(\ppt{\theta}
	 									+\frac{1}{Pe}\lap \theta\right)^2} .
\end{eqnarray}

We then compute the following derivative:
%
\begin{eqnarray*}
	\ddt{} \pbrac{ \frac{\hone{\theta}^2}{\ltwo{\theta}^2} } 
			&=& \frac{1}{\ltwo{\theta}^4}
			\sbrac{
				\ltwo{\theta}^2\ddt{}\hone{\theta}^2
				-\ddt{}\ltwo{\theta}^2\hone{\theta}^2			
			}\\
			&=& \frac{1}{\ltwo{\theta}^4}
			\sbrac{
				\ltwo{\theta}^2
				\pbrac{
					Pe \sint{\left(\ppt{\theta}
	 									-\frac{1}{Pe}\lap \theta\right)^2} 
 					-Pe\sint{\left(\ppt{\theta}
	 									+\frac{1}{Pe}\lap \theta\right)^2} 
				}
			}\\
		&-&\frac{1}{\ltwo{\theta}^4}
			\sbrac{
				Pe
				\pbrac{
					 \sint{\theta\left(\ppt{\theta}
	 									-\frac{1}{Pe}\lap \theta\right)} 
 				}^2		
 				-
 				Pe
 				\pbrac{
					 \sint{\theta\left(\ppt{\theta}
	 									+\frac{1}{Pe}\lap \theta\right)} 
 				}^2					
			}.
\end{eqnarray*}
%
Using H\"older's inequality and \eqref{eq:PDE_advection}, this simplifies to
%
\begin{eqnarray*}
	\ddt{} \pbrac{ \frac{\hone{\theta}^2}{\ltwo{\theta}^2} } 
			&\leq & \frac{Pe}{\ltwo{\theta}^2}
			\sbrac{
					 \sint{(\vec{u}\cdot \nabla \theta)^2} 
			}.
\end{eqnarray*}
By applying H\"older's inequality again, we have
\begin{equation}
\label{eq:k2growth_energy}
	\ddt{} 
		\pbrac{ 
			\frac{\hone{\theta}^2}{\ltwo{\theta}^2} 
		} 
		\leq  
		Pe
		\frac{\hone{\theta}^2}{\ltwo{\theta}^2} .
\end{equation}
%
Thus, we find that 
%
\begin{equation}
		\frac{\hone{\theta}}{\ltwo{\theta}} 
		\leq  
		\frac{\hone{\theta_0}}{\ltwo{\theta_0}}
		\exp{\pbrac{\frac{Pe}{2} t}}
\end{equation}
%
Using the inequality $\hone{\theta}\hmone{\theta}\geq \ltwo{\theta}^2$, we know that 
%
\begin{equation}
\label{eq:lambda_bound}
\lambda(t) \geq \frac{\ltwo{\theta_0}}{\hone{\theta_0}}\exp{\pbrac{-\frac{Pe}{2}t}}.
\end{equation}
%
Using \eqref{eq:k2growth_energy} with  $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, 
we find that
%
\begin{equation}
\ltwo{\theta}\geq \ltwo{\theta_{0}}\exp\left[-\frac{1}{Pe^2}\frac{\hone{\theta_0}^2}{\ltwo{\theta_0}^2}\left(e^{Pe \, \, t}-1\right)\right]
\end{equation}
%
Using the above relation with  \eqref{eq:lambda_bound}, we arrive at
%
\begin{equation}
\hmone{\theta}\geq \frac{\ltwo{\theta_{0}}^2}{\hone{\theta_0}}\exp\left[-\frac{Pe}{2} \,\, t-\frac{1}{Pe^2}\frac{\hone{\theta_0}^2}{\ltwo{\theta_0}^2}\left(e^{Pe \,\, t}-1\right)\right]
\end{equation}

\section{Local-in-time optimization for $L^{2}$ constrained flows}

We consider the local-in-time optimization strategy first introduced by \cite{JFM2011} in the diffusion-less case. We find that this strategy generalizes to the case with diffusion. The local-in-time optimal velocity fields maximize the instantaneous mixing rate by minimizing $\ddt{}\hmone{\theta}^2$ or equivalently minimizing $\ddt{\lambda^2}$ . The velocity field is constrained by energy $\ltwo{\u} = U$ or rate-of-strain $\ltwo{\nabla\u} = \Gamma.$ Note the use of the $L^2$ norm rather than the $L^{\infty}$ norm used earlier.  As similarly done with the $L^{\infty}$ constrained system, we can perform non-dimensionalization to arrive at \eqref{eq:nd_ade} where $U$ and $\Gamma$ now constrain the $L^{2}$ norms of the velocity field. The optimal velocity fields are given instantaneously by (in non-dimensional form)
\begin{equation}
\mathbf{u}= \frac{\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
\end{equation} 
and,  for the rate-of-strain constraint, by 
\begin{equation}
\mathbf{u}= \frac{-\invlap\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\nabla^{-1}\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}.
\end{equation}

We solve \eqref{eq:nd_ade} by using a Fourier spectral basis to represent the spatial domain with a 4th order Runge-Kutta time-stepping method. See Appendix \ref{sec:num_analysis} for details on numerical error analysis. We use

\begin{figure}
\includegraphics[width=\textwidth]{enstrophy_film}
\caption{Local-in-time optimization with enstrophy constraint. Top filmstrip is for $Pe = 4096$ and the bottom filmstrip is $Pe=256$.}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{enstrophy_norms}
\caption{Enstrophy}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{enstrophy_length}
\caption{Enstrophy}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{enstrophy_rate}
\caption{Enstrophy}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{energy_film}
\caption{Local-in-time optimization with energy constraint. Top filmstrip is for $Pe = 4096$ and the bottom filmstrip is $Pe=256$.}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{energy_norms}
\caption{Energy}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{energy_length}
\caption{Energy}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{energy_rate}
\caption{Energy}
\end{figure}

%Define the spectral variance as
%%
%\begin{equation}
%		\left[ 
%			\frac{\hone{\theta}^2\hmone{\theta}^2}
%			{\ltwo{\theta}^4}  
%			- 1
%		\right].
%\end{equation}
%%
%By using this definition with H\"older's inequality provided that  $\linf{\nabla\vec{u}}\leq \Gamma$, we find that
%%
%\begin{equation}
%\label{eq:length_ineq_rate-of-strain}
%	\ddt{\lambda^2} \geq 2 1/Pe \sigma^2 - 2 \Gamma \lambda^2 .
%\end{equation}
%%
%By taking the long-time average (noted as $\langle \cdot \rangle \equiv\lim_{T\rightarrow\infty}\frac{1}{T}\int_{0}^T \,\, \cdot \,\, dt $ ) of the inequality above, we find that 
%%
%\begin{equation}
%	0 \geq  2 \kappa \tavg{\sigma^2} - 2 \Gamma \tavg{\lambda^2}.
%\end{equation}
%%
%The left hand side is zero since $\lambda^2$ is bounded by Poincar\'e's inequality. Thus, we find that
%%
%\begin{equation}
%	\tavg{\lambda^2} \geq   \lambda_{B}^2 \tavg{\sigma^2} 
%\end{equation}
%%
%where the Batchelor scale is given by $\lambda_{B} = \sqrt{\kappa/\Gamma}.$

\section{Conclusion}

We conclude that ...

\
\section*{Acknowledgements}

We thank ....

\appendix
\section{Numerical analysis}
\label{sec:num_analysis}
\bibliographystyle{jfm}
%% Note the spaces between the initials
\bibliography{manuscript}

\end{document}

### 2017-09-08 run.py
removed file run.py

@@ -1,45 +1,0 @@
-from integrators import RK4, RK4_timestepper, FE_timestepper
-from tools import ScalarTool, VectorTool, create_grid, dt_cfl
-from operators import OperatorKit
-import numpy as np
-import matplotlib.pyplot as plt
-import pickle
-
-if __name__ == "__main__":
-    # Parameters
-    L = 1.0
-    N = 256
-    U = 1.0
-    T = 2.0
-    Pe_list = np.linspace(5, 100, 20)
-
-    for Pe in Pe_list:
-        print(Pe)
-        kappa = 1.0 / Pe
-        # Create tool box
-        st = ScalarTool(N, L)
-        okit = OperatorKit(N, L, kappa)
-
-        # Initial condition
-        X = create_grid(N, L)
-        th0 = np.sin((2.0 * np.pi / L) * X[0])
-        th0_hat = st.ifft(th0)
-
-        # Create operators: d th / dt = operator (th)
-        def lit_energy_op_hat(scalar_hat):
-            return okit.lit_energy_op_hat(scalar_hat, U)
-
-        def sin_op_hat(scalar_hat):
-            return okit.sin_flow_op_hat(scalar_hat)
-
-        dt = 0.25 * dt_cfl(N, L, kappa, U)
-        print('dt= ', dt)
-        time = np.linspace(0, T, round(T / dt))
-
-        th0_hat = RK4_timestepper(sin_op_hat, th0_hat, 0.001)
-        # th_hist_hat = RK4(lit_energy_op_hat, th0_hat, time)
-        th_hist_hat = RK4(lit_energy_op_hat, th0_hat, time)
-
-        output = open('pe=%d' % Pe + '.pkl', 'wb')
-        pickle.dump([time, th_hist_hat], output)
-        output.close()

### 2017-09-22 jfm_rapids/manuscript.tex
made changes to manuscript

@@
 \documentclass{jfm}
-\usepackage{graphicx}
-\usepackage{epstopdf, epsfig}
+%\usepackage{graphicx}
+%\usepackage{epstopdf, epsfig}
 
@@
 \usepackage{amsmath}
-
-% User-defined commands
-
+\usepackage{hyperref}
+%
+%% User-defined commands
+%
 \newcommand{\ddt}[1]{\frac{d #1}{dt}}
@@
 
-\shorttitle{Diffusion effects on optimal mixing and filamentation}
+\shorttitle{Diffusion limitations on mixing by incompressible flows}
 \shortauthor{C. J. Miles and C. R. Doering}
 
-\title{Diffusion effects on optimal mixing and filamentation}
+\title{Diffusion limitations on mixing by incompressible flows}
 
@@
 \begin{abstract}
-In this work, we investigate the role of diffusion and its impact on our goals for optimal mixing.
-We show numerical evidence that diffusion can limit the length scales achievable by a generalized Batchelor length scale [\cite{Batchelor1959a}] for incompressible flows with uniformly bounded energy or rate-of-strain for optimal stirring protocols.
-We also show that perfect mixing in finite time is impossible for such constraints by extending the work of \cite{Chi-Cheu1996}.
+An incompressible flow can be an effective mixer of a dye by appropriately advecting the dye to produce small filamentation length scales.
+It is known that the Batchelor length scale [\cite{Batchelor1959a}] is the theorized lower limit of dye length scales  achievable under turbulent flows.
+We provide numerical evidence that this limitation may be more general and applies to incompressible flows under mild physical constraints such as fixed enstrophy and energy.
+We consider local-in-time flow optimization under these constraints with the objective of maximizing mixing rate performance.
+For enstrophy-bounded optimal flows, we find that the strength of diffusion has no impact on the long-term mixing rate performance.
+For energy-constrained optimal flows, we find that an increase in the strength of diffusion worsens this performance.
+We provide analytical lower bounds on mixing rates and length scales achievable under related constraints (pointwise bounded speed and rate-of-strain) by extending the work of \cite{JFM2011} and \cite{Chi-Cheu1996}.
+
 \end{abstract}
@@
 \begin{keywords}
+Optimal mixing, incompressible flow, diffusion, Batchelor scale
 \end{keywords}
@@
 Optimal mixing is important to many areas of science and engineering.
-A question of interest across these domains is ``How can one stir to enhance the rate of mixing?'' We address this question by formulating the problem by considering complete control of an incompressible flow in a periodic domain with mild physical constraints.
-In particular, we consider a  domain $D=[0,L]^{d}$  where $L$ is the side length and $d$ is the total number of spatial dimensions.
-All functions defined on $D$ have periodic boundary conditions.
-Let $\theta(\mathbf{x},t): D \times [0,T] \rightarrow [-1,1]$ be the tracer concentration field that evolves according to the advection-diffusion equation,
+A question of interest across these domains is ``How can one stir to enhance the rate of mixing?'' We explore this question and study the impact of molecular diffusion.
+We address this topic by considering an incompressible flow with mild physical constraints in a periodic box with side length $L$ in $d$ dimensions.
+We consider a mean-zero tracer concentration field $\theta$ that evolves according to the advection-diffusion equation,
 \begin{equation}
 	\label{eq:PDE_advection}
-	\ppt{\theta}+\mathbf{u}\cdot \nabla \theta=\kappa \lap\theta
+	\ppt{\theta}+\mathbf{u}\cdot \nabla \theta=\kappa \lap\theta,
 \end{equation}
-where $\kappa$ is the molecular diffusion coefficient and $\mathbf{u}(\mathbf{x},t)$ is an incompressible ($\nabla\cdot \mathbf{u}=0$) velocity field constrained by bounded energy
+with initial data $\theta(\mathbf{x},0)=\theta_{0}(\mathbf{x})$, where $\kappa$ is the molecular diffusion coefficient and $\mathbf{u}(\mathbf{x},t)$ is the incompressible ($\nabla\,\cdot\, \vec{u}=0$) flow field.
+The flow is constrained by enstrophy $\ltwo{\nabla\u} = \Gamma L^{d/2}$ or energy $\ltwo{\u} = UL^{d/2}$ where $\Gamma$ is the root mean square rate-of-strain and $U$ is the root mean square speed.
+We primarily use the $H^{-1}$ norm or mix-norm throughout to measure homogenization,
+
 \begin{equation}
-	\label{eq:PDE_energy}
-	\linf{\u} \leq U
+\hmone{\theta}=\sqrt{\sint{ |\nabla^{-1} \theta( \vec{x},t)|^2}}=\sqrt{ \sum_{\vec{k}\neq \vec{0}} L^d \frac{|\hat{\theta}_{\vec{k}}(t)|^{2}}{|\vec{k}|^2}}
 \end{equation}
-or rate-of-strain
+where $\nabla^{-1}=\nabla \Delta^{-1}$, the operator $\Delta^{-1}$ acting on  a function $\rho$ returns the solution $\phi$ of the Poisson equation $ \Delta \phi = \rho $, and $\hat{\theta}_{\vec{k}}(t) =  \frac{1}{L^{d}}\sint{\theta(\vec{x},t)e^{-i\vec{k}\cdot\vec{x}}}$.
+Lower values of the  $H^{-1}$ norm corresponds to a more mixed state.
+Note that $H^{-1}$ norm can decrease in two ways: either by decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ or by advecting the flow such that the tracer concentration acquires more spectral mass in the higher wave-numbers and takes advantage of the $1/|\vec{k}|^2$ dependence.
+We use the $H^{-1}$ norm to define the (exponential) rate of mixing as
 \begin{equation}
-	\label{eq:PDE_rate-of-strain}
-	\linf{\nabla\u} \leq \Gamma.
+\label{eq:rate}
+r(t) = -  \frac{\ddt{}\hmone{\theta}}{\hmone{\theta}}.
 \end{equation}
-We are provided with initial data, $\theta(\mathbf{x},0)=\theta_{0}(\mathbf{x})$. We use the mix-norm throughout to measure homogenization,   $\|\nabla^{-1}\theta(\,\cdot\,,t)\|_{L^{2}}$.
-We define the following ratio as a measure of the dominant scalar length scale:
+The $L^{2}$ norm $\ltwo{\theta}$ and the $H^{1}$ norm $\hone{\theta}$ are also common measures of mixing and will be considered here as well.
+
+We define the following ratio as a measure of the characteristic filamentation length scale:
 \begin{equation}
-\lambda(t)\equiv  \frac{\|\nabla^{-1}\theta(\,\cdot\,,t)\|_{L^{2}}}{\|\theta(\,\cdot\,,t)\|_{L^{2}}}.
+\lambda(t)\equiv  2\pi \frac{\|\nabla^{-1}\theta(\,\cdot\,,t)\|_{L^{2}}}{\|\theta(\,\cdot\,,t)\|_{L^{2}}}.
 \end{equation}
+Note that $\lambda(t)$ returns the wavelength of the wavenumber $\vec{k}$ for a tracer concentration field composed only of the Fourier mode with wavenumber $\vec{k}$ (i.e.
+$\theta(\vec{x},t) = Re[ A e^{-i\vec{k}\cdot \vec{x}}]$ and $A$ is a complex constant).
+In general, $\lambda$ is the weighted root mean square wavelength with weights given by $|\theta_{\vec{k}}|/\ltwo{\theta}$.
 
-For the energy-bounded flow problem, we non-dimensionalize the system by choosing $L$ as the length scale, $U$ as the velocity scale, and $U/L$ as the time scale.
 For the enstrophy-bounded flow problem, we choose the same length scale $L$, the velocity scale $L\Gamma $, and  the time scale $1/\Gamma$.
-Both scaling produce the following form of the advection-diffusion equation,
+For the energy-bounded flow problem, we non-dimensionalize the system by choosing $L$ as the length scale, $U$ as the velocity scale, and $L/U$ as the time scale.
+Both scalings produce the following form of the advection-diffusion equation,
 \begin{equation}
@@
 \end{equation}
-where $Pe= \frac{UL}{\kappa}$ for the energy-constrained case and  $Pe=  \frac{\Gamma L^2}{\kappa}$ for the enstrophy-constrained case.
-The constraints on the velocity field become $\linf{\u} \leq 1$ or $\linf{\nabla\u} \leq 1$.
+where $Pe=  \frac{\Gamma L^2}{\kappa}$ for the enstrophy-constrained case and $Pe= \frac{UL}{\kappa}$ for the energy-constrained case.
+The constraints on the flow become $\ltwo{\nabla\u} = 1$ or $\ltwo{\u} = 1$.
 
-\section{Absolute lower bounds on $\lambda$}
+We will first review results for the $Pe = \infty$ enstrophy-constrained case.
+\cite{JFM2011} showed numerical evidence that the filament width $\lambda$ seemingly decreased continually by instanateous flow optimization.
+This type of optimization will be considered in this work as well.
+Self-similar flows can realize a decreasing $\lambda$ over time as shown analytically by [\cite{Alberti2014a}].
+It was rigorously proven indepedently by \cite{GI2014} and \cite{CS2013} that $\lambda$ decreased at most exponentially --- consistent with \cite{JFM2011}  and \cite{Alberti2014a}.
+The work of \cite{GI2014} relied on PDE regularization results of \cite{Crippa} while the approach of\cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
 
-\subsection{Results for $\linf{\nabla \vec{u}} \leq 1$}
+For $Pe = \infty$ energy-constrained problem, \cite{JMP2012} showed that a `checkerboard' flow can also provide continually decreasing length scales.
+Moreover, $\lambda$ decreased at a fast enough rate to approach zero in finite time in contrast to the enstrophy-constrained problem where $\lambda$ decreases to zero in infinite time.
+
+The inclusion of diffusion ($Pe <\infty$) with the objective of optimal mixing has been explored.
+\cite{DF2014} investigated optimal mixing and study the evolution of the mentioned measures ($H^{-1}, L^2,$ and $H^1$ norms) of mixing under the checkerboard flow introduced by \cite{JMP2012}.
+They show that the $H^{-1}$ and $L^2$ norms decrease monotonically under this flow while the $H^{1}$ increases until it reaches a peak and then decreases.
+This peak corresponds to a  time when the length scales developed are small enough for diffusion to effectively act on steep gradients.
+\cite{Miles2017a} explored this phenomena further in the context of optimal mixing of a shell model, a reduced model using ordinary differential equations that mimic the spectral dynamics of the advection-diffusion equation.
+The authors concluded that shell-model mixing could not surpass length scales given by $\kappa/ \Gamma$ for enstrophy-constrained flows and $U/K$ for energy-constrained flows up to $O(1)$ constants.
+These length scales can be identified as a generalized Batchelor scale [\cite{Batchelor1959a}], introduced in the context of turbulence theory.
+
+In this work, we explore how diffusion impacts the evolution of the filament width $\lambda$ over time and mixing rates.
+We show numerical evidence that $\lambda$ appears to be limited by the Batchelor scale as seen in the shell model.
+Even when actively trying to choose the most optimal flow to minimize filimentation length.
+Thus, this may suggest that the Batchelor scale does not only limit turbulent flows but also all incompressible flows under the flow constraints considered here.
+
+The paper is organized as follows.
+We introduce the necessary theory regarding local-in-time optimization, a shell model, and $L^{\infty}$ flow constraints in section \ref{sec:theory}.
+Section \ref{sec:numerical_experiment} details the methodology and results of numerically implementing local-in-time flow optimization.
+Lastly, we finish with a discussion and conclusion in sections \ref{sec:discussion} and \ref{sec:conclusion} respectively.
+
+\section{Theory}
+\label{sec:theory}
+\subsection{Local-in-time optimization}
+We consider the local-in-time optimization strategy first introduced by \cite{JFM2011} in the diffusion-less case.
+We find that this strategy generalizes to the case with diffusion.
+The local-in-time optimal velocity fields maximize the instantaneous mixing rate by minimizing $\ddt{}\hmone{\theta}^2$ or equivalently minimizing $\ddt{\lambda^2}$ .
+The optimal velocity fields are given instantaneously by (in non-dimensional form)
+%
+\begin{equation}
+\mathbf{u}= \frac{\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
+\end{equation} 
+%
+for the energy constraint and by 
+%
+\begin{equation}
+\mathbf{u}= \frac{-\invlap\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\nabla^{-1}\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
+\end{equation}
+%
+for the enstrophy constraint where $\mathds{P}$ is the Leray divergence-free projector given by $\mathds{P}(\vec{v}) = \vec{v} - \nabla \Delta^{-1}(\nabla \cdot \vec{v})$.
+These flows will be studied numerically later and is the main focus of this paper.
+
+\subsection{Shell model predictions of local-in-time optimization}
+
+The shell model is a reduced model of the spectral dynamics present in the advection-diffusion equation.
+The model consists of a system of ordinary differential equations with nearest-neighboring coupling between `shells' in wavenumber space.
+\cite{Miles2017a} performed local-in-time mixing optimization in this model.
+The shell-model analysis predicts a limiting length scale given by the Batchelor scale, $\Lambda_{\Gamma} \propto\sqrt{\frac{\kappa}{\Gamma}}$  and its generalization $\Lambda_{U} \propto \frac{U}{\kappa} $.
+The non-dimensional versions are given by $\lambda_{\Gamma} \propto \frac{1}{\sqrt{Pe}}$ and $\lambda_{U} \propto\frac{1}{Pe}$.
+Throughout, when the symbol $\propto $ is used, the proportionality constant is $O(1)$.
+Also from here forward, we will refer to the Batchelor scale to mean either $\lambda_{\Gamma}$ or its generalization $\lambda_{U}$.
+The predicted long-run rates (after reaching the Batchelor scale) are given by $R_{\Gamma} \propto \kappa/\lambda_{\Gamma}^2 $  and  $R_{U}\propto \kappa/\lambda_{U}^2$  The non-dimensional versions are given by $r_{\Gamma} \propto 1$ and $r_{U} \propto 1/Pe $.
+
+\subsection{Bounds for $L^{\infty}$ constrained flows}
+We consider a subset of $L^{2}$ constrained flows --- those belonging to $L^{\infty}$.
+Quantities of rate-of-strain and speed are bounded point-wise uniformly in space and time rather than demanding that they be $L^2$ integrable as before.
+We will provide bounds on $\lambda$ and measures of mixing in this restricted setting.
+
+\label{sec:linfty_flows}
+\subsubsection{Results for $\linf{\nabla \vec{u}} = 1$}
 
@@
 
-\subsection{Results for $\linf{\u}\leq 1$}
+\subsubsection{Results for $\linf{\u}= 1$}
 Here we extend the results first introduced by \cite{Chi-Cheu1996}.  It is first useful to express the following quantities as:
@@
 
-\section{Local-in-time optimization for $L^{2}$ constrained flows}
+%
+\section{Numerical experiment: local-in-time optimization}
+\label{sec:numerical_experiment}
+\subsection{Methodology}
 
-We consider the local-in-time optimization strategy first introduced by \cite{JFM2011} in the diffusion-less case.
-We find that this strategy generalizes to the case with diffusion.
-The local-in-time optimal velocity fields maximize the instantaneous mixing rate by minimizing $\ddt{}\hmone{\theta}^2$ or equivalently minimizing $\ddt{\lambda^2}$ .
-The velocity field is constrained by energy $\ltwo{\u} = U$ or rate-of-strain $\ltwo{\nabla\u} = \Gamma.$ Note the use of the $L^2$ norm rather than the $L^{\infty}$ norm used earlier.
-As similarly done with the $L^{\infty}$ constrained system, we can perform non-dimensionalization to arrive at \eqref{eq:nd_ade} where $U$ and $\Gamma$ now constrain the $L^{2}$ norms of the velocity field.
-The optimal velocity fields are given instantaneously by (in non-dimensional form)
-\begin{equation}
-\mathbf{u}= \frac{\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
-\end{equation} 
-and,  for the rate-of-strain constraint, by 
-\begin{equation}
-\mathbf{u}= \frac{-\invlap\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\nabla^{-1}\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}.
-\end{equation}
+We solve \eqref{eq:nd_ade} by using a Fourier basis to represent the spatial domain with a 4th order Runge-Kutta time-stepping method.
+All simulation code was created in the programming language Python with package modules, pyfftw and numpy.
+The code repository can be found at \href{http://github.com/cjm715/lit}{ http://github.com/cjm715/lit}.
 
-We solve \eqref{eq:nd_ade} by using a Fourier spectral basis to represent the spatial domain with a 4th order Runge-Kutta time-stepping method.
-See Appendix \ref{sec:num_analysis} for details on numerical error analysis.
-We use
+\subsection{Results}
 
@@
 \includegraphics[width=\textwidth]{enstrophy_film}
-\caption{Local-in-time optimization with enstrophy constraint. Top filmstrip is for $Pe = 4096$ and the bottom filmstrip is $Pe=256$.}
+\caption{Local-in-time optimization with enstrophy constraint. Top filmstrip is for $Pe =\infty$ and the bottom filmstrip is $Pe=256$.}
+\label{fig:enstrophy_film}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{energy_film}
+\caption{Local-in-time optimization with energy constraint. Top filmstrip is for $Pe = \infty$ and the bottom filmstrip is $Pe=32$.}
+\label{fig:energy_film}
 \end{figure}
@@
 \caption{Enstrophy}
+\label{fig:enstrophy_norms}
+\end{figure}
+\begin{figure}
+\includegraphics[width=\textwidth]{energy_norms}
+\caption{Energy}
+\label{fig:energy_norms}
+\end{figure}
+\begin{figure}
+\includegraphics[width=\textwidth]{enstrophy_length}
+\caption{Enstrophy}
+\label{fig:enstrophy_length}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{enstrophy_length}
-\caption{Enstrophy}
+\includegraphics[width=\textwidth]{energy_length}
+\caption{Energy}
+\label{fig:energy_length}
 \end{figure}
@@
 \caption{Enstrophy}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{energy_film}
-\caption{Local-in-time optimization with energy constraint. Top filmstrip is for $Pe = 4096$ and the bottom filmstrip is $Pe=256$.}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{energy_norms}
-\caption{Energy}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{energy_length}
-\caption{Energy}
+\label{fig:enstrophy_rate}
 \end{figure}
@@
 \caption{Energy}
+\label{fig:energy_rate}
 \end{figure}
 
+ Figure \ref{fig:enstrophy_film} shows the evolution of a scalar field under the optimal flow for the enstrophy constraint.
+The top film strip corresponds to $Pe =\infty$ while the bottom is $Pe = 256$.
+The time evolution is initially similar but soon diverges over time.
+Figure \ref{fig:energy_film} shows the evolution for the energy case.
+The top film strip corresponds to $Pe =\infty$ while the bottom is $Pe = 32$.
+Notice that, unlike the $Pe = \infty$ cases, the flows with finite $Pe$ are incapable of creating length scales arbitrarily small for either the energy or enstrophy cases.
+The left subplot of Figures \ref{fig:enstrophy_length} and \ref{fig:energy_length} shows this phenomena more quantitatively by showing $\lambda$ over time eventually reaching a plateau.
+The shell-model prediction of this limiting length scale is the Batchelor scale given by $\lambda_{\Gamma} = L/\sqrt{Pe}$ for the enstrophy case and  $\lambda_{U} = L/Pe$ for the energy case.
+The right plots of Figures \ref{fig:enstrophy_length} and \ref{fig:energy_length} shows scaled versions of $\lambda$ given by  $\lambda/\lambda_{\Gamma}$ and $\lambda/\lambda_{U}$ respectively.
+Notice how they plateau around an $O(1)$ constant.
+Thus, this result is consistent with the shell-model predictions.
+
+ Figures \ref{fig:enstrophy_rate} and \ref{fig:energy_rate} shows the rate $r$ as defined in \eqref{eq:rate}.
+The rate during the transient phase for the enstrophy case is $\Gamma$ which is consistent with rates expected from $Pe=\infty$ mixing studies.
+For all values of $Pe$ considered, there is an increase in the rate of mixing after transient behavior has finished to a long-run rate.
+Surprisingly, this long-run mixing rate appears to be {\it independent} of $Pe$ for fixed enstrophy.
+Thus, this implies that the rate of mixing is only dependent on the rate-of-strain $\Gamma$ and not influenced by the strength of diffusion.
+Although, it should be noted that the onset of the long-run rate is affected by the values of $Pe$.
+When $Pe$ is small (strong diffusion), the Batchelor scale is reached early.
+From the work of \cite{GI2014} and \cite{CS2013}, $\lambda$ can decreases at most exponentially for $Pe = \infty$.
+If we assume that the local-in-time flows nearly saturate this bound in the transient phase, we model $\lambda$ as  $\lambda (t) = \lambda(0)\exp(- t) $ during this time.
+Thus, we expect the critical transition time $t_{c}$ that marks the end of this transient period is given by the condition $\lambda(t_{c})= \lambda_{\Gamma}$.
+Thus, this time is theorized to be $t_{c}=\ln(\lambda(0)/\lambda_{\Gamma}) = \ln ( \sqrt{Pe} )$ for $Pe>1$ (If $Pe \leq 1$, then there is no transient phase).
+From the work of \cite{JMP2012} on the fixed energy case, $\lambda(t)$ can decrease linearly in time to produce perfect mixing in finite time.
+Thus, we model the transient phase as $\lambda(t)=\lambda(0)(1/2-t)$ where we are assuming that the optimal local-in-time flow nearly saturates the bound of the modified checkerboard flow (See Appendix \ref{appendix:checkerboard}).
+Therefore, we theorize that the critical transition time is $t_{c}=1/2 - \lambda_{U}/\lambda(0) = 1/2 - 1/Pe$ with $Pe> 2$ (If $Pe \leq 2$, there is not transient phase) for the energy case.
+
+ For the energy case, we again have an increase in mixining rate compared to the $Pe=\infty$ transient behavior.
+The long-term mixing rate is proportional to $Pe$ in contrast to the long-term mixing rate of enstrophy which carried no dependence on $Pe$.
+
+The right subplot of Figure \ref{fig:energy_rate} is the rate $r$ divided by $Pe$.
+We see oscillations of $r/Pe$ around the value $1.0$ which indicates that our numerical results are consistent with our predictions from the shell model.
+
+% Figures \ref{fig:enstrophy_norms} and \ref{fig:energy_norms} show the evolution the  $H^{-1}$,  $L^{2}$, and $H^{1}$ norms for different values of finite $Pe$.
+
+\section{Discussion}
+\label{sec:discussion}
+Our local-in-time optimization results suggest that there is a limiting length scale and rate.
+The bounds derived under the $L^{\infty}$ constrained flow assumption did result in proving either of these observations.
+However, they did definitely rule out the possibility of perfect mixing in finite time in either case of enstrophy and energy.
+However this result may have already been known based on regularity theory of partial differential equations.
+Although, we believe there is a gap between the inequalities derived.
+We surmise that the deficiencies in our predictions is not due to the added assumption of optimal flows belonging to $L^{\infty}$, but rather that the incompressibility condition was not fully exploited and maybe crucial to proving the limiting length scale.
+The analysis for energy and enstrophy constrained cases both relied on bounding the $\frac{\hone{\theta}}{\ltwo{\theta}}$ over time.
+This analysis allowed for the possibility of infinite growth without bound.
+From our local-in-time optimization analysis, we can see that this is not the case and approaches a maximum in time.
+Thus, we believe that this maybe a crucial step in proving the limiting length and rate.
+However, we have not successfully ruled out the possibility of infinite growth of this quantity over time.
+The the question remains, "Does there exist energy or enstrophy-constrained incompressible flows where $\frac{\hone{\theta}}{\ltwo{\theta}}$grows to infinity in time in the presence of molecular diffusion?" Or rather, can this possibility be ruled out definitively by proof.
+
+In future work, we would like to consider the optimal control problem coined global-in-time optimization which tries to minimize the filamentation width at the end time rather than instantaneously attempting to minimize the its decay rate.
+This may lead to flows that are able to extend to even smaller length scales.
+This global-in-time optimization has been explored in the work of \cite{Miles2017a} within the context of the shell model.
+The authors showed that global-in-time and local-in-time optimization appeared to give similar mixing rates.
+
+\section{Conclusion}
+\label{sec:conclusion}
+We provided numerical evidence that the Batchelor scale may be the limiting scale for incompressible flows with bounded energy and enstrophy.
+It remains an open question if this can be proved rigorously.
+We also demonstrated that larger diffusion strength (larger $Pe$)  does not appear to affect the long-term mixing performance for the enstrophy case.
+For the energy-case, an increase in diffusion strength has an adverse affect and worsens the long-term mixing performance.
+.
+
+%
 %Define the spectral variance as
@@
 %where the Batchelor scale is given by $\lambda_{B} = \sqrt{\kappa/\Gamma}.$ 
-
-\section{Conclusion}
-
-We conclude that ...
-
+%
+%
+%We conclude that ...
+%
+%By a dimensional analysis, we conjecture that the velocity field with $\hmone{\u}$=1 may be capable decreasing $\lambda$ past the Batchelor scale. 
 \
@@
 
-We thank ....
+This work was supported in part by NSF Awards PHY-1205219 and DMS-1515161.
+One of us (CRD) is additionally grateful for Fellowship funding from the John Simon Guggenheim Memorial Foundation.
+We are appreciative of the valuable feedback provided by Ian Tobasco and Karen Zaya.
 
 \appendix
-\section{Numerical analysis}
-\label{sec:num_analysis}
+\section{Mixing time of modified checkerboard flow}
+\label{appendix:checkerboard}
+The  consider a modified version of the checkerboard flow from \cite{JMP2012}.
+Suppose one starts with the initial `binary' dye concentration field where $\theta_{0}(\vec{x}) = 1$ for $x_{1}< 1/2$ and $\theta_{0}(\vec{x}) = -1$ for $x_{1}\geq 1/2$ as done in  \cite{JMP2012}.
+We constrain $\vec{u}$ to be  $\ltwo{\vec{u}} = 1$.
+
+%\section{Numerical analysis}
+%\label{sec:num_analysis}
+%Our conclusions rely heavily on the accuracy of our numerical solutions to the advection diffusion equations.
+Careful numerical analysis is thus important to make sure the length resolution is sufficient and spectral amplitudes are computed to sufficient numerical accuracy.
+
 \bibliographystyle{jfm}
-%% Note the spaces between the initials
 \bibliography{manuscript}

### 2017-09-28 jfm_rapids/jfm-instructions.tex
adding create_flux_pbs_script.py

--- 2017-09-08 jfm_rapids/manuscript.tex
@@
 
-% My own packages
-
-\usepackage{ dsfont }
-\usepackage{amsmath}
-
-% User-defined commands
-
-\newcommand{\ddt}[1]{\frac{d #1}{dt}}
-%\newcommand{\hmone}[1]{\|#1\|_{H^{-1}}}
-\newcommand{\hmone}[1]{\|\nabla^{-1} #1\|_{L^{2}}}
-\newcommand{\ltwo}[1]{\|#1\|_{L^{2}}}
-%\newcommand{\hone}[1]{\|#1\|_{H^{1}}}
-\newcommand{\hone}[1]{\| \nabla #1\|_{L^{2}}}
-\newcommand{\htwo}[1]{\|#1\|_{H^{2}}}
-\newcommand{\sint}[1]{\int_{D} #1 \, d^{d}\mathbf{x}}
-\newcommand{\tint}[1]{\int_{0}^{T} #1 \, dt}
-\renewcommand{\vec}[1]{\mathbf{#1}}
-\newcommand{\linf}[1]{\| #1 \|_{L^{\infty}}}
-\newcommand{\tavg}[1]{\langle  #1 \rangle}
-\renewcommand{\u}{\mathbf{u}}
-%\newcommand{\ppt}[1]{\frac{\partial #1}{\partial t}}
-\newcommand{\ppt}[1]{\partial_{t} #1}
-\newcommand{\lap}{\Delta }
-\newcommand{\invlap}{\Delta^{-1}}
-%\newcommand{\lap}{\nabla^{2}}
-%\newcommand{\invlap}{\nabla^{-2}}
-\newcommand{\pbrac}[1]{\left( #1 \right)}
-\newcommand{\sbrac}[1]{\left[ #1 \right]}
 \newtheorem{lemma}{Lemma}
@@
 
-\shorttitle{Diffusion effects on optimal mixing and filamentation}
-\shortauthor{C. J. Miles and C. R. Doering}
+\shorttitle{Guidelines for authors}
+\shortauthor{A. N. Other, H.-C. Smith and J. Q. Public}
 
-\title{Diffusion effects on optimal mixing and filamentation}
+\title{Guidelines for authors and submission template}
 
-\author{Christopher J. Miles\aff{1,2,3}
-  \corresp{\email{cmiless@umich.edu}}
- \and Charles R. Doering\aff{1,2,3}}
+\author{Alan N. Other\aff{1}
+  \corresp{\email{jfm@damtp.cam.ac.uk}},
+  H. - C. Smith\aff{1}
+ \and J. Q.  Public\aff{2}}
 
-\affiliation{\aff{1}Department of Physics, University of Michigan,
-Ann Arbor, MI 48104-1040, USA
-\aff{2}Department of Mathematics, University of Michigan,
-Ann Arbor, MI 48104-1043, USA
-\aff{3}Center for the Study of Complex Systems, University of Michigan,
-Ann Arbor, MI 48104-1107, USA}
+\affiliation{\aff{1}Department of Chemical Engineering, University of America,
+Somewhere, IN 12345, USA
+\aff{2}Department of Aerospace and Mechanical Engineering, University of
+Camford, Academic Street, Camford CF3 5QL, UK}
 
@@
 \begin{abstract}
-In this work, we investigate the role of diffusion and its impact on our goals for optimal mixing.
-We show numerical evidence that diffusion can limit the length scales achievable by a generalized Batchelor length scale [\cite{Batchelor1959a}] for incompressible flows with uniformly bounded energy or rate-of-strain for optimal stirring protocols.
-We also show that perfect mixing in finite time is impossible for such constraints by extending the work of \cite{Chi-Cheu1996}.
+An incompressible flow can be an effective mixer of a dye by appropriately advecting the dye to produce small filamentation length scales.
+It is known that the Batchelor length scale [\cite{Batchelor1959a}] is the theorized lower limit of dye length scales  achievable under turbulent flows.
+We provide numerical evidence that this limitation may be more general and applies to incompressible flows under mild physical constraints such as fixed enstrophy and energy.
+We consider local-in-time flow optimization under these constraints with the objective of maximizing mixing rate performance.
+For enstrophy-bounded optimal flows, we find that the strength of diffusion has no impact on the long-term mixing rate performance.
+For energy-constrained optimal flows, we find that an increase in the strength of diffusion worsens this performance.
+We provide analytical lower bounds on mixing rates and length scales achievable under related constraints (pointwise bounded speed and rate-of-strain) by extending the work of \cite{JFM2011} and \cite{Chi-Cheu1996}.
 \end{abstract}
@@
 \begin{keywords}
+Authors should not enter keywords on the manuscript, as these must be chosen by the author during the online submission process and will then be added during the typesetting process (see http://journals.cambridge.org/data/\linebreak[3]relatedlink/jfm-\linebreak[3]keywords.pdf for the full list)
 \end{keywords}
 
-\section{Introduction}
+\section{How to submit to the \textbf{\textit{Journal of Fluid Mechanics}}}
+Authors must submit using the online submission and peer review system, Scholar One Manuscripts (formerly Manuscript Central) at http://mc.manuscriptcentral.com/jfm.
+If visiting the site for the first time, users must create
 
-Optimal mixing is important to many areas of science and engineering.
-A question of interest across these domains is ``How can one stir to enhance the rate of mixing?'' We address this question by formulating the problem by considering complete control of an incompressible flow in a periodic domain with mild physical constraints.
-In particular, we consider a  domain $D=[0,L]^{d}$  where $L$ is the side length and $d$ is the total number of spatial dimensions.
-All functions defined on $D$ have periodic boundary conditions.
-Let $\theta(\mathbf{x},t): D \times [0,T] \rightarrow [-1,1]$ be the tracer concentration field that evolves according to the advection-diffusion equation,
-\begin{equation}
-	\label{eq:PDE_advection}
-	\ppt{\theta}+\mathbf{u}\cdot \nabla \theta=\kappa \lap\theta
-\end{equation}
-where $\kappa$ is the molecular diffusion coefficient and $\mathbf{u}(\mathbf{x},t)$ is an incompressible ($\nabla\cdot \mathbf{u}=0$) velocity field constrained by bounded energy
-\begin{equation}
-	\label{eq:PDE_energy}
-	\linf{\u} \leq U
-\end{equation}
-or rate-of-strain
-\begin{equation}
-	\label{eq:PDE_rate-of-strain}
-	\linf{\nabla\u} \leq \Gamma.
-\end{equation}
-We are provided with initial data, $\theta(\mathbf{x},0)=\theta_{0}(\mathbf{x})$. We use the mix-norm throughout to measure homogenization,   $\|\nabla^{-1}\theta(\,\cdot\,,t)\|_{L^{2}}$.
-We define the following ratio as a measure of the dominant scalar length scale:
-\begin{equation}
-\lambda(t)\equiv  \frac{\|\nabla^{-1}\theta(\,\cdot\,,t)\|_{L^{2}}}{\|\theta(\,\cdot\,,t)\|_{L^{2}}}.
-\end{equation}
-
-For the energy-bounded flow problem, we non-dimensionalize the system by choosing $L$ as the length scale, $U$ as the velocity scale, and $U/L$ as the time scale.
-For the enstrophy-bounded flow problem, we choose the same length scale $L$, the velocity scale $L\Gamma $, and  the time scale $1/\Gamma$.
-Both scaling produce the following form of the advection-diffusion equation,
-\begin{equation}
-\label{eq:nd_ade}
-	\ppt{\theta}+\mathbf{u}\cdot \nabla \theta=\frac{1}{Pe} \lap\theta,
-\end{equation}
-where $Pe= \frac{UL}{\kappa}$ for the energy-constrained case and  $Pe=  \frac{\Gamma L^2}{\kappa}$ for the enstrophy-constrained case.
-The constraints on the velocity field become $\linf{\u} \leq 1$ or $\linf{\nabla\u} \leq 1$.
-
-\section{Absolute lower bounds on $\lambda$}
-
-\subsection{Results for $\linf{\nabla \vec{u}} \leq 1$}
-
-Taking the time derivative of $\lambda^2$, we find
-%
-\begin{equation}
-	\ddt{\lambda^2} = \frac{2}{Pe}
-		\left[ 
-			\frac{\hone{\theta}^2\hmone{\theta}^2}
-					{\ltwo{\theta}^4}  
-			- 1
-		\right]
-		+ 2 \frac{\sint{\nabla^{-1}\theta \cdot \nabla\vec{u} \cdot 
-							\nabla^{-1}\theta  }}
-					  {\ltwo{\theta}^{2}}.
-\end{equation}
-By H\"older's inequality, we have that
-\begin{equation}
-\label{eq:length_ineq_rate-of-strain}
-	\ddt{\lambda^2} \geq \frac{2}{Pe} \left[ 
-			\frac{\hone{\theta}^2\hmone{\theta}^2}
-					{\ltwo{\theta}^4}  
-			- 1
-		\right] - 2  \lambda^2 .
-\end{equation}
-We can provide a lower bound on $\lambda$ at each instant.
-By apply Gr\"onwall's inequality and the fact that the bracketed term is greater than or equal to zero, it follows from \eqref{eq:length_ineq_rate-of-strain} that
-%
-\begin{equation}
-\label{eq:exponential_enstrophy}
-	\lambda (t) \geq \lambda(0)e^{- t}.
-\end{equation}
-%
-Therefore, perfect mixing in finite time is impossible.
-
-One can show that 
-%
-\begin{subequations}
-\begin{align}
-\frac{d}{dt}\left(\frac{\|\nabla\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}\right) &= \frac{\|\theta\|_{L^{2}}^2\frac{d}{dt}\|\nabla\theta\|_{L^{2}}^2-\|\nabla\theta\|_{L^{2}}^2\frac{d}{dt}\|\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^4}\\
-&= \frac{-2\int \partial_{i}u_{j}\partial_{i}\theta\partial_{j}\theta - \frac{2}{Pe} \|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}+\frac{2}{Pe}\frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \\
-&=-\frac{2}{Pe}\left(\frac{\|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2} - \frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \right) - 2\frac{\sint{\nabla\theta \cdot \nabla\vec{u} \cdot 
-							\nabla\theta  }}{\|\theta\|_{L^{2}}^2} 
-\\
-&\leq 2 \frac{\hone{\theta}^2}{\ltwo{\theta}^2}
-\end{align}
-\end{subequations}
-%
-From $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, one finds that 
-\begin{equation}
-\ltwo{\theta}\geq  \ltwo{\theta_{0}}\exp\left[-\frac{1}{2Pe}\frac{\hone{\theta_{0}}^2}{\ltwo{\theta_{0}}^2}\left(e^{2 t} -1\right)\right]
-\end{equation}
-Using this with \eqref{eq:exponential_enstrophy}, we find that 
-\begin{equation}
-\hmone{\theta} \geq  \hmone{\theta_{0}} \exp\left[- t -\frac{1}{2 Pe}\frac{\hone{\theta_{0}}^2}{\ltwo{\theta_{0}}}\left(e^{2 t} -1\right)\right]
-\end{equation}
-
-\subsection{Results for $\linf{\u}\leq 1$}
-Here we extend the results first introduced by \cite{Chi-Cheu1996}.  It is first useful to express the following quantities as:
-%
-\begin{eqnarray}
-	 \hone{\theta}^2 &=& - 2\sint{\theta \lap \theta} \\
-	 							&=& Pe \sint{\theta\left(\ppt{\theta}
-	 									-\frac{1}{Pe}\lap \theta\right)} 
-	 									-Pe \sint{\theta\left(\ppt{\theta}
-	 									+\frac{1}{Pe}\lap \theta\right)} 
-\end{eqnarray}
-%
-\begin{eqnarray}
-	\ddt{}\ltwo{\theta}^2 &=& 2\sint{\theta\ppt{\theta}} \\
-										 &=&\sint{\theta\left(\ppt{\theta}
-	 									-\frac{1}{Pe}\lap \theta\right)} 
-										 + \sint{\theta\left(\ppt{\theta}
-	 									+\frac{1}{Pe}\lap \theta\right)} 
-\end{eqnarray}
-%
-\begin{eqnarray}
-	\ddt{}\hone{\theta}^2 &=& -2\sint{\ppt{\theta}\lap \theta} \\
-	 									&=& Pe \sint{\left(\ppt{\theta}
-	 									-\frac{1}{Pe}\lap \theta\right)^2} 
-	 									-Pe \sint{\left(\ppt{\theta}
-	 									+\frac{1}{Pe}\lap \theta\right)^2} .
-\end{eqnarray}
-
-We then compute the following derivative:
-%
-\begin{eqnarray*}
-	\ddt{} \pbrac{ \frac{\hone{\theta}^2}{\ltwo{\theta}^2} } 
-			&=& \frac{1}{\ltwo{\theta}^4}
-			\sbrac{
-				\ltwo{\theta}^2\ddt{}\hone{\theta}^2
-				-\ddt{}\ltwo{\theta}^2\hone{\theta}^2			
-			}\\
-			&=& \frac{1}{\ltwo{\theta}^4}
-			\sbrac{
-				\ltwo{\theta}^2
-				\pbrac{
-					Pe \sint{\left(\ppt{\theta}
-	 									-\frac{1}{Pe}\lap \theta\right)^2} 
- 					-Pe\sint{\left(\ppt{\theta}
-	 									+\frac{1}{Pe}\lap \theta\right)^2} 
-				}
-			}\\
-		&-&\frac{1}{\ltwo{\theta}^4}
-			\sbrac{
-				Pe
-				\pbrac{
-					 \sint{\theta\left(\ppt{\theta}
-	 									-\frac{1}{Pe}\lap \theta\right)} 
- 				}^2		
- 				-
- 				Pe
- 				\pbrac{
-					 \sint{\theta\left(\ppt{\theta}
-	 									+\frac{1}{Pe}\lap \theta\right)} 
- 				}^2					
-			}.
-\end{eqnarray*}
-%
-Using H\"older's inequality and \eqref{eq:PDE_advection}, this simplifies to
-%
-\begin{eqnarray*}
-	\ddt{} \pbrac{ \frac{\hone{\theta}^2}{\ltwo{\theta}^2} } 
-			&\leq & \frac{Pe}{\ltwo{\theta}^2}
-			\sbrac{
-					 \sint{(\vec{u}\cdot \nabla \theta)^2} 
-			}.
-\end{eqnarray*}
-By applying H\"older's inequality again, we have
-\begin{equation}
-\label{eq:k2growth_energy}
-	\ddt{} 
-		\pbrac{ 
-			\frac{\hone{\theta}^2}{\ltwo{\theta}^2} 
-		} 
-		\leq  
-		Pe
-		\frac{\hone{\theta}^2}{\ltwo{\theta}^2} .
-\end{equation}
-%
-Thus, we find that 
-%
-\begin{equation}
-		\frac{\hone{\theta}}{\ltwo{\theta}} 
-		\leq  
-		\frac{\hone{\theta_0}}{\ltwo{\theta_0}}
-		\exp{\pbrac{\frac{Pe}{2} t}}
-\end{equation}
-%
-Using the inequality $\hone{\theta}\hmone{\theta}\geq \ltwo{\theta}^2$, we know that 
-%
-\begin{equation}
-\label{eq:lambda_bound}
-\lambda(t) \geq \frac{\ltwo{\theta_0}}{\hone{\theta_0}}\exp{\pbrac{-\frac{Pe}{2}t}}.
-\end{equation}
-%
-Using \eqref{eq:k2growth_energy} with  $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, 
-we find that
-%
-\begin{equation}
-\ltwo{\theta}\geq \ltwo{\theta_{0}}\exp\left[-\frac{1}{Pe^2}\frac{\hone{\theta_0}^2}{\ltwo{\theta_0}^2}\left(e^{Pe \, \, t}-1\right)\right]
-\end{equation}
-%
-Using the above relation with  \eqref{eq:lambda_bound}, we arrive at
-%
-\begin{equation}
-\hmone{\theta}\geq \frac{\ltwo{\theta_{0}}^2}{\hone{\theta_0}}\exp\left[-\frac{Pe}{2} \,\, t-\frac{1}{Pe^2}\frac{\hone{\theta_0}^2}{\ltwo{\theta_0}^2}\left(e^{Pe \,\, t}-1\right)\right]
-\end{equation}
-
-\section{Local-in-time optimization for $L^{2}$ constrained flows}
-
-We consider the local-in-time optimization strategy first introduced by \cite{JFM2011} in the diffusion-less case.
-We find that this strategy generalizes to the case with diffusion.
-The local-in-time optimal velocity fields maximize the instantaneous mixing rate by minimizing $\ddt{}\hmone{\theta}^2$ or equivalently minimizing $\ddt{\lambda^2}$ .
-The velocity field is constrained by energy $\ltwo{\u} = U$ or rate-of-strain $\ltwo{\nabla\u} = \Gamma.$ Note the use of the $L^2$ norm rather than the $L^{\infty}$ norm used earlier.
-As similarly done with the $L^{\infty}$ constrained system, we can perform non-dimensionalization to arrive at \eqref{eq:nd_ade} where $U$ and $\Gamma$ now constrain the $L^{2}$ norms of the velocity field.
-The optimal velocity fields are given instantaneously by (in non-dimensional form)
-\begin{equation}
-\mathbf{u}= \frac{\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
-\end{equation} 
-and,  for the rate-of-strain constraint, by 
-\begin{equation}
-\mathbf{u}= \frac{-\invlap\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\nabla^{-1}\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}.
-\end{equation}
-
-We solve \eqref{eq:nd_ade} by using a Fourier spectral basis to represent the spatial domain with a 4th order Runge-Kutta time-stepping method.
-See Appendix \ref{sec:num_analysis} for details on numerical error analysis.
-We use
-
-\begin{figure}
-\includegraphics[width=\textwidth]{enstrophy_film}
-\caption{Local-in-time optimization with enstrophy constraint. Top filmstrip is for $Pe = 4096$ and the bottom filmstrip is $Pe=256$.}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{enstrophy_norms}
-\caption{Enstrophy}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{enstrophy_length}
-\caption{Enstrophy}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{enstrophy_rate}
-\caption{Enstrophy}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{energy_film}
-\caption{Local-in-time optimization with energy constraint. Top filmstrip is for $Pe = 4096$ and the bottom filmstrip is $Pe=256$.}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{energy_norms}
-\caption{Energy}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{energy_length}
-\caption{Energy}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{energy_rate}
-\caption{Energy}
-\end{figure}
-
-%Define the spectral variance as
-%%
-%\begin{equation}
-%		\left[ 
-%			\frac{\hone{\theta}^2\hmone{\theta}^2}
-%			{\ltwo{\theta}^4}  
-%			- 1
-%		\right].
-%\end{equation}
-%%
-%By using this definition with H\"older's inequality provided that  $\linf{\nabla\vec{u}}\leq \Gamma$, we find that
-%%
-%\begin{equation}
-%\label{eq:length_ineq_rate-of-strain}
-%	\ddt{\lambda^2} \geq 2 1/Pe \sigma^2 - 2 \Gamma \lambda^2 .
-%\end{equation}
-%%
-%By taking the long-time average (noted as $\langle \cdot \rangle \equiv\lim_{T\rightarrow\infty}\frac{1}{T}\int_{0}^T \,\, \cdot \,\, dt $ ) of the inequality above, we find that 
-%%
-%\begin{equation}
-%	0 \geq  2 \kappa \tavg{\sigma^2} - 2 \Gamma \tavg{\lambda^2}.
-%\end{equation}
-%%
-%The left hand side is zero since $\lambda^2$ is bounded by Poincar\'e's inequality. Thus, we find that
-%%
-%\begin{equation}
-%	\tavg{\lambda^2} \geq   \lambda_{B}^2 \tavg{\sigma^2} 
-%\end{equation}
-%%
-%where the Batchelor scale is given by $\lambda_{B} = \sqrt{\kappa/\Gamma}.$
-
-\section{Conclusion}
-
-We conclude that ...
-
-\
-\section*{Acknowledgements}
-
-We thank ....
-
-\appendix
-\section{Numerical analysis}
-\label{sec:num_analysis}
 \bibliographystyle{jfm}
-%% Note the spaces between the initials
+% Note the spaces between the initials
 \bibliography{manuscript}

### 2017-09-28 jfm_rapids/manuscript.tex
adding create_flux_pbs_script.py

@@
 An incompressible flow can be an effective mixer of a dye by appropriately advecting the dye to produce small filamentation length scales.
-It is known that the Batchelor length scale [\cite{Batchelor1959a}] is the theorized lower limit of dye length scales  achievable under turbulent flows.
+It is known that the Batchelor length scale \citep{Batchelor1959a} is the theorized lower limit of dye length scales  achievable under turbulent flows.
 We provide numerical evidence that this limitation may be more general and applies to incompressible flows under mild physical constraints such as fixed enstrophy and energy.
@@
 \end{equation}
-with initial data $\theta(\mathbf{x},0)=\theta_{0}(\mathbf{x})$, where $\kappa$ is the molecular diffusion coefficient and $\mathbf{u}(\mathbf{x},t)$ is the incompressible ($\nabla\,\cdot\, \vec{u}=0$) flow field.
+with initial data $\theta(\mathbf{x},0)=\theta_{0}(\mathbf{x})$, where $\kappa$ is the molecular diffusion coefficient and $\mathbf{u}(\mathbf{x},t)$ is a incompressible ($\nabla\,\cdot\, \vec{u}=0$) flow field.
 The flow is constrained by enstrophy $\ltwo{\nabla\u} = \Gamma L^{d/2}$ or energy $\ltwo{\u} = UL^{d/2}$ where $\Gamma$ is the root mean square rate-of-strain and $U$ is the root mean square speed.
@@
 Lower values of the  $H^{-1}$ norm corresponds to a more mixed state.
-Note that $H^{-1}$ norm can decrease in two ways: either by decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ or by advecting the flow such that the tracer concentration acquires more spectral mass in the higher wave-numbers and takes advantage of the $1/|\vec{k}|^2$ dependence.
+Note that $H^{-1}$ norm can decrease in two ways: either by decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ or by advecting the flow such that the tracer concentration acquires more spectral mass in the higher wavenumbers and takes advantage of the $1/|\vec{k}|^2$ dependence.
 We use the $H^{-1}$ norm to define the (exponential) rate of mixing as
@@
 Note that $\lambda(t)$ returns the wavelength of the wavenumber $\vec{k}$ for a tracer concentration field composed only of the Fourier mode with wavenumber $\vec{k}$ (i.e.
-$\theta(\vec{x},t) = Re[ A e^{-i\vec{k}\cdot \vec{x}}]$ and $A$ is a complex constant).
+$\theta(\vec{x},t) = Re[ A e^{-i\vec{k}\cdot \vec{x}}]$ where $A$ is a complex constant).
 In general, $\lambda$ is the weighted root mean square wavelength with weights given by $|\theta_{\vec{k}}|/\ltwo{\theta}$.
@@
 This type of optimization will be considered in this work as well.
-Self-similar flows can realize a decreasing $\lambda$ over time as shown analytically by [\cite{Alberti2014a}].
+Self-similar flows can realize a decreasing $\lambda$ over time as shown analytically by \cite{Alberti2014a}.
 It was rigorously proven indepedently by \cite{GI2014} and \cite{CS2013} that $\lambda$ decreased at most exponentially --- consistent with \cite{JFM2011}  and \cite{Alberti2014a}.
-The work of \cite{GI2014} relied on PDE regularization results of \cite{Crippa} while the approach of\cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
+The work of \cite{GI2014} relied on PDE regularization results of \cite{Crippa} while the approach of \cite{CS2013} used methods from optimal transportation theory \citep{villani2003topics}.
 
@@
 This peak corresponds to a  time when the length scales developed are small enough for diffusion to effectively act on steep gradients.
-\cite{Miles2017a} explored this phenomena further in the context of optimal mixing of a shell model, a reduced model using ordinary differential equations that mimic the spectral dynamics of the advection-diffusion equation.
-The authors concluded that shell-model mixing could not surpass length scales given by $\kappa/ \Gamma$ for enstrophy-constrained flows and $U/K$ for energy-constrained flows up to $O(1)$ constants.
-These length scales can be identified as a generalized Batchelor scale [\cite{Batchelor1959a}], introduced in the context of turbulence theory.
+\cite{Miles2017a} explored this phenomena further in the context of a shell model, a reduced model using ordinary differential equations that mimic the spectral dynamics of the advection-diffusion equation.
+The authors concluded that shell-model mixing could not surpass length scales given by $\sqrt{\kappa/ \Gamma}$ for enstrophy-constrained flows and $\kappa/U$ for energy-constrained flows up to $O(1)$ constants.
+These length scales can be identified as a generalized Batchelor scale \citep{Batchelor1959a}, introduced in the context of turbulence theory.
 
@@
 Thus, this may suggest that the Batchelor scale does not only limit turbulent flows but also all incompressible flows under the flow constraints considered here.
+Although these quantities have been known in the context of turbulence theory, the impact of these limitations on mixing rates has not been fully studied to our knowledge.
+
+Furthermore, we believe that the study of determining the smallest length scales achievable demands more attention.
+This assumption is used today throughout the computational fluid dynamics community to provide a heuristic for the grid resolutions necessary.
+Thus, we believe it is imperative to determine what conditions on $\mathbf{u}$ are necessary to justify this assumption.
 
@@
 \cite{Miles2017a} performed local-in-time mixing optimization in this model.
-The shell-model analysis predicts a limiting length scale given by the Batchelor scale, $\Lambda_{\Gamma} \propto\sqrt{\frac{\kappa}{\Gamma}}$  and its generalization $\Lambda_{U} \propto \frac{U}{\kappa} $.
-The non-dimensional versions are given by $\lambda_{\Gamma} \propto \frac{1}{\sqrt{Pe}}$ and $\lambda_{U} \propto\frac{1}{Pe}$.
-Throughout, when the symbol $\propto $ is used, the proportionality constant is $O(1)$.
+The shell-model analysis predicts a limiting length scale given by the Batchelor scale, $\Lambda_{\Gamma} =\sqrt{\frac{\kappa}{\Gamma}}$  and its generalization $\Lambda_{U}= \frac{U}{\kappa} $.
+The non-dimensional versions are given by $\lambda_{\Gamma}= \frac{1}{\sqrt{Pe}}$ and $\lambda_{U} = \frac{1}{Pe}$.
 Also from here forward, we will refer to the Batchelor scale to mean either $\lambda_{\Gamma}$ or its generalization $\lambda_{U}$.
-The predicted long-run rates (after reaching the Batchelor scale) are given by $R_{\Gamma} \propto \kappa/\lambda_{\Gamma}^2 $  and  $R_{U}\propto \kappa/\lambda_{U}^2$  The non-dimensional versions are given by $r_{\Gamma} \propto 1$ and $r_{U} \propto 1/Pe $.
+The predicted long-term rates (after reaching the Batchelor scale) are given by $R_{\Gamma} =\kappa/\lambda_{\Gamma}^2 $  and  $R_{U}=\kappa/\lambda_{U}^2$  The non-dimensional versions are given by $r_{\Gamma} =1$ and $r_{U} = Pe $.
 
@@
 
-We solve \eqref{eq:nd_ade} by using a Fourier basis to represent the spatial domain with a 4th order Runge-Kutta time-stepping method.
+We solve \eqref{eq:nd_ade} by using a Fourier basis to represent the $512 \times 512$ discretized spatial domain with a 4th order Runge-Kutta time-stepping method.
 All simulation code was created in the programming language Python with package modules, pyfftw and numpy.
@@
 \end{figure}
-
+%
 \begin{figure}
@@
 \end{figure}
-
+%
 \begin{figure}
 \includegraphics[width=\textwidth]{enstrophy_norms}
-\caption{Enstrophy}
+\caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal enstrophy-constrained flow.}
 \label{fig:enstrophy_norms}
 \end{figure}
+%
 \begin{figure}
 \includegraphics[width=\textwidth]{energy_norms}
-\caption{Energy}
+\caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal energy-constrained flow.}
 \label{fig:energy_norms}
 \end{figure}
+%
 \begin{figure}
 \includegraphics[width=\textwidth]{enstrophy_length}
-\caption{Enstrophy}
+\caption{The left subplot shows the filament length $\lambda$ over time subject to the optimal enstrophy-constrained flow.
+The right subplot is the same data except scaled: $\lambda(t)/\lambda_{\Gamma} = \lambda(t)\sqrt{Pe}$.}
 \label{fig:enstrophy_length}
 \end{figure}
-
+%
 \begin{figure}
 \includegraphics[width=\textwidth]{energy_length}
-\caption{Energy}
+\caption{The left subplot shows the filament length $\lambda$ over time subject to the optimal energy-constrained flow.
+The right subplot is the same data except scaled: $\lambda(t)/\lambda_{U} = \lambda(t) Pe$.}
 \label{fig:energy_length}
 \end{figure}
-
+%
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{enstrophy_rate}
-\caption{Enstrophy}
+\caption{Mixing rate $r(t)$ over time when subject to the optimal enstrophy-constrained flow.}
 \label{fig:enstrophy_rate}
 \end{figure}
-
+%
 \begin{figure}
@@
 \includegraphics[width=\textwidth]{energy_rate}
-\caption{Energy}
+\caption{The left subplot shows the mixing rate $r(t)$ over time when subject to the optimal energy-constrained flow. The right subplot is the same data except scaled: $r(t)/r_{U} = r(t)/Pe$.}
 \label{fig:energy_rate}
@@
 The left subplot of Figures \ref{fig:enstrophy_length} and \ref{fig:energy_length} shows this phenomena more quantitatively by showing $\lambda$ over time eventually reaching a plateau.
-The shell-model prediction of this limiting length scale is the Batchelor scale given by $\lambda_{\Gamma} = L/\sqrt{Pe}$ for the enstrophy case and  $\lambda_{U} = L/Pe$ for the energy case.
+The shell-model prediction of this limiting length scale is the Batchelor scale given by $\lambda_{\Gamma} = 1/\sqrt{Pe}$ for the enstrophy case and  $\lambda_{U} = 1/Pe$ for the energy case.
 The right plots of Figures \ref{fig:enstrophy_length} and \ref{fig:energy_length} shows scaled versions of $\lambda$ given by  $\lambda/\lambda_{\Gamma}$ and $\lambda/\lambda_{U}$ respectively.
@@
 
- Figures \ref{fig:enstrophy_rate} and \ref{fig:energy_rate} shows the rate $r$ as defined in \eqref{eq:rate}.
-The rate during the transient phase for the enstrophy case is $\Gamma$ which is consistent with rates expected from $Pe=\infty$ mixing studies.
-For all values of $Pe$ considered, there is an increase in the rate of mixing after transient behavior has finished to a long-run rate.
-Surprisingly, this long-run mixing rate appears to be {\it independent} of $Pe$ for fixed enstrophy.
-Thus, this implies that the rate of mixing is only dependent on the rate-of-strain $\Gamma$ and not influenced by the strength of diffusion.
-Although, it should be noted that the onset of the long-run rate is affected by the values of $Pe$.
-When $Pe$ is small (strong diffusion), the Batchelor scale is reached early.
-From the work of \cite{GI2014} and \cite{CS2013}, $\lambda$ can decreases at most exponentially for $Pe = \infty$.
-If we assume that the local-in-time flows nearly saturate this bound in the transient phase, we model $\lambda$ as  $\lambda (t) = \lambda(0)\exp(- t) $ during this time.
-Thus, we expect the critical transition time $t_{c}$ that marks the end of this transient period is given by the condition $\lambda(t_{c})= \lambda_{\Gamma}$.
-Thus, this time is theorized to be $t_{c}=\ln(\lambda(0)/\lambda_{\Gamma}) = \ln ( \sqrt{Pe} )$ for $Pe>1$ (If $Pe \leq 1$, then there is no transient phase).
+Figure \ref{fig:enstrophy_rate} shows the mixing rates for the enstrophy case.
+The rate during the transient phase is $\Gamma$ which is consistent with rates expected from $Pe=\infty$ mixing studies.
+For all $Pe$ considered, there is an increase in the rate of mixing after transient behavior has finished to a long-term rate.
+Surprisingly, this long-term mixing rate appears to be independent of $Pe$ for fixed enstrophy.
+{\it Thus, this implies that the long-term rate of mixing is only dependent on the rate-of-strain $\Gamma$ and not influenced by the strength of diffusion.
+}Although, it should be noted that the onset of the long-term rate is affected by the value of $Pe$.
+When there is strong diffusion (small $Pe$), the Batchelor scale is reached early.
+From the work of \cite{GI2014} and \cite{CS2013}, $\lambda$ decreases at most exponentially for $Pe = \infty$.
+If we assume that the local-in-time flows nearly saturate this bound in the transient phase, we model $\lambda$ as  $\lambda (t) = \lambda(0)\exp(- \alpha t) $ during this time.
+We expect the critical transition time $t_{c}$ that marks the end of this transient period to satisfy $\lambda(t_{c})= \lambda_{\Gamma}$.
+This time is theorized to be $t_{c}=\frac{1}{\alpha}\ln(\lambda(0)/\lambda_{\Gamma}) = \frac{1}{\alpha}\ln ( \sqrt{Pe} )$ for $Pe>1$ (If $Pe \leq 1$, then there is no transient phase).
+Hence, a smaller value of $Pe$ will result in an earlier onset of the long-term rate of mixing.
+Therefore, it is advantageous to have strong diffusion (small $Pe$) so that there is an earlier onset of the long-term mixing rate (although independent of $Pe$) which is an improvement over the mixing rate of the purely non-diffusive situation ($Pe=\infty$).
+
+For the energy case, the long-term mixing rate decreases with decreasing $Pe$ (see the left subplot of figure \ref{fig:energy_rate}).
+{\it Thus, strong diffusion results in a weak long-term mixing rate}.
+The right subplot of Figure \ref{fig:energy_rate} is $r/r_{U} =  r/Pe$.
+We see oscillations of $r/r_{U}$ around a value that is $O(1)$ which indicates that our numerical results are consistent with our predictions from the shell model.
+Thus, the long-term mixing rate is proportional to $Pe$ in contrast to the long-term mixing rate of enstrophy which carries no dependence on $Pe$.
+For the enstrophy case, we saw a benefit of picking a lower $Pe$ to result in a earlier onset of the long-term mixing behavior.
+The fixed energy case however is different.
+The onset of the long run-mixing behavior can be determined by the following model.
 From the work of \cite{JMP2012} on the fixed energy case, $\lambda(t)$ can decrease linearly in time to produce perfect mixing in finite time.
-Thus, we model the transient phase as $\lambda(t)=\lambda(0)(1/2-t)$ where we are assuming that the optimal local-in-time flow nearly saturates the bound of the modified checkerboard flow (See Appendix \ref{appendix:checkerboard}).
-Therefore, we theorize that the critical transition time is $t_{c}=1/2 - \lambda_{U}/\lambda(0) = 1/2 - 1/Pe$ with $Pe> 2$ (If $Pe \leq 2$, there is not transient phase) for the energy case.
-
- For the energy case, we again have an increase in mixining rate compared to the $Pe=\infty$ transient behavior.
-The long-term mixing rate is proportional to $Pe$ in contrast to the long-term mixing rate of enstrophy which carried no dependence on $Pe$.
-
-The right subplot of Figure \ref{fig:energy_rate} is the rate $r$ divided by $Pe$.
-We see oscillations of $r/Pe$ around the value $1.0$ which indicates that our numerical results are consistent with our predictions from the shell model.
+We model the transient phase as $\lambda(t)=\lambda(0)(1-\beta t)$.
+Therefore, we theorize that the critical transition time is $t_{c}=\frac{1}{\beta}(1 -\lambda_{U}/\lambda(0)) = \frac{1}{\beta}(1 - 1/Pe)$ with $Pe> 1$ (If $Pe \leq 1$, there is not transient phase) for the energy case.
+Thus, it is true that on can still achieve an earlier onset of the long-term mixing behavior by choosing a smaller $Pe$.
+However, an earlier onset time is accompanied by a slower long-term mixing rate.
+As for choosing a large $Pe$, the onset time is bounded above by $\frac{1}{\beta}$ and results in a faster long-term mixing rate.
+Thus, it is advantageous to have weak diffusion (large $Pe$) for mixing in the fixed energy case.
+This benefit is well illustrated by $H^{-1}$ norm in figure \ref{fig:energy_norms}.
+Notice that the mixing rate is initially slow for $Pe = 512$ but then outcompetes the mixing rate of smaller values of $Pe$.
 
@@
 \label{sec:discussion}
-Our local-in-time optimization results suggest that there is a limiting length scale and rate.
-The bounds derived under the $L^{\infty}$ constrained flow assumption did result in proving either of these observations.
-However, they did definitely rule out the possibility of perfect mixing in finite time in either case of enstrophy and energy.
-However this result may have already been known based on regularity theory of partial differential equations.
-Although, we believe there is a gap between the inequalities derived.
-We surmise that the deficiencies in our predictions is not due to the added assumption of optimal flows belonging to $L^{\infty}$, but rather that the incompressibility condition was not fully exploited and maybe crucial to proving the limiting length scale.
-The analysis for energy and enstrophy constrained cases both relied on bounding the $\frac{\hone{\theta}}{\ltwo{\theta}}$ over time.
-This analysis allowed for the possibility of infinite growth without bound.
-From our local-in-time optimization analysis, we can see that this is not the case and approaches a maximum in time.
-Thus, we believe that this maybe a crucial step in proving the limiting length and rate.
-However, we have not successfully ruled out the possibility of infinite growth of this quantity over time.
-The the question remains, "Does there exist energy or enstrophy-constrained incompressible flows where $\frac{\hone{\theta}}{\ltwo{\theta}}$grows to infinity in time in the presence of molecular diffusion?" Or rather, can this possibility be ruled out definitively by proof.
+The local-in-time optimization results suggest that there is a limiting length scale and rate.
+The bounds derived, under the $L^{\infty}$ constrained flow assumption, did not result in proving either of these observations.
+However, they did definitively rule out the possibility of perfect mixing in finite time in either constraint.
+We believe these bounds could be drastically improved.
+We surmise that the deficiencies in these bounds is due to not fully exploiting the incompressibility condition.
+It remains to be shown that $\liminf_{t\rightarrow \infty} \lambda (t)\geq C\lambda_{\Gamma}$ where C is constant dependent on domain and initial condition under an enstrophy constrained flow.
+A similar problem remains open for the fixed energy case.
+If these statements are shown, then many of the results demonstrated here numerically will hold more generally.
 
-In future work, we would like to consider the optimal control problem coined global-in-time optimization which tries to minimize the filamentation width at the end time rather than instantaneously attempting to minimize the its decay rate.
+In future work, we would like to consider the optimal control problem coined global-in-time optimization which tries to minimize the filamentation width at the end time rather than instantaneously attempting to minimize its decay rate.
 This may lead to flows that are able to extend to even smaller length scales.
@@
 \label{sec:conclusion}
-We provided numerical evidence that the Batchelor scale may be the limiting scale for incompressible flows with bounded energy and enstrophy.
-It remains an open question if this can be proved rigorously.
-We also demonstrated that larger diffusion strength (larger $Pe$)  does not appear to affect the long-term mixing performance for the enstrophy case.
-For the energy-case, an increase in diffusion strength has an adverse affect and worsens the long-term mixing performance.
-.
+
+Our numerical study of local-in-time optimization suggests that there is a limiting length scale given by a generalized Batchelor length scale which in turn determines a long-term mixing Batchelor rate.
+Although the Batchelor scale has been a theorized lower bound on the length scales present on turbulent flows, it has not been shown rigorously.
+We hope this numerical study provides insight and promotes investigation into proving what conditions are necessary on the flow for this to be the case.
+Furthermore, we showed that these limitations imply that (1), for fixed enstrophy optimal flows, strong diffusion can benefit from an early onset of a long-term mixing rate (where the rate itself however is independent of diffusion strength) while (2), for energy fixed optimal flows, strong diffusion weakens the long-term mixing rate.
+
+\section*{Acknowledgements}
+
+This work was supported in part by NSF Awards PHY-1205219 and DMS-1515161.
+One of us (CRD) is additionally grateful for Fellowship funding from the John Simon Guggenheim Memorial Foundation.
+We are appreciative of the valuable feedback provided by Guatum Iyer, Alexander Kiselev, Ian Tobasco, and Karen Zaya.
+
+%Our numerical study of local-in-time optimization suggest that there is a limiting length scale given by $\lambda_{\Gamma} = 1/\sqrt{Pe}$ (in dimensional form, $\sqrt{\kappa/\Gamma}$) for fixed enstrophy and $\lambda_{U} = 1/Pe$ (in dimensional form $\kappa/U$) for fixed energy.
+The study also suggests a long-term mixing rate given by  $r_{\Gamma} = 1 $ (in dimensional form, $\Gamma$) for fixed enstrophy and $r_{U} = Pe$ (in dimensional form, $U^2/\kappa$) for fixed energy.
 
@@
 %By a dimensional analysis, we conjecture that the velocity field with $\hmone{\u}$=1 may be capable decreasing $\lambda$ past the Batchelor scale.
-\
-\section*{Acknowledgements}
 
-This work was supported in part by NSF Awards PHY-1205219 and DMS-1515161.
-One of us (CRD) is additionally grateful for Fellowship funding from the John Simon Guggenheim Memorial Foundation.
-We are appreciative of the valuable feedback provided by Ian Tobasco and Karen Zaya.
-
-\appendix
-\section{Mixing time of modified checkerboard flow}
-\label{appendix:checkerboard}
-The  consider a modified version of the checkerboard flow from \cite{JMP2012}.
-Suppose one starts with the initial `binary' dye concentration field where $\theta_{0}(\vec{x}) = 1$ for $x_{1}< 1/2$ and $\theta_{0}(\vec{x}) = -1$ for $x_{1}\geq 1/2$ as done in  \cite{JMP2012}.
+%\appendix
+%\section{Mixing time of modified checkerboard flow}
+%\label{appendix:checkerboard}
+%We consider a similar  the checkerboard flow from \cite{JMP2012}.
+Suppose one starts with the initial `binary' dye concentration field where $\theta_{0}(\vec{x}) = 1$ for $x_{1}< 1/2$ and $\theta_{0}(\vec{x}) = -1$ for $x_{1}\geq 1/2$.
 We constrain $\vec{u}$ to be  $\ltwo{\vec{u}} = 1$.
+We consider a sheer flow as described by \cite{JMP2012}
 

### 2017-10-04 nonlinearity/manuscript.tex
adding nonlinearity version of manuscript

--- 2017-09-28 jfm_rapids/manuscript.tex
@@
-% This is file JFM2esam.tex
-% first release v1.0, 20th October 1996
-%       release v1.01, 29th October 1996
-%       release v1.1, 25th June 1997
-%       release v2.0, 27th July 2004
-%       release v3.0, 16th July 2014
-%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
-% Copyright (C) 1996, 1997, 2014 Cambridge University Press
-
-\documentclass{jfm}
-%\usepackage{graphicx}
-%\usepackage{epstopdf, epsfig}
-
-% My own packages
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%    INSTITUTE OF PHYSICS PUBLISHING                                   %
+%                                                                      %
+%   `Preparing an article for publication in an Institute of Physics   %
+%    Publishing journal using LaTeX'                                   %
+%                                                                      %
+%    LaTeX source code `ioplau2e.tex' used to generate `author         %
+%    guidelines', the documentation explaining and demonstrating use   %
+%    of the Institute of Physics Publishing LaTeX preprint files       %
+%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
+%                                                                      %
+%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
+%                                                                      %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+% First we have a character check
+%
+% ! exclamation mark    " double quote  
+% # hash                ` opening quote (grave)
+% & ampersand           ' closing quote (acute)
+% $ dollar              % percent       
+% ( open parenthesis    ) close paren.  
+% - hyphen              = equals sign
+% | vertical bar        ~ tilde         
+% @ at sign             _ underscore
+% { open curly brace    } close curly   
+% [ open square         ] close square bracket
+% + plus sign           ; semi-colon    
+% * asterisk            : colon
+% < open angle bracket  > close angle   
+% , comma               . full stop
+% ? question mark       / forward slash 
+% \ backslash           ^ circumflex
+%
+% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
+% abcdefghijklmnopqrstuvwxyz 
+% 1234567890
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+\documentclass[12pt]{iopart}
+\newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
+%Uncomment next line if AMS fonts required
+%\usepackage{iopams}  
+%
+%% My own packages
+%
 \usepackage{ dsfont }
-\usepackage{amsmath}
 \usepackage{hyperref}
+\usepackage{graphicx}
 %
@@
 
-\shorttitle{Diffusion limitations on mixing by incompressible flows}
-\shortauthor{C. J. Miles and C. R. Doering}
-
-\title{Diffusion limitations on mixing by incompressible flows}
-
-\author{Christopher J. Miles\aff{1,2,3}
-  \corresp{\email{cmiless@umich.edu}}
- \and Charles R. Doering\aff{1,2,3}}
-
-\affiliation{\aff{1}Department of Physics, University of Michigan,
-Ann Arbor, MI 48104-1040, USA
-\aff{2}Department of Mathematics, University of Michigan,
-Ann Arbor, MI 48104-1043, USA
-\aff{3}Center for the Study of Complex Systems, University of Michigan,
-Ann Arbor, MI 48104-1107, USA}
-
 \begin{document}
 
-\maketitle
+\title[Diffusion-limited mixing by incompressible flows]{Diffusion-limited mixing by incompressible flows}
+
+\author{C J Miles$^{1,2,3}$ and C R Doering$^{1,2,3}$ }
+
+\address{$^1$ Department of Physics, University of Michigan,
+Ann Arbor, MI 48104-1040, USA}
+\address{$^2$ Department of Mathematics, University of Michigan,
+Ann Arbor, MI 48104-1043, USA}
+\address{$^3$ Center for the Study of Complex Systems, University of Michigan,
+Ann Arbor, MI 48104-1107, USA}
+\ead{doering@umich.edu}
+\vspace{10pt}
+\begin{indented}
+\item[]February 2014
+\end{indented}
 
 \begin{abstract}
-An incompressible flow can be an effective mixer of a dye by appropriately advecting the dye to produce small filamentation length scales.
-It is known that the Batchelor length scale \citep{Batchelor1959a} is the theorized lower limit of dye length scales  achievable under turbulent flows.
-We provide numerical evidence that this limitation may be more general and applies to incompressible flows under mild physical constraints such as fixed enstrophy and energy.
-We consider local-in-time flow optimization under these constraints with the objective of maximizing mixing rate performance.
+Incompressible flows can be effective mixers by appropriately advecting a passive tracer to produce small filamentation length scales.
+The Batchelor length scale \cite{Batchelor1959a} was proposed as thelower limit of length scales achievable in turbulent flows.
+Here, we provide numerical evidence that this limitation may be even more general, applying as well to all incompressible flows under mild physical constraints such as bounded enstrophy or energy.
+We consider local-in-time flow optimization under these flow intensity constraints with the objective of maximizing mixing rate performance.
 For enstrophy-bounded optimal flows, we find that the strength of diffusion has no impact on the long-term mixing rate performance.
@@
 
-\begin{keywords}
-Optimal mixing, incompressible flow, diffusion, Batchelor scale
-\end{keywords}
+% Uncomment for PACS numbers
+\pacs{00.00, 20.00, 42.10}
+%
+% Uncomment for keywords
+\vspace{2pc}
+\noindent{\it Keywords}: Optimal mixing, incompressible flow, diffusion, Batchelor scale
+
+% Uncomment for Submitted to journal title message
+\submitto{\NL}
+%
+% Uncomment if a separate title page is required
+%\maketitle
+% 
+% For two-column output uncomment the next line and choose [10pt] rather than [12pt] in the \documentclass declaration
+%\ioptwocol
+%
 
@@
 It was rigorously proven indepedently by \cite{GI2014} and \cite{CS2013} that $\lambda$ decreased at most exponentially --- consistent with \cite{JFM2011}  and \cite{Alberti2014a}.
-The work of \cite{GI2014} relied on PDE regularization results of \cite{Crippa} while the approach of \cite{CS2013} used methods from optimal transportation theory \citep{villani2003topics}.
+The work of \cite{GI2014} relied on PDE regularization results of \cite{Crippa} while the approach of \cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
 
@@
 The authors concluded that shell-model mixing could not surpass length scales given by $\sqrt{\kappa/ \Gamma}$ for enstrophy-constrained flows and $\kappa/U$ for energy-constrained flows up to $O(1)$ constants.
-These length scales can be identified as a generalized Batchelor scale \citep{Batchelor1959a}, introduced in the context of turbulence theory.
+These length scales can be identified as a generalized Batchelor scale \cite{Batchelor1959a}, introduced in the context of turbulence theory.
 
@@
 We can provide a lower bound on $\lambda$ at each instant.
-By apply Gr\"onwall's inequality and the fact that the bracketed term is greater than or equal to zero, it follows from \eqref{eq:length_ineq_rate-of-strain} that
+By apply Gr\"onwall's inequality and the fact that the bracketed term is greater than or equal to zero, it follows from (\ref{eq:length_ineq_rate-of-strain}) that
 %
@@
 %
-\begin{subequations}
-\begin{align}
+\numparts \begin{eqnarray}
 \frac{d}{dt}\left(\frac{\|\nabla\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}\right) &= \frac{\|\theta\|_{L^{2}}^2\frac{d}{dt}\|\nabla\theta\|_{L^{2}}^2-\|\nabla\theta\|_{L^{2}}^2\frac{d}{dt}\|\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^4}\\
@@
 &\leq 2 \frac{\hone{\theta}^2}{\ltwo{\theta}^2}
-\end{align}
-\end{subequations}
+\end{eqnarray} \endnumparts:
 %
@@
 \end{equation}
-Using this with \eqref{eq:exponential_enstrophy}, we find that 
+Using this with (\ref{eq:exponential_enstrophy}), we find that 
 \begin{equation}
@@
 %
-Using H\"older's inequality and \eqref{eq:PDE_advection}, this simplifies to
+Using H\"older's inequality and (\ref{eq:PDE_advection}), this simplifies to
 %
@@
 %
-Using \eqref{eq:k2growth_energy} with  $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, 
+Using (\ref{eq:k2growth_energy}) with  $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, 
 we find that
@@
 %
-Using the above relation with  \eqref{eq:lambda_bound}, we arrive at
+Using the above relation with  (\ref{eq:lambda_bound}), we arrive at
 %
@@
 
-We solve \eqref{eq:nd_ade} by using a Fourier basis to represent the $512 \times 512$ discretized spatial domain with a 4th order Runge-Kutta time-stepping method.
+We solve (\ref{eq:nd_ade}) by using a Fourier basis to represent the $512 \times 512$ discretized spatial domain with a 4th order Runge-Kutta time-stepping method.
 All simulation code was created in the programming language Python with package modules, pyfftw and numpy.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{enstrophy_film}
+\includegraphics[width=\textwidth]{images/enstrophy_film}
 \caption{Local-in-time optimization with enstrophy constraint. Top filmstrip is for $Pe =\infty$ and the bottom filmstrip is $Pe=256$.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{energy_film}
+\includegraphics[width=\textwidth]{images/energy_film}
 \caption{Local-in-time optimization with energy constraint. Top filmstrip is for $Pe = \infty$ and the bottom filmstrip is $Pe=32$.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{enstrophy_norms}
+\includegraphics[width=\textwidth]{images/enstrophy_norms}
 \caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal enstrophy-constrained flow.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{energy_norms}
+\includegraphics[width=\textwidth]{images/energy_norms}
 \caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal energy-constrained flow.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{enstrophy_length}
+\includegraphics[width=\textwidth]{images/enstrophy_length}
 \caption{The left subplot shows the filament length $\lambda$ over time subject to the optimal enstrophy-constrained flow.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{energy_length}
+\includegraphics[width=\textwidth]{images/energy_length}
 \caption{The left subplot shows the filament length $\lambda$ over time subject to the optimal energy-constrained flow.
@@
 \centering
-\includegraphics[width=0.5\textwidth]{enstrophy_rate}
+\includegraphics[width=0.5\textwidth]{images/enstrophy_rate}
 \caption{Mixing rate $r(t)$ over time when subject to the optimal enstrophy-constrained flow.}
@@
 \centering
-\includegraphics[width=\textwidth]{energy_rate}
+\includegraphics[width=\textwidth]{images/energy_rate}
 \caption{The left subplot shows the mixing rate $r(t)$ over time when subject to the optimal energy-constrained flow. The right subplot is the same data except scaled: $r(t)/r_{U} = r(t)/Pe$.}
@@
 
-\bibliographystyle{jfm}
-\bibliography{manuscript}
+\bibliographystyle{unsrt.bst}
+\bibliography{library}
 

### 2017-10-04 flux/create_flux_pbs_script.py

@@ -1,2 +1,113 @@
+import numpy as np
 
-# 
+
+def create_flux_pbs_script(python_file, dict_of_parameter_lists, script_file_name='flux_pbs.sh', jobname='flux_job', procs=1, memory_mb=4000, walltime='6:00:00', email='cmiless@umich.edu'):
+    """ creates a flux pbs script as output to enclosed folder. It will take in a function and lists of parameters to sweep over as input. """
+
+    # create file
+    f = open(script_file_name, 'w')
+
+    # Create PBS preamble and cd commands
+    f.write("""# !/bin/sh
+#### PBS preamble
+
+#PBS -N %s""" % jobname + """
+
+# Your email:
+#PBS -M  %s""" % email + """
+#PBS -m a
+#PBS -V
+
+# Change the number of cores (ppn=1), amount of memory, and walltime:
+#PBS -l procs=%s""" % str(procs) + "," + "pmem=%s" % str(memory_mb) + "mb,walltime=%s" % walltime + """
+
+# Change "example_flux" to the name of your Flux allocation:
+#PBS -A lsa_flux
+#PBS -q flux
+#PBS -l qos=flux
+
+# End PBS preamble
+
+
+#  Show list of CPUs you ran on, if you're running under PBS
+if [ -n "$PBS_NODEFILE" ]; then cat $PBS_NODEFILE; fi
+
+#  Change to the directory you submitted from
+if [ -n "$PBS_O_WORKDIR" ]; then cd $PBS_O_WORKDIR; fi
+
+#  Put your job commands here:
+
+description=("sim_number = $PBS_ARRAYID")
+echo $description
+
+""")
+
+    # Create parameter lists
+    for parameter_name, parameter_list in dict_of_parameter_lists.items():
+        f.write(str(parameter_name) + "_list=(")
+        for parameter in parameter_list:
+            f.write(" " + str(parameter))
+        f.write(" )\n")
+
+    # Create empty argments list and initialize counter
+    f.write("params=()\n")
+    f.write("count=1\n")
+    f.write("\n")
+
+    # create necessary for-loop statements in script file
+    single_indentation = "   "
+    for i, (parameter_name, parameter_list) in enumerate(dict_of_parameter_lists.items()):
+        indentation = single_indentation * i
+        f.write(indentation + "for %s" % parameter_name +
+                " in ${" + parameter_name + "_list[@]}\n")
+        f.write(indentation + "do\n")
+
+    # Write if statement to match run with flux server queue number
[…]

### 2017-10-04 flux/lit_enstrophy.py

@@ -1,72 +1,0 @@
-from integrators import RK4_timestepper, mega_RK4_timestepper, integrator2
-from tools import ScalarTool, create_grid, dt_cfl, N_boyd
-from post_processing import plot_norms, movie
-from operators import OperatorKit
-import numpy as np
-import matplotlib
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-
-import time
-import pickle
-import os
-import sys
-
-if __name__ == "__main__":
-    # Parameters
-    L = 1.0
-    gamma = 1.0
-
-    Pe = float(sys.argv[1])
-    print('Pe = ', Pe)
-    kappa = 1.0 / Pe
-    T = 6.0
-
-    N = int(float(sys.argv[2]))
-
-    print('N = ', N)
-
-    dt0_cfl = 0.25 * dt_cfl(N, L, kappa, gamma * L)
-
-    # Create tool box
-    okit = OperatorKit(N, L, kappa)
-    st = ScalarTool(N, L)
-
-    # Initial condition
-    X = create_grid(N, L)
-    th0 = np.sin((2.0 * np.pi / L) * X[0])
-
-    # Create operators: d th / dt = operator (th)
-    def lit_enstrophy_op(scalar):
-        return okit.lit_enstrophy_op(scalar, gamma)
-
-    def sin_op(scalar):
-        return okit.sin_flow_op(scalar)
-
-    # Perform simulation
-    time_array = np.linspace(0, T, 200)
-
-    th0 = RK4_timestepper(sin_op, th0, dt0_cfl)
-
-    th = integrator2(lit_enstrophy_op, mega_RK4_timestepper,
-                     th0, time_array, dt0_cfl)
-
-    # Output
-    output_folder = 'output-pe=%d' % Pe + '-N=%d' % N + '/'
-    os.system('mkdir ' + output_folder)
-    os.system('cp lit_enstrophy.py ' + output_folder)
-
-    plt.figure()
-    st.plot(th[-1])
-    plt.savefig(output_folder + 'plot_final_frame-pe=%d' %
-                Pe + '-N=%d' % N + '.png')
-
-    plt.figure()
-    plot_norms(time_array, th, N, L)
-    plt.savefig(output_folder + 'plot_norms-pe=%d' % Pe + '-N=%d' % N + '.png')
-
-    movie(time_array, th, N, L, output_path=output_folder)
-
[…]

### 2017-10-04 integrators.py

@@ -1,5 +1,6 @@
 import numpy as np
 import pyfftw
+import pdb
 
 
 def FE_timestepper(op, th0, dt):
@@ -62,6 +63,7 @@ def integrator2(op, timestepper, th0, tarray, dt0_cfl):
             dt = tarray[i] - tarray[i - 1]
             M = np.ceil(dt / dt0_cfl).astype('int') if dt > dt0_cfl else 1
             # print(M)
+            # pdb.set_trace()
             th[i] = timestepper(op, th[i - 1], dt, M)
 
         #print('Time: ', tarray[i])

### 2017-10-04 simulations.py

@@ -2,9 +2,10 @@ from integrators import RK4_timestepper, mega_RK4_timestepper, integrator2, inte
 from tools import create_grid, dt_cfl
 from operators import OperatorKit
 import numpy as np
+import pdb
 
 
-def lit_enstrophy_sim(N, Pe, T, num_time_pts=100, L=1.0, gamma=1.0, cfl=True):
+def lit_enstrophy_sim(N, L, Pe, T, reported_num_time_pts=100,  gamma=1.0, cfl=True):
     kappa = 1.0 / Pe
 
     # Create tool box
@@ -21,11 +22,13 @@ def lit_enstrophy_sim(N, Pe, T, num_time_pts=100, L=1.0, gamma=1.0, cfl=True):
         return okit.sin_flow_op(scalar)
 
     # Perform simulation
-    time_array = np.linspace(0, T, num_time_pts)
+    time_array = np.linspace(0, T, reported_num_time_pts)
 
+    # perform perturbation
     th0 = RK4_timestepper(sin_op, th0, 0.001 * T)
     if cfl is True:
-        dt0_cfl = 0.25 * dt_cfl(N, L, kappa, gamma * L)
+        dt0_cfl = dt_cfl(N, L, kappa, gamma * L)
+        pdb.set_trace()
         th = integrator2(lit_enstrophy_op, mega_RK4_timestepper,
                          th0, time_array, dt0_cfl)
     else:

### 2017-10-04 test/test_simulations.py

@@ -13,7 +13,7 @@ def test_lit_enstrophy_sim():
 
     N_largest = 128  # largest number of modes
 
-    dt_stable_for_N_largest = 0.25 * dt_cfl(N_largest, L, kappa, gamma * L)
+    dt_stable_for_N_largest = dt_cfl(N_largest, L, kappa, gamma * L)
     M_smallest = int(np.ceil(T / dt_stable_for_N_largest))
     # M_smallest = 1
     M_largest = 16 * M_smallest  # largest number of time steps
@@ -22,15 +22,16 @@ def test_lit_enstrophy_sim():
     for N in [N_largest // 16, N_largest // 8, N_largest // 4, N_largest // 2]:
         # print(N)
         sol_N_collection.append(lit_enstrophy_sim(
-            N, Pe, T, M_largest, cfl=False))
+            N, L, Pe, T, M_largest, cfl=False))
 
     sol_M_collection = []
     for M in [M_largest // 16, M_largest // 8, M_largest // 4, M_largest // 2]:
         # print(M)
         sol_M_collection.append(lit_enstrophy_sim(
-            N_largest, Pe, T, M, cfl=False))
+            N_largest, L, Pe, T, M, cfl=False))
 
-    best_solution = lit_enstrophy_sim(N_largest, Pe, T, M_largest, cfl=False)
+    best_solution = lit_enstrophy_sim(
+        N_largest, L, Pe, T, M_largest, cfl=False)
     sol_N_collection.append(best_solution)
     sol_M_collection.append(best_solution)
 

### 2017-10-04 tools.py

@@ -20,10 +20,11 @@ def create_grid(N, L):
 
 
 def dt_cfl(N, L, kappa, U):
+    prefactor = 0.10
     if kappa == 0:
-        dt = L / (N * U)
+        dt = prefactor * L / (N * U)
     else:
-        dt = min(L / (N * U), L**2 / (N**2 * kappa))
+        dt = prefactor * min(L / (N * U), L**2 / (N**2 * kappa))
 
     return dt
 

### 2017-10-04 fluxtools.py
adding new pyton files

@@ -1,0 +1,171 @@
+import numpy as np
+import os
+import sys
+
+
+def create_flux_pbs_script(path_to_place_pbs_script, script_file_name, python_file, dict_of_parameter_lists, jobname='flux_job', procs=1, memory_mb=4000, walltime='6:00:00', email='cmiless@umich.edu'):
+    """ creates a flux pbs script as output to enclosed folder. It will take in a function and lists of parameters to sweep over as input. """
+
+    # create file
+    f = open(path_to_place_pbs_script + script_file_name, 'w')
+
+    # Create PBS preamble and cd commands
+    f.write("""# !/bin/sh
+#### PBS preamble
+
+#PBS -N %s""" % jobname + """
+
+# Your email:
+#PBS -M  %s""" % email + """
+#PBS -m a
+#PBS -V
+
+# Change the number of cores (ppn=1), amount of memory, and walltime:
+#PBS -l procs=%s""" % str(procs) + "," + "pmem=%s" % str(memory_mb) + "mb,walltime=%s" % walltime + """
+
+# Change "example_flux" to the name of your Flux allocation:
+#PBS -A lsa_flux
+#PBS -q flux
+#PBS -l qos=flux
+
+# End PBS preamble
+
+
+#  Show list of CPUs you ran on, if you're running under PBS
+if [ -n "$PBS_NODEFILE" ]; then cat $PBS_NODEFILE; fi
+
+#  Change to the directory you submitted from
+if [ -n "$PBS_O_WORKDIR" ]; then cd $PBS_O_WORKDIR; fi
+
+#  Put your job commands here:
+
+description=("sim_number = $PBS_ARRAYID")
+echo $description
+
+""")
+
+    # Create parameter lists
+    for parameter_name, parameter_list in dict_of_parameter_lists.items():
+        f.write(str(parameter_name) + "_list=(")
+        for parameter in parameter_list:
+            f.write(" " + str(parameter))
+        f.write(" )\n")
+
+    # Create empty argments list and initialize counter
+    f.write("params=()\n")
+    f.write("count=1\n")
+    f.write("\n")
+
+    # create necessary for-loop statements in script file
+    single_indentation = "   "
+    for i, (parameter_name, parameter_list) in enumerate(dict_of_parameter_lists.items()):
+        indentation = single_indentation * i
+        f.write(indentation + "for %s" % parameter_name +
+                " in ${" + parameter_name + "_list[@]}\n")
+        f.write(indentation + "do\n")
+
[…]

### 2017-10-04 lit_enstrophy.py

@@ -1,0 +1,52 @@
+from simulations import lit_enstrophy_sim
+from integrators import RK4_timestepper, mega_RK4_timestepper, integrator2
+from tools import ScalarTool, create_grid, dt_cfl, N_boyd
+from post_processing import plot_norms, movie
+from operators import OperatorKit
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import pdb
+
+import time
+import pickle
+import os
+import sys
+
+if __name__ == "__main__":
+    Pe = float(sys.argv[1])
+    N = int(float(sys.argv[2]))
+    M = int(float(sys.argv[2]))
+
+    # Parameters
+    L = 1.0
+    gamma = 1.0
+    T = 6.0
+    kappa = 1.0 / Pe
+
+    print('Pe = ', Pe)
+    print('N = ', N)
+
+    [time_array, th] = lit_enstrophy_sim(N, L, Pe, T, M, cfl=True)
+
+    # Output
+    output_folder = 'output-pe=%d' % Pe + '-N=%d' % N + '/'
+    os.system('mkdir ' + output_folder)
+    os.system('cp lit_enstrophy.py ' + output_folder)
+
+    plt.figure()
+    st = ScalarTool(N, L)
+    st.plot(th[-1])
+    plt.savefig(output_folder + 'plot_final_frame-pe=%d' %
+                Pe + '-N=%d' % N + '.png')
+
+    plt.figure()
+    plot_norms(time_array, th, N, L)
+    plt.savefig(output_folder + 'plot_norms-pe=%d' % Pe + '-N=%d' % N + '.png')
+
+    movie(time_array, th, N, L, output_path=output_folder)
+
+    output = open(output_folder + 'pe=%d' % Pe + '-N=%d' % N + '.pkl', 'wb')
+    pickle.dump([time_array, th], output)
+    output.close()

### 2017-10-04 run_simulations_on_flux.py
adding new pyton files

@@ -1,0 +1,12 @@
+import fluxtools
+from simulations import lit_enstrophy_sim
+
+if __name__ == "__main__":
+    python_file = 'lit_enstrophy.py'
+    flux_folder_name = 'lit_enstrophy/'
+    dict_of_parameter_lists = {'Pe': [8.0, 16.0, 32.0, 64.0, 128.0, 256.0,
+                                      512.0, 1024.0, 2048.0, 4096.0, 8192.0, 16384.0],
+                               'N': [64, 128, 256, 512]}
+
+    fluxtools.run_python_file(
+        python_file, dict_of_parameter_lists, flux_folder_name)

### 2017-10-04 nonlinearity/manuscript.tex
finished charlies revisions to abstract

@@
 Incompressible flows can be effective mixers by appropriately advecting a passive tracer to produce small filamentation length scales.
-The Batchelor length scale \cite{Batchelor1959a} was proposed as thelower limit of length scales achievable in turbulent flows.
+The Batchelor length scale \cite{Batchelor1959a} was proposed as the lower limit of length scales achievable in turbulent flows.
 Here, we provide numerical evidence that this limitation may be even more general, applying as well to all incompressible flows under mild physical constraints such as bounded enstrophy or energy.
 We consider local-in-time flow optimization under these flow intensity constraints with the objective of maximizing mixing rate performance.
-For enstrophy-bounded optimal flows, we find that the strength of diffusion has no impact on the long-term mixing rate performance.
-For energy-constrained optimal flows, we find that an increase in the strength of diffusion worsens this performance.
+We observe that, for enstrophy-bounded optimal flows, the strength of diffusion has no impact on the long-term mixing rate performance.
+For energy-constrained optimal flows, however an increase in the strength of diffusion decreases the mixing rate.
 We provide analytical lower bounds on mixing rates and length scales achievable under related constraints (pointwise bounded speed and rate-of-strain) by extending the work of \cite{JFM2011} and \cite{Chi-Cheu1996}.

### 2017-10-04 nonlinearity/manuscript.tex
made charlies corrections to introduction

@@
 \end{abstract}
-
-% Uncomment for PACS numbers
-\pacs{00.00, 20.00, 42.10}
+%
+\pacs{47.85.lk, 47.85.L-, 42.10, 47.57.eb}
+\ams{76R50, 37A25, 76F25, 76D55}
 %
@@
 \vspace{2pc}
-\noindent{\it Keywords}: Optimal mixing, incompressible flow, diffusion, Batchelor scale
+\noindent{\it Keywords}: Mixing, incompressible flow, diffusion processes, flow control and optimization, Batchelor scale
 
@@
 
-Optimal mixing is important to many areas of science and engineering.
+Mixing a passive tracer concentration via an incompressible fluid flow is important to many areas of science and engineering.
 A question of interest across these domains is ``How can one stir to enhance the rate of mixing?'' We explore this question and study the impact of molecular diffusion.
@@
 This assumption is used today throughout the computational fluid dynamics community to provide a heuristic for the grid resolutions necessary.
-Thus, we believe it is imperative to determine what conditions on $\mathbf{u}$ are necessary to justify this assumption.
+Thus, it is important to determine what conditions on $\mathbf{u}$ are necessary to justify this assumption.
 

### 2017-10-04 nonlinearity/manuscript.tex
made charlies corrections to subsection on Linfinity rate-of-strain flow analysis

@@
 We consider a subset of $L^{2}$ constrained flows --- those belonging to $L^{\infty}$.
-Quantities of rate-of-strain and speed are bounded point-wise uniformly in space and time rather than demanding that they be $L^2$ integrable as before.
+In this restricted setting the rate-of-strain and speed are bounded point-wise uniformly in space and time rather than demanding that they merely be $L^2$ integrable as before.
 We will provide bounds on $\lambda$ and measures of mixing in this restricted setting.
@@
 
-Taking the time derivative of $\lambda^2$, we find
+The time derivative of $\lambda^2$ is
 %
@@
 							\nabla^{-1}\theta  }}
-					  {\ltwo{\theta}^{2}}.
+					  {\ltwo{\theta}^{2}}
 \end{equation}
-By H\"older's inequality, we have that
+and by H\"older's inequality, we deduce
 \begin{equation}
@@
 \end{equation}
-We can provide a lower bound on $\lambda$ at each instant.
-By apply Gr\"onwall's inequality and the fact that the bracketed term is greater than or equal to zero, it follows from (\ref{eq:length_ineq_rate-of-strain}) that
+This establishes a lower bound on $\lambda$ at each instant: by apply Gr\"onwall's inequality and the fact that the bracketed term is greater than or equal to zero, it follows that
 %
@@
 %
-Therefore, perfect mixing in finite time is impossible.
+Therefore, perfect mixing in finite time is impossible for bounded rate-of-strain flows.
 
-One can show that 
+Furthermore,
 %
@@
 &\leq 2 \frac{\hone{\theta}^2}{\ltwo{\theta}^2}
-\end{eqnarray} \endnumparts:
+\end{eqnarray} \endnumparts
 %
-From $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, one finds that 
+and using $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, it follows that
 \begin{equation}
-\ltwo{\theta}\geq  \ltwo{\theta_{0}}\exp\left[-\frac{1}{2Pe}\frac{\hone{\theta_{0}}^2}{\ltwo{\theta_{0}}^2}\left(e^{2 t} -1\right)\right]
+\ltwo{\theta}\geq  \ltwo{\theta_{0}}\exp\left[-\frac{1}{2Pe}\frac{\hone{\theta_{0}}^2}{\ltwo{\theta_{0}}^2}\left(e^{2 t} -1\right)\right].
 \end{equation}

### 2017-10-04 nonlinearity/manuscript.tex
made charlies revisions to subsection Linfinity speed limited flow constraint analysis

@@
 Here, we provide numerical evidence that this limitation may be even more general, applying as well to all incompressible flows under mild physical constraints such as bounded enstrophy or energy.
-We consider local-in-time flow optimization under these flow intensity constraints with the objective of maximizing mixing rate performance.
+We consider local-in-time flow optimisation under these flow intensity constraints with the objective of maximising mixing rate performance.
 We observe that, for enstrophy-bounded optimal flows, the strength of diffusion has no impact on the long-term mixing rate performance.
 For energy-constrained optimal flows, however an increase in the strength of diffusion decreases the mixing rate.
-We provide analytical lower bounds on mixing rates and length scales achievable under related constraints (pointwise bounded speed and rate-of-strain) by extending the work of \cite{JFM2011} and \cite{Chi-Cheu1996}.
+We provide analytical lower bounds on mixing rates and length scales achievable under related constraints (point-wise bounded speed and rate-of-strain) by extending the work of \cite{JFM2011} and \cite{Chi-Cheu1996}.
 
@@
 \vspace{2pc}
-\noindent{\it Keywords}: Mixing, incompressible flow, diffusion processes, flow control and optimization, Batchelor scale
+\noindent{\it Keywords}: Mixing, incompressible flow, diffusion processes, flow control and optimisation, Batchelor scale
 
@@
 The flow is constrained by enstrophy $\ltwo{\nabla\u} = \Gamma L^{d/2}$ or energy $\ltwo{\u} = UL^{d/2}$ where $\Gamma$ is the root mean square rate-of-strain and $U$ is the root mean square speed.
-We primarily use the $H^{-1}$ norm or mix-norm throughout to measure homogenization,
+We primarily use the $H^{-1}$ norm or mix-norm throughout to measure homogenisation,
 
@@
 Lower values of the  $H^{-1}$ norm corresponds to a more mixed state.
-Note that $H^{-1}$ norm can decrease in two ways: either by decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ or by advecting the flow such that the tracer concentration acquires more spectral mass in the higher wavenumbers and takes advantage of the $1/|\vec{k}|^2$ dependence.
+Note that $H^{-1}$ norm can decrease in two ways: either by decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ or by advecting the flow such that the tracer concentration acquires more spectral mass in the higher wave numbers and takes advantage of the $1/|\vec{k}|^2$ dependence.
 We use the $H^{-1}$ norm to define the (exponential) rate of mixing as
@@
 \end{equation}
-Note that $\lambda(t)$ returns the wavelength of the wavenumber $\vec{k}$ for a tracer concentration field composed only of the Fourier mode with wavenumber $\vec{k}$ (i.e.
+Note that $\lambda(t)$ returns the wavelength of the wave number $\vec{k}$ for a tracer concentration field composed only of the Fourier mode with wave number $\vec{k}$ (i.e.
 $\theta(\vec{x},t) = Re[ A e^{-i\vec{k}\cdot \vec{x}}]$ where $A$ is a complex constant).
@@
 For the enstrophy-bounded flow problem, we choose the same length scale $L$, the velocity scale $L\Gamma $, and  the time scale $1/\Gamma$.
-For the energy-bounded flow problem, we non-dimensionalize the system by choosing $L$ as the length scale, $U$ as the velocity scale, and $L/U$ as the time scale.
+For the energy-bounded flow problem, we non-dimensionalise the system by choosing $L$ as the length scale, $U$ as the velocity scale, and $L/U$ as the time scale.
 Both scalings produce the following form of the advection-diffusion equation,
@@
 We will first review results for the $Pe = \infty$ enstrophy-constrained case.
-\cite{JFM2011} showed numerical evidence that the filament width $\lambda$ seemingly decreased continually by instanateous flow optimization.
-This type of optimization will be considered in this work as well.
-Self-similar flows can realize a decreasing $\lambda$ over time as shown analytically by \cite{Alberti2014a}.
-It was rigorously proven indepedently by \cite{GI2014} and \cite{CS2013} that $\lambda$ decreased at most exponentially --- consistent with \cite{JFM2011}  and \cite{Alberti2014a}.
-The work of \cite{GI2014} relied on PDE regularization results of \cite{Crippa} while the approach of \cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
+\cite{JFM2011} showed numerical evidence that the filament width $\lambda$ seemingly decreased continually by instantaneous flow optimisation.
+This type of optimisation will be considered in this work as well.
+Self-similar flows can realise a decreasing $\lambda$ over time as shown analytically by \cite{Alberti2014a}.
+It was rigorously proven independently by \cite{GI2014} and \cite{CS2013} that $\lambda$ decreased at most exponentially --- consistent with \cite{JFM2011}  and \cite{Alberti2014a}.
+The work of \cite{GI2014} relied on PDE regularisation results of \cite{Crippa} while the approach of \cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
 
-For $Pe = \infty$ energy-constrained problem, \cite{JMP2012} showed that a `checkerboard' flow can also provide continually decreasing length scales.
+For $Pe = \infty$ energy-constrained problem, \cite{JMP2012} showed that a `chequerboard' flow can also provide continually decreasing length scales.
 Moreover, $\lambda$ decreased at a fast enough rate to approach zero in finite time in contrast to the enstrophy-constrained problem where $\lambda$ decreases to zero in infinite time.
@@
 The inclusion of diffusion ($Pe <\infty$) with the objective of optimal mixing has been explored.
-\cite{DF2014} investigated optimal mixing and study the evolution of the mentioned measures ($H^{-1}, L^2,$ and $H^1$ norms) of mixing under the checkerboard flow introduced by \cite{JMP2012}.
+\cite{DF2014} investigated optimal mixing and study the evolution of the mentioned measures ($H^{-1}, L^2,$ and $H^1$ norms) of mixing under the chequerboard flow introduced by \cite{JMP2012}.
 They show that the $H^{-1}$ and $L^2$ norms decrease monotonically under this flow while the $H^{1}$ increases until it reaches a peak and then decreases.
@@
 The authors concluded that shell-model mixing could not surpass length scales given by $\sqrt{\kappa/ \Gamma}$ for enstrophy-constrained flows and $\kappa/U$ for energy-constrained flows up to $O(1)$ constants.
-These length scales can be identified as a generalized Batchelor scale \cite{Batchelor1959a}, introduced in the context of turbulence theory.
+These length scales can be identified as a generalised Batchelor scale \cite{Batchelor1959a}, introduced in the context of turbulence theory.
 
@@
 We show numerical evidence that $\lambda$ appears to be limited by the Batchelor scale as seen in the shell model.
-Even when actively trying to choose the most optimal flow to minimize filimentation length.
+Even when actively trying to choose the most optimal flow to minimise filamentation length.
 Thus, this may suggest that the Batchelor scale does not only limit turbulent flows but also all incompressible flows under the flow constraints considered here.
@@
 
-The paper is organized as follows.
-We introduce the necessary theory regarding local-in-time optimization, a shell model, and $L^{\infty}$ flow constraints in section \ref{sec:theory}.
-Section \ref{sec:numerical_experiment} details the methodology and results of numerically implementing local-in-time flow optimization.
+The paper is organised as follows.
+We introduce the necessary theory regarding local-in-time optimisation, a shell model, and $L^{\infty}$ flow constraints in section \ref{sec:theory}.
+Section \ref{sec:numerical_experiment} details the methodology and results of numerically implementing local-in-time flow optimisation.
 Lastly, we finish with a discussion and conclusion in sections \ref{sec:discussion} and \ref{sec:conclusion} respectively.
@@
 \label{sec:theory}
-\subsection{Local-in-time optimization}
-We consider the local-in-time optimization strategy first introduced by \cite{JFM2011} in the diffusion-less case.
-We find that this strategy generalizes to the case with diffusion.
-The local-in-time optimal velocity fields maximize the instantaneous mixing rate by minimizing $\ddt{}\hmone{\theta}^2$ or equivalently minimizing $\ddt{\lambda^2}$ .
+\subsection{Local-in-time optimisation}
+We consider the local-in-time optimisation strategy first introduced by \cite{JFM2011} in the diffusion-less case.
+We find that this strategy generalises to the case with diffusion.
+The local-in-time optimal velocity fields maximise the instantaneous mixing rate by minimising $\ddt{}\hmone{\theta}^2$ or equivalently minimising $\ddt{\lambda^2}$ .
 The optimal velocity fields are given instantaneously by (in non-dimensional form)
@@
 
-\subsection{Shell model predictions of local-in-time optimization}
+\subsection{Shell model predictions of local-in-time optimisation}
 
 The shell model is a reduced model of the spectral dynamics present in the advection-diffusion equation.
-The model consists of a system of ordinary differential equations with nearest-neighboring coupling between `shells' in wavenumber space.
-\cite{Miles2017a} performed local-in-time mixing optimization in this model.
-The shell-model analysis predicts a limiting length scale given by the Batchelor scale, $\Lambda_{\Gamma} =\sqrt{\frac{\kappa}{\Gamma}}$  and its generalization $\Lambda_{U}= \frac{U}{\kappa} $.
+The model consists of a system of ordinary differential equations with nearest-neighbour coupling between `shells' in wave number space.
+\cite{Miles2017a} performed local-in-time mixing optimisation in this model.
+The shell-model analysis predicts a limiting length scale given by the Batchelor scale, $\Lambda_{\Gamma} =\sqrt{\frac{\kappa}{\Gamma}}$  and its generalisation $\Lambda_{U}= \frac{U}{\kappa} $.
 The non-dimensional versions are given by $\lambda_{\Gamma}= \frac{1}{\sqrt{Pe}}$ and $\lambda_{U} = \frac{1}{Pe}$.
-Also from here forward, we will refer to the Batchelor scale to mean either $\lambda_{\Gamma}$ or its generalization $\lambda_{U}$.
+Also from here forward, we will refer to the Batchelor scale to mean either $\lambda_{\Gamma}$ or its generalisation $\lambda_{U}$.
 The predicted long-term rates (after reaching the Batchelor scale) are given by $R_{\Gamma} =\kappa/\lambda_{\Gamma}^2 $  and  $R_{U}=\kappa/\lambda_{U}^2$  The non-dimensional versions are given by $r_{\Gamma} =1$ and $r_{U} = Pe $.
@@
 \end{equation}
-Using this with (\ref{eq:exponential_enstrophy}), we find that 
+Using this with (\ref{eq:exponential_enstrophy}), we deduce the lower bound
 \begin{equation}
-\hmone{\theta} \geq  \hmone{\theta_{0}} \exp\left[- t -\frac{1}{2 Pe}\frac{\hone{\theta_{0}}^2}{\ltwo{\theta_{0}}}\left(e^{2 t} -1\right)\right]
+\hmone{\theta} \geq  \hmone{\theta_{0}} \exp\left[- t -\frac{1}{2 Pe}\frac{\hone{\theta_{0}}^2}{\ltwo{\theta_{0}}}\left(e^{2 t} -1\right)\right].
 \end{equation}
@@
 \subsubsection{Results for $\linf{\u}= 1$}
-Here we extend the results first introduced by \cite{Chi-Cheu1996}.  It is first useful to express the following quantities as:
+Here we extend the result of \cite{Chi-Cheu1996} to show that the presence of diffusion rules out perfect mixing in finite time for bounded velocity flows.  First note that
 %
@@
 	 									+\frac{1}{Pe}\lap \theta\right)} 
-\end{eqnarray}
+\end{eqnarray},
 %
@@
 	 									+\frac{1}{Pe}\lap \theta\right)} 
-\end{eqnarray}
+\end{eqnarray},
+%
+and
 %
@@
 
-We then compute the following derivative:
+Then compute:
 %
@@
 \end{eqnarray*}
-By applying H\"older's inequality again, we have
+Again applying H\"older's inequality we have
 \begin{equation}
@@
 		Pe
-		\frac{\hone{\theta}^2}{\ltwo{\theta}^2} .
+		\frac{\hone{\theta}^2}{\ltwo{\theta}^2} 
 \end{equation}
 %
-Thus, we find that 
+and thus 
 %
@@
 		\frac{\hone{\theta_0}}{\ltwo{\theta_0}}
-		\exp{\pbrac{\frac{Pe}{2} t}}
+		\exp{\pbrac{\frac{Pe}{2} t}}.
 \end{equation}
 %
-Using the inequality $\hone{\theta}\hmone{\theta}\geq \ltwo{\theta}^2$, we know that 
+The inequality $\hone{\theta}\hmone{\theta}\geq \ltwo{\theta}^2$ then ensures that
 %
@@
 %
-Using (\ref{eq:k2growth_energy}) with  $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, 
-we find that
+Using (\ref{eq:k2growth_energy}) together with  $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$ we observe that
 %
@@
 %
-Using the above relation with  (\ref{eq:lambda_bound}), we arrive at
+and this combined with  (\ref{eq:lambda_bound}) implies
 %
 \begin{equation}
-\hmone{\theta}\geq \frac{\ltwo{\theta_{0}}^2}{\hone{\theta_0}}\exp\left[-\frac{Pe}{2} \,\, t-\frac{1}{Pe^2}\frac{\hone{\theta_0}^2}{\ltwo{\theta_0}^2}\left(e^{Pe \,\, t}-1\right)\right]
+\hmone{\theta}\geq \frac{\ltwo{\theta_{0}}^2}{\hone{\theta_0}}\exp\left[-\frac{Pe}{2} \,\, t-\frac{1}{Pe^2}\frac{\hone{\theta_0}^2}{\ltwo{\theta_0}^2}\left(e^{Pe \,\, t}-1\right)\right].
 \end{equation}
@@
 %
-\section{Numerical experiment: local-in-time optimization}
+\section{Numerical experiment: local-in-time optimisation}
 \label{sec:numerical_experiment}
@@
 
-We solve (\ref{eq:nd_ade}) by using a Fourier basis to represent the $512 \times 512$ discretized spatial domain with a 4th order Runge-Kutta time-stepping method.
+We solve (\ref{eq:nd_ade}) by using a Fourier basis to represent the $512 \times 512$ discretised spatial domain with a 4th order Runge-Kutta time-stepping method.
 All simulation code was created in the programming language Python with package modules, pyfftw and numpy.
@@
 \includegraphics[width=\textwidth]{images/enstrophy_film}
-\caption{Local-in-time optimization with enstrophy constraint. Top filmstrip is for $Pe =\infty$ and the bottom filmstrip is $Pe=256$.}
+\caption{Local-in-time optimisation with enstrophy constraint.
+Top filmstrip is for $Pe =\infty$ and the bottom filmstrip is $Pe=256$.
+Note that the grey-scale for the $Pe=\infty$ is constant in time while it is adjusted to show the tracer concentration structure in the finite $Pe$ case.
+}
 \label{fig:enstrophy_film}
@@
 \includegraphics[width=\textwidth]{images/energy_film}
-\caption{Local-in-time optimization with energy constraint. Top filmstrip is for $Pe = \infty$ and the bottom filmstrip is $Pe=32$.}
+\caption{Local-in-time optimisation with energy constraint.
+Top filmstrip is for $Pe = \infty$ and the bottom filmstrip is $Pe=32$.
+Note that the grey-scale for the $Pe=\infty$ is constant in time while it is adjusted to show the tracer concentration structure in the finite $Pe$ case.
+}
 \label{fig:energy_film}
@@
 \includegraphics[width=\textwidth]{images/enstrophy_norms}
-\caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal enstrophy-constrained flow.}
+\caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal enstrophy-constrained flow.  }
 \label{fig:enstrophy_norms}
@@
 The rate during the transient phase is $\Gamma$ which is consistent with rates expected from $Pe=\infty$ mixing studies.
-For all $Pe$ considered, there is an increase in the rate of mixing after transient behavior has finished to a long-term rate.
+For all $Pe$ considered, there is an increase in the rate of mixing after transient behaviour has finished to a long-term rate.
 Surprisingly, this long-term mixing rate appears to be independent of $Pe$ for fixed enstrophy.
@@
 We expect the critical transition time $t_{c}$ that marks the end of this transient period to satisfy $\lambda(t_{c})= \lambda_{\Gamma}$.
-This time is theorized to be $t_{c}=\frac{1}{\alpha}\ln(\lambda(0)/\lambda_{\Gamma}) = \frac{1}{\alpha}\ln ( \sqrt{Pe} )$ for $Pe>1$ (If $Pe \leq 1$, then there is no transient phase).
+This time is theorised to be $t_{c}=\frac{1}{\alpha}\ln(\lambda(0)/\lambda_{\Gamma}) = \frac{1}{\alpha}\ln ( \sqrt{Pe} )$ for $Pe>1$ (If $Pe \leq 1$, then there is no transient phase).
 Hence, a smaller value of $Pe$ will result in an earlier onset of the long-term rate of mixing.
@@
 Thus, the long-term mixing rate is proportional to $Pe$ in contrast to the long-term mixing rate of enstrophy which carries no dependence on $Pe$.
-For the enstrophy case, we saw a benefit of picking a lower $Pe$ to result in a earlier onset of the long-term mixing behavior.
+For the enstrophy case, we saw a benefit of picking a lower $Pe$ to result in a earlier onset of the long-term mixing behaviour.
 The fixed energy case however is different.
-The onset of the long run-mixing behavior can be determined by the following model.
+The onset of the long run-mixing behaviour can be determined by the following model.
 From the work of \cite{JMP2012} on the fixed energy case, $\lambda(t)$ can decrease linearly in time to produce perfect mixing in finite time.
 We model the transient phase as $\lambda(t)=\lambda(0)(1-\beta t)$.
-Therefore, we theorize that the critical transition time is $t_{c}=\frac{1}{\beta}(1 -\lambda_{U}/\lambda(0)) = \frac{1}{\beta}(1 - 1/Pe)$ with $Pe> 1$ (If $Pe \leq 1$, there is not transient phase) for the energy case.
-Thus, it is true that on can still achieve an earlier onset of the long-term mixing behavior by choosing a smaller $Pe$.
+Therefore, we theorise that the critical transition time is $t_{c}=\frac{1}{\beta}(1 -\lambda_{U}/\lambda(0)) = \frac{1}{\beta}(1 - 1/Pe)$ with $Pe> 1$ (If $Pe \leq 1$, there is not transient phase) for the energy case.
+Thus, it is true that on can still achieve an earlier onset of the long-term mixing behaviour by choosing a smaller $Pe$.
 However, an earlier onset time is accompanied by a slower long-term mixing rate.
@@
 This benefit is well illustrated by $H^{-1}$ norm in figure \ref{fig:energy_norms}.
-Notice that the mixing rate is initially slow for $Pe = 512$ but then outcompetes the mixing rate of smaller values of $Pe$.
+Notice that the mixing rate is initially slow for $Pe = 512$ but then out competes the mixing rate of smaller values of $Pe$.
 
@@
 \label{sec:discussion}
-The local-in-time optimization results suggest that there is a limiting length scale and rate.
+The local-in-time optimisation results suggest that there is a limiting length scale and rate.
 The bounds derived, under the $L^{\infty}$ constrained flow assumption, did not result in proving either of these observations.
@@
 
-In future work, we would like to consider the optimal control problem coined global-in-time optimization which tries to minimize the filamentation width at the end time rather than instantaneously attempting to minimize its decay rate.
+In future work, we would like to consider the optimal control problem coined global-in-time optimisation which tries to minimise the filamentation width at the end time rather than instantaneously attempting to minimise its decay rate.
 This may lead to flows that are able to extend to even smaller length scales.
-This global-in-time optimization has been explored in the work of \cite{Miles2017a} within the context of the shell model.
-The authors showed that global-in-time and local-in-time optimization appeared to give similar mixing rates.
+This global-in-time optimisation has been explored in the work of \cite{Miles2017a} within the context of the shell model.
+The authors showed that global-in-time and local-in-time optimisation appeared to give similar mixing rates.
 
@@
 
-Our numerical study of local-in-time optimization suggests that there is a limiting length scale given by a generalized Batchelor length scale which in turn determines a long-term mixing Batchelor rate.
-Although the Batchelor scale has been a theorized lower bound on the length scales present on turbulent flows, it has not been shown rigorously.
+Our numerical study of local-in-time optimisation suggests that there is a limiting length scale given by a generalised Batchelor length scale which in turn determines a long-term mixing Batchelor rate.
+Although the Batchelor scale has been a theorised lower bound on the length scales present on turbulent flows, it has not been shown rigorously.
 We hope this numerical study provides insight and promotes investigation into proving what conditions are necessary on the flow for this to be the case.

### 2017-10-05 nonlinearity/manuscript.tex
added charlies revisions to results section

@@
 Notice how they plateau around an $O(1)$ constant.
-Thus, this result is consistent with the shell-model predictions.
+Thus this result is consistent with the shell-model predictions.
 
@@
 For all $Pe$ considered, there is an increase in the rate of mixing after transient behaviour has finished to a long-term rate.
-Surprisingly, this long-term mixing rate appears to be independent of $Pe$ for fixed enstrophy.
-{\it Thus, this implies that the long-term rate of mixing is only dependent on the rate-of-strain $\Gamma$ and not influenced by the strength of diffusion.
-}Although, it should be noted that the onset of the long-term rate is affected by the value of $Pe$.
-When there is strong diffusion (small $Pe$), the Batchelor scale is reached early.
-From the work of \cite{GI2014} and \cite{CS2013}, $\lambda$ decreases at most exponentially for $Pe = \infty$.
-If we assume that the local-in-time flows nearly saturate this bound in the transient phase, we model $\lambda$ as  $\lambda (t) = \lambda(0)\exp(- \alpha t) $ during this time.
+Perhaps surprisingly, this long-term mixing rate appears to be {\it independent} of $Pe$ for fixed enstrophy.
+This suggests that the optimal long-term rate of mixing is only dependent on the rate-of-strain $\Gamma$ and not influenced by the strength of diffusion.
+
+Although it should be noted that the onset of the long-term rate is affected by the value of $Pe$.
+When there is strong diffusion (small $Pe$), the Batchelor scale is reached quickly.
+From the work of \cite{GI2014} and \cite{CS2013}, we know that $\lambda$ decreases at most exponentially for $Pe = \infty$.
+If we assume that the local-in-time optimal flows nearly saturate this bound in the transient phase, we model $\lambda$ as  $\lambda (t) = \lambda(0)\exp(- \alpha t) $ during this time.
 We expect the critical transition time $t_{c}$ that marks the end of this transient period to satisfy $\lambda(t_{c})= \lambda_{\Gamma}$.
@@
 Thus, the long-term mixing rate is proportional to $Pe$ in contrast to the long-term mixing rate of enstrophy which carries no dependence on $Pe$.
+
  For the enstrophy case, we saw a benefit of picking a lower $Pe$ to result in a earlier onset of the long-term mixing behaviour.

### 2017-10-05 nonlinearity/manuscript.tex
finished revisoins on discussion

@@
 Lastly, we finish with a discussion and conclusion in sections \ref{sec:discussion} and \ref{sec:conclusion} respectively.
+
+%%%
+%%%
+%%% THEORY
+%%%
+%%%
 
@@
 
+%%%
+%%%
+%%% RESULTS
+%%%
+%%%
+
 \subsection{Results}
@@
 
-% Figures \ref{fig:enstrophy_norms} and \ref{fig:energy_norms} show the evolution the  $H^{-1}$,  $L^{2}$, and $H^{1}$ norms for different values of finite $Pe$.
+%%%
+%%%
+%%% DISCUSSION 
+%%%
+%%%
 
@@
 \label{sec:discussion}
-The local-in-time optimisation results suggest that there is a limiting length scale and rate.
-The bounds derived, under the $L^{\infty}$ constrained flow assumption, did not result in proving either of these observations.
-However, they did definitively rule out the possibility of perfect mixing in finite time in either constraint.
-We believe these bounds could be drastically improved.
-We surmise that the deficiencies in these bounds is due to not fully exploiting the incompressibility condition.
+The local-in-time optimisation results suggest that there is a limiting length scale for passive tracer mixing whenever flows are optimised to decrease the mix-norm.
+The bounds derived under the $L^{\infty}$ constrained flow assumption did not result in proving either of these observations, but they did definitively rule out the possibility of perfect mixing in finite time for either constraint.
+These bounds could be drastically improved: we surmise that the deficiencies in these analyses may be due to not fully exploiting the incompressibility condition in the estimates.
 It remains to be shown that $\liminf_{t\rightarrow \infty} \lambda (t)\geq C\lambda_{\Gamma}$ where C is constant dependent on domain and initial condition under an enstrophy constrained flow.
 A similar problem remains open for the fixed energy case.
-If these statements are shown, then many of the results demonstrated here numerically will hold more generally.
+If these statements can be shown, then many of the results demonstrated here computationally will hold more generally.
 
-In future work, we would like to consider the optimal control problem coined global-in-time optimisation which tries to minimise the filamentation width at the end time rather than instantaneously attempting to minimise its decay rate.
-This may lead to flows that are able to extend to even smaller length scales.
-This global-in-time optimisation has been explored in the work of \cite{Miles2017a} within the context of the shell model.
-The authors showed that global-in-time and local-in-time optimisation appeared to give similar mixing rates.
+In future work, we would like to consider the optimal control problem with finite-time optimisation to minimise the filamentation width at the end time rather than instantaneously attempting to minimise its decay rate.
+This might lead to flows that are able to extend to even smaller length scales.
+Finite-time optimisation was explored in \cite{Miles2017a} in the context of the shell model where it was found that global-in-time and local-in-time optimisation appeared to give similar mixing rates.
+Fore the shell model, however, the analysis was consistent with computation.
+In the PDE case the gap between analysis and computation remains to be closed.
+
+%%%
+%%%
+%%% CONCLUSION
+%%%
+%%%
 

### 2017-10-05 nonlinearity/manuscript.tex
finished with conclusion and acknoledgments. All revisions provided from charlie have been taken care of with the exception of adding a comment about Christian Seiss observation about the rate being dependent on the initial condition

@@
 
-Our numerical study of local-in-time optimisation suggests that there is a limiting length scale given by a generalised Batchelor length scale which in turn determines a long-term mixing Batchelor rate.
+Our numerical study of local-in-time optimisation suggests that there is a limiting length scale, a generalised Batchelor length scale, which in turn determines a long-term mixing ``Batchelor rate".
 Although the Batchelor scale has been a theorised lower bound on the length scales present on turbulent flows, it has not been shown rigorously.
@@
 \section*{Acknowledgements}
-
+We gratefully acknowledge helpful comments from Hongjie Done, Luis Escauriaza, Guatum Iyer, Alexander Kiselev, Anna Mazzucato, Christian Seis, Ian Tobasco, and Karen Zaya.
 This work was supported in part by NSF Awards PHY-1205219 and DMS-1515161.
 One of us (CRD) is additionally grateful for Fellowship funding from the John Simon Guggenheim Memorial Foundation.
-We are appreciative of the valuable feedback provided by Guatum Iyer, Alexander Kiselev, Ian Tobasco, and Karen Zaya.
 

### 2017-10-10 nonlinearity/manuscript.tex
rewrote introduction

@@
 
-\author{C J Miles$^{1,2,3}$ and C R Doering$^{1,2,3}$ }
+\author{Christopher J. Miles$^{1,2,3}$ and Charles R. Doering$^{1,2,3}$ }
 
@@
 \begin{indented}
-\item[]February 2014
+\item[]\today
 \end{indented}
@@
 Incompressible flows can be effective mixers by appropriately advecting a passive tracer to produce small filamentation length scales.
-The Batchelor length scale \cite{Batchelor1959a} was proposed as the lower limit of length scales achievable in turbulent flows.
-Here, we provide numerical evidence that this limitation may be even more general, applying as well to all incompressible flows under mild physical constraints such as bounded enstrophy or energy.
-We consider local-in-time flow optimisation under these flow intensity constraints with the objective of maximising mixing rate performance.
+In addition, diffusion is generally perceived as beneficial to mixing due to its ability to homogenize a passive tracer.
+However in the case where advection and diffusion are both actively present, we provide numerical evidence that diffusion in quite general cases produce nearly neutral or even {\it negative} effects by limiting the mixing effectiveness of incompressible optimal flows.
+The underlying mechanism causing this limitation appears to be due to the presence of a limiting length scale given by a generalized Batchelor length \cite{Batchelor1959a}.
+This length scale limitation in turn affects long-term mixing rates.
+More specifically, we consider local-in-time flow optimisation under energy and enstrophy flow constraints with the objective of maximising mixing rate performance.
 We observe that, for enstrophy-bounded optimal flows, the strength of diffusion has no impact on the long-term mixing rate performance.
 For energy-constrained optimal flows, however an increase in the strength of diffusion decreases the mixing rate.
-We provide analytical lower bounds on mixing rates and length scales achievable under related constraints (point-wise bounded speed and rate-of-strain) by extending the work of \cite{JFM2011} and \cite{Chi-Cheu1996}.
+We provide analytical lower bounds on mixing rates and length scales achievable under related constraints (point-wise bounded speed and rate-of-strain) by extending the work of Z.
+Lin {\it et.
+al.} \cite{JFM2011} and C.-C.
+Poon \cite{Chi-Cheu1996}.
 
@@
 
-Mixing a passive tracer concentration via an incompressible fluid flow is important to many areas of science and engineering.
-A question of interest across these domains is ``How can one stir to enhance the rate of mixing?'' We explore this question and study the impact of molecular diffusion.
+%%%%%
+
+%
+
+%
+
+% Furthermore, we believe that the study of determining the smallest length scales achievable demands more attention.
+This assumption is used today throughout the computational fluid dynamics community to provide a heuristic for the grid resolutions necessary.
+Thus, it is important to determine what conditions on $\mathbf{u}$ are necessary to justify this assumption.
+
+% We explore this question and study the impact of molecular diffusion.
 We address this topic by considering an incompressible flow with mild physical constraints in a periodic box with side length $L$ in $d$ dimensions.
 We consider a mean-zero tracer concentration field $\theta$ that evolves according to the advection-diffusion equation,
+%\begin{equation}
+%	\label{eq:PDE_advection}
+%	\ppt{\theta}+\mathbf{u}\cdot \nabla \theta=\kappa \lap\theta,
+%\end{equation}
+%with initial data $\theta(\mathbf{x},0)=\theta_{0}(\mathbf{x})$, where $\kappa$ is the molecular diffusion coefficient and $\mathbf{u}(\mathbf{x},t)$ is a incompressible ($\nabla\,\cdot\, \vec{u}=0$) flow field.
+
+%%%%%
+
+% -- Introduction of the advection-diffusion equation and inherent nonlinearities
+%%% 
+%%% Furthermore, the complexity of $u$ can be inherently complicated as solutions to the Navier-Stokes equations.
+Futhermore, when concerned with optimal mixing one must make a decision on which velocity field to  prescribe based on the the current scalar concentration field.
+
+% -- Motivation for fluid dynamicists / physicists
+%%% Impact on turbulence theory and Batchelor length.
+
+% -- Motivation for computionational fluid dynamics practioners
+%%% Impact considerations for smallest lengths in grid discretizations.
+
+% -- Motivation for industrial process engineers
+%%% Industrial processes as a motivation for studying mixing
+
+%-- Motivation for mathematicians
+%%% The approach taken here may apeal to the mathematician as an abstraction of the mixing process and focuses on the core transportation equation --- advection-diffusion.
+We ask how qualities (cecay of functional norms) of the solution depend on which function space $u$ belongs to.
+%%% Fundamental insights into a core partial differential equation
+
+%
+%%-- Motivation for mathematicians
+%The approach taken here may apeal to the mathematician as an abstraction of the mixing process and focuses on the core transportation equation --- advection-diffusion.
+We ask how qualities (cecay of functional norms) of the solution depend on which function space $\vec{u}$ belongs to.
+%%%% Fundamental insights into a core partial differential equation 
+%
+%By `mixing', we mean the combined influence of advection or stirring of bulk fluid motion and molecular diffusion of a tracer concentration which could take the form of temperature, salinity, solute, or any scalar quantity.
+%
+%of a passive tracer concentration via an incompressible fluid flow
+
+Mixing of a passive tracer quantity, such as temperature, solute cocentration, or salinity, by an incompressible flow is a fundamental fluid process.
+It is relevant to many domains such as turbulence theory \cite{Dimotakis2005,Violeau2000a}, aerospace engineering, oceanography \cite{Wunsch2004}, and atmospheric sciences.
+It also serves as a key industrial process within the food, pharmaceutical, petrochemical, and other industries \cite{paul2004handbook}.
+The estimated costs due to poor industrial mixing in 1989 was \$1 -- \$10 billion US dollars for the chemical industry alone \cite{paul2004handbook}.
+Although mixing is highly prevalent and used, its fundamental principles are still not fully known especially concerning how the interplay of advection and diffusion processes affect mixing rates and achievable filamentation length scales.
+
+The effect of diffusion and advection on the rate of fluid mixing depends on the particular mixing situation characterized by the unique fluid properties, specific mixing flow, and boundary geometry.
+In view of the vast complexity of the mixing situation, general principles of mixing underlying these various situations would be beneficial.
+In particular, it is valuable to determine how the mixing rate (typically the most optimal mixing rate) depends on aggregate flow intensity measures such as energy and enstrophy.
+This is the objective of the research program encompassing many efforts \cite{CS2013,GI2014,JLT2012,JFM2011, Miles2017a,  JLT2012, DF2014, GM2005} in last decade.
+
+With these goals in mind, a common approach taken throughout the literature is to consider the evolution of a tracer quantity $\theta$ advected by an incompressible ($\nabla \cdot\vec{u}=0$) flow $\vec{u}$ with mild physical constraints within a periodic box  of side length $L$ in $d$ dimensions.
+The tracer concentration field $\theta$ evolves according to the advection-diffusion equation,
 \begin{equation}
@@
 \end{equation}
-with initial data $\theta(\mathbf{x},0)=\theta_{0}(\mathbf{x})$, where $\kappa$ is the molecular diffusion coefficient and $\mathbf{u}(\mathbf{x},t)$ is a incompressible ($\nabla\,\cdot\, \vec{u}=0$) flow field.
+with initial data $\theta(\mathbf{x},0)=\theta_{0}(\mathbf{x})$, where $\kappa$ is the molecular diffusion coefficient.
 The flow is constrained by enstrophy $\ltwo{\nabla\u} = \Gamma L^{d/2}$ or energy $\ltwo{\u} = UL^{d/2}$ where $\Gamma$ is the root mean square rate-of-strain and $U$ is the root mean square speed.
-We primarily use the $H^{-1}$ norm or mix-norm throughout to measure homogenisation,
 
+The $H^{-1}$ norm or mix-norm \cite{GM2005} is also a common measure of mixing used throughout the literature and will be used here as well.
+For those interested in other measures of mixing, see \cite{JLT2012}.
+The $H^{-1}$ norm is given by
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $\nabla^{-1}=\nabla \Delta^{-1}$, the operator $\Delta^{-1}$ acting on  a function $\rho$ returns the solution $\phi$ of the Poisson equation $ \Delta \phi = \rho $, and $\hat{\theta}_{\vec{k}}(t) =  \frac{1}{L^{d}}\sint{\theta(\vec{x},t)e^{-i\vec{k}\cdot\vec{x}}}$.
-Lower values of the  $H^{-1}$ norm corresponds to a more mixed state.
-Note that $H^{-1}$ norm can decrease in two ways: either by decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ or by advecting the flow such that the tracer concentration acquires more spectral mass in the higher wave numbers and takes advantage of the $1/|\vec{k}|^2$ dependence.
+Lower values of the  $H^{-1}$ norm correspond to a more mixed state.
+Note that $H^{-1}$ norm can decrease in two ways.
+The first way is to decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ for $\vec{k}\neq 0$.
+This matches our first sense of mixing --- {\it homogenization}.
+The second way is by transferring spectral mass from the lower wave numbers to the higher wave numbers to take advantage of the $1/|\vec{k}|^2$ dependence.
+This produces a scalar field with sharp gradients and small length scales which matches our second sense of mixing --- {\it filamentation}.
+Thus we can see that the $H^{-1}$ embodies both senses.
+
+In the case without advection ($\vec{u}=\vec{0}$), equation \eref{eq:PDE_advection} reduces to the classical heat equation \cite{Evans2010}.
+The Fourier modes evolve according to $\hat{\theta}_{\vec{k}}(t)=\hat{\theta}_{\vec{k}}(0)e^{-\kappa|\vec{k}|^2t}$.
+Thus we have explicit analytical results for the decay of the $H^{-1}$ mix-norm by simply substituting this result.
+Note that $H^{-1}$ mix-norm will surely decay monotonically.
+Diffusion is incapable of transferring spectral mass from the low wave number modes to the high wave number modes and thus is incapable of filamentation.
+Thus the pure diffusion case solely exploits homogenization.
+Also notice the unequal weighting attach to each mode.
+The Fourier modes with large wave number $|\vec{k}|$ decay at a faster rate relative to the decay of those with small wave number.
+
+%To further facilitate discussion, we define the following ratio as a measure of the characteristic {\it filamentation length} scale:
+%\begin{equation}
+%\label{eq:length}
+%\lambda(t)\equiv  2\pi \frac{\|\nabla^{-1}\theta(\,\cdot\,,t)\|_{L^{2}}}{\|\theta(\,\cdot\,,t)\|_{L^{2}}}.
+%\end{equation}
+%Note that $\lambda(t)$ returns the wavelength of the wave number $\vec{k}$ for a tracer concentration field composed only of the Fourier mode with wave number $\vec{k}$ (i.e.
+$\theta(\vec{x},t) = Re[ A e^{-i\vec{k}\cdot \vec{x}}]$ where $A$ is a complex constant).
+In general, $\lambda$ is the weighted root mean square wavelength with weights given by $|\theta_{\vec{k}}|^2/\ltwo{\theta}^2$.
+
+In the case without diffusion ($\kappa = 0$), pure advection of the flow is the only method of mixing or colloquially known as stirring.
+For a flow that is constrained by enstrophy, the mix-norm decays at most exponentially where the exponential rate depends on the support of the initial data and is proportional to $\Gamma$ \cite{GI2014,CS2013}.
+This was mathematically proven by two separate approaches: G.
+Iyer {\it et.
+al.} \cite{GI2014} used regularisation results of partial differential equations \cite{Crippa} while C.
+Seis \cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
+Furthermore, enstrophy-constrained flows that realize this exponential decay rate have been constructed analytically \cite{Alberti2014a}.
+On the other hand, energy-constrained flows can achieve even faster mixing rates.
+In fact they can achieve {\it perfect mixing in finite time} which means that the $H^{-1}$ mix-norm approaches zero in finite time as opposed to approaching zero in infinite time as in the case for enstrophy-constrained mixing.
+This can be demonstrated by a `chequerboard' flow \cite{JMP2012} where the mix-norm achieves perfect mixing in finite time by a linear decay rate.
+In either flow intensity constraint, note that $H^{-1}$ mix-norm decreases by exclusively exploiting filamentation without homogenization.
+This is  exactly opposite to the purely diffusive case.
+
+Finally, the case with diffusion and advection is the least explored in this framework and the focus of this paper. 
+It is known that the evolution of the $H^{-1}$ and $L^2$ norms decrease monotonically under the chequerboard flow introduced by \cite{JMP2012}
+ while the $H^{1}$ increases until it reaches a peak and then decreases \cite{DF2014}.
+This peak corresponds to a  time when the length scales developed are small enough for diffusion to effectively act on steep gradients.
+C.
+Miles and C.
+Doering \cite{Miles2017a} explored this phenomena further in the context of a shell model, a reduced model using ordinary differential equations that mimic the spectral dynamics of the advection-diffusion equation.
+The authors concluded that shell-model mixing could not surpass length scales given by $\sqrt{\kappa/ \Gamma}$ for enstrophy-constrained flows and $\kappa/U$ for energy-constrained flows up to $O(1)$ constants.
+These length scales can be identified as a generalised Batchelor scale \cite{Batchelor1959a}, introduced in the context of turbulence theory.
+These limitations on the length scale in turn controlled the long-run optimal mixing rates determined to be $\Gamma$ under the enstrophy constraint and $U^2/\kappa$ under the energy constraint up to $O(1)$ constants.
+In contrast to the `pure' cases mentioned earlier, it is important to note that the $H^{-1}$ can now decrease by the two avenues of homogenization and filamentation simultaneously.
+
+At this point, we can already see a glimpse of a conflict between diffusion and advection for the ultimate goal of optimal mixing.
+Pure advection succeeds at filamentation by transferring spectral mass from the low wave number modes to the high wave number modes in a continuous fashion.
+However in the presence of diffusion, a once optimal pure advection flow exceptional at filamentation will be met with potential conflict since homogenization by diffusion may stifle its progress in progressing spectral mass to high wave number modes.
+Given that diffusion ubitquitous, we must come to terms with this conflict to promote more efficient mixing.
+
+In this paper, we make progress towards answering ``What is the most optimal mixing rate in the presence of diffusion for an enstrophy or energy constrained flow?'' This question was also asked in the question of the shell model.
+We would like to determine if the predictions of the shell model hold in the partial differential equation setting.
+
+We approach the posed question by considering the general setup introduced of the evolution of passive scalar in a periodic box.
+We consider the local-in-time optimization problem first introduced by Z.
+Lin {\it et.
+al.} \cite{JFM2011} in the context of diffusion.
+Local-in-time optimization seeks to find the optimal flow that achieves the best instantaneous mixing rate.
+We will see that the best choice leads to a $\vec{u}$ that depends on $\theta$.
+This feedback causes the dynamics of $\theta$ governed by \eref{eq:PDE_advection} to be nonlinear.
+
+%These results also imply that the filamentation length scale $\lambda$ also decays exponentially to zero over time given by the observation that the denominator of \eref{eq:length} is constant in time (this can be shown directly from \eref{eq:PDE_advection}).
+Since the filamentation length scale $\lambda$ is proportional $H^{-1}$ for $\kappa = 0$, we know that the $\lambda$ can become arbitrarily small as well.
+
+%On the other hand, diffusion is generally perceived to enhance mixing rates of a passive tracer.
+It is a reasonable expectation since molecular diffusion of a dye can lead to a more homogeneous mixture as seen in everyday experience from allowing cream in coffee to diffusion over time without actively stirring --- diffusion surely benefits mixing in this case.
+However, the case where advection and diffusion processes are both relevant with the goal of enhance mixing rates must be treated with care and is the topic of this paper.
+
+%We use the $H^{-1}$ norm to define the (exponential) rate of mixing as
+%\begin{equation}
+%\label{eq:rate}
+%r(t) = -  \frac{\ddt{}\hmone{\theta}}{\hmone{\theta}}.
+%\end{equation}
+%The $L^{2}$ norm $\ltwo{\theta}$ and the $H^{1}$ norm $\hone{\theta}$ are also common measures of mixing and will be considered here as well.
+
+%In particular, we explore the impact of molecular diffusion on mixing through analytic and computational means. 
+%
+%
+% \cite{JFM2011} showed numerical evidence that the filament width $\lambda$ seemingly decreased continually by instantaneous flow optimisation.
+This type of optimisation will be considered in this work as well.
+Self-similar flows can realise a decreasing $\lambda$ over time as shown analytically by \cite{Alberti2014a}.
+It was rigorously proven independently by \cite{GI2014} and \cite{CS2013} that $\lambda$ decreased at most exponentially --- consistent with \cite{JFM2011} and \cite{Alberti2014a}.
+The work of \cite{GI2014} relied on PDE regularisation results of \cite{Crippa} while the approach of \cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
+%
+%For $Pe = \infty$ energy-constrained problem, \cite{JMP2012} showed that a `chequerboard' flow can also provide continually decreasing length scales.
+Moreover, $\lambda$ decreased at a fast enough rate to approach zero in finite time in contrast to the enstrophy-constrained problem where $\lambda$ decreases to zero in infinite time.
+%
+%The inclusion of diffusion ($Pe <\infty$) with the objective of optimal mixing has been explored.
+\cite{DF2014} investigated optimal mixing and study the evolution of the mentioned measures ($H^{-1}, L^2,$ and $H^1$ norms) of mixing under the chequerboard flow introduced by \cite{JMP2012}.
+They show that the $H^{-1}$ and $L^2$ norms decrease monotonically under this flow while the $H^{1}$ increases until it reaches a peak and then decreases.
+This peak corresponds to a  time when the length scales developed are small enough for diffusion to effectively act on steep gradients.
+\cite{Miles2017a} explored this phenomena further in the context of a shell model, a reduced model using ordinary differential equations that mimic the spectral dynamics of the advection-diffusion equation.
+The authors concluded that shell-model mixing could not surpass length scales given by $\sqrt{\kappa/ \Gamma}$ for enstrophy-constrained flows and $\kappa/U$ for energy-constrained flows up to $O(1)$ constants.
+These length scales can be identified as a generalised Batchelor scale \cite{Batchelor1959a}, introduced in the context of turbulence theory.
+%
+
+%Diffusion is generally perceived as a beneficiary to the goal of enhanced mixing rates of a passive tracer.
+It is a reasonable expectation since molecular diffusion of a dye can lead to a more homogeneous mixture as seen in everyday experience from allowing cream in coffee to diffusion over time without actively stirring --- diffusion surely benefits mixing in this case.
+However every coffee drinker knows that they can accelerate the mixing process by stirring or in other words advecting the fluid appropriately.
+Note that if diffusion were completely absent, then advection is the only way to enhance mixing.
+Pure advection is undoubtedly beneficial in this case.
+However, the case where advection and diffusion processes are both relevant with the goal of enhance mixing rates must be treated with care and is the topic of this paper.
+
+%The length scales achievable within a passive scalar can also be affected by the same fluid properties and environmental conditions. It has
+%
+% 
+%
+
+In this work, we will demonstrate that homogenization via diffusion and filamentation via advection can sometimes be in conflict and collectively produce a negative impact on mixing.
+We explore how diffusion impacts the evolution of the filament width $\lambda$ over time and mixing rates.
+We show numerical evidence that $\lambda$ appears to be limited by the Batchelor scale as seen in the shell model.
+Even when actively trying to choose the most optimal flow to minimise filamentation length.
+Thus, this may suggest that the Batchelor scale does not only limit turbulent flows but also all incompressible flows under the flow constraints considered here.
+Although these quantities have been known in the context of turbulence theory, the impact of these limitations on mixing rates has not been fully studied to our knowledge.
+
+The paper is organised as follows.
+We introduce the necessary theory regarding local-in-time optimisation, a shell model, and $L^{\infty}$ flow constraints in section \ref{sec:theory}.
+Section \ref{sec:numerical_experiment} details the methodology and results of numerically implementing local-in-time flow optimisation.
+Lastly, we finish with a discussion and conclusion in sections \ref{sec:discussion} and \ref{sec:conclusion} respectively.
+
+%%%
+%%%
+%%% THEORY
+%%%
+%%%
+
+\section{Theory}
+\label{sec:theory}
+\subsection{Local-in-time optimisation}
+
 We use the $H^{-1}$ norm to define the (exponential) rate of mixing as
@@
 
-We will first review results for the $Pe = \infty$ enstrophy-constrained case.
-\cite{JFM2011} showed numerical evidence that the filament width $\lambda$ seemingly decreased continually by instantaneous flow optimisation.
-This type of optimisation will be considered in this work as well.
-Self-similar flows can realise a decreasing $\lambda$ over time as shown analytically by \cite{Alberti2014a}.
-It was rigorously proven independently by \cite{GI2014} and \cite{CS2013} that $\lambda$ decreased at most exponentially --- consistent with \cite{JFM2011}  and \cite{Alberti2014a}.
-The work of \cite{GI2014} relied on PDE regularisation results of \cite{Crippa} while the approach of \cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
-
-For $Pe = \infty$ energy-constrained problem, \cite{JMP2012} showed that a `chequerboard' flow can also provide continually decreasing length scales.
-Moreover, $\lambda$ decreased at a fast enough rate to approach zero in finite time in contrast to the enstrophy-constrained problem where $\lambda$ decreases to zero in infinite time.
-
-The inclusion of diffusion ($Pe <\infty$) with the objective of optimal mixing has been explored.
-\cite{DF2014} investigated optimal mixing and study the evolution of the mentioned measures ($H^{-1}, L^2,$ and $H^1$ norms) of mixing under the chequerboard flow introduced by \cite{JMP2012}.
-They show that the $H^{-1}$ and $L^2$ norms decrease monotonically under this flow while the $H^{1}$ increases until it reaches a peak and then decreases.
-This peak corresponds to a  time when the length scales developed are small enough for diffusion to effectively act on steep gradients.
-\cite{Miles2017a} explored this phenomena further in the context of a shell model, a reduced model using ordinary differential equations that mimic the spectral dynamics of the advection-diffusion equation.
-The authors concluded that shell-model mixing could not surpass length scales given by $\sqrt{\kappa/ \Gamma}$ for enstrophy-constrained flows and $\kappa/U$ for energy-constrained flows up to $O(1)$ constants.
-These length scales can be identified as a generalised Batchelor scale \cite{Batchelor1959a}, introduced in the context of turbulence theory.
-
-In this work, we explore how diffusion impacts the evolution of the filament width $\lambda$ over time and mixing rates.
-We show numerical evidence that $\lambda$ appears to be limited by the Batchelor scale as seen in the shell model.
-Even when actively trying to choose the most optimal flow to minimise filamentation length.
-Thus, this may suggest that the Batchelor scale does not only limit turbulent flows but also all incompressible flows under the flow constraints considered here.
-Although these quantities have been known in the context of turbulence theory, the impact of these limitations on mixing rates has not been fully studied to our knowledge.
-
-Furthermore, we believe that the study of determining the smallest length scales achievable demands more attention.
-This assumption is used today throughout the computational fluid dynamics community to provide a heuristic for the grid resolutions necessary.
-Thus, it is important to determine what conditions on $\mathbf{u}$ are necessary to justify this assumption.
-
-The paper is organised as follows.
-We introduce the necessary theory regarding local-in-time optimisation, a shell model, and $L^{\infty}$ flow constraints in section \ref{sec:theory}.
-Section \ref{sec:numerical_experiment} details the methodology and results of numerically implementing local-in-time flow optimisation.
-Lastly, we finish with a discussion and conclusion in sections \ref{sec:discussion} and \ref{sec:conclusion} respectively.
-
-%%%
-%%%
-%%% THEORY
-%%%
-%%%
-
-\section{Theory}
-\label{sec:theory}
-\subsection{Local-in-time optimisation}
 We consider the local-in-time optimisation strategy first introduced by \cite{JFM2011} in the diffusion-less case.
@@
 \end{equation}
-Using this with (\ref{eq:exponential_enstrophy}), we deduce the lower bound
+Using this with \eref{eq:exponential_enstrophy}, we deduce the lower bound
 \begin{equation}
@@
 	 									-Pe \sint{\theta\left(\ppt{\theta}
-	 									+\frac{1}{Pe}\lap \theta\right)} 
-\end{eqnarray},
+	 									+\frac{1}{Pe}\lap \theta\right)},
+\end{eqnarray}
 %
@@
 										 + \sint{\theta\left(\ppt{\theta}
-	 									+\frac{1}{Pe}\lap \theta\right)} 
-\end{eqnarray},
+	 									+\frac{1}{Pe}\lap \theta\right)} ,
+\end{eqnarray}
 %
@@
 %
-Using H\"older's inequality and (\ref{eq:PDE_advection}), this simplifies to
+Using H\"older's inequality and \eref{eq:PDE_advection}, this simplifies to
 %
@@
 %
-Using (\ref{eq:k2growth_energy}) together with  $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$ we observe that
+Using \eref{eq:k2growth_energy} together with  $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$ we observe that
 %
@@
 %
-and this combined with  (\ref{eq:lambda_bound}) implies
+and this combined with  \eref{eq:lambda_bound} implies
 %
@@
 
-We solve (\ref{eq:nd_ade}) by using a Fourier basis to represent the $512 \times 512$ discretised spatial domain with a 4th order Runge-Kutta time-stepping method.
+We solve \eref{eq:nd_ade} by using a Fourier basis to represent the $512 \times 512$ discretised spatial domain with a 4th order Runge-Kutta time-stepping method.
 All simulation code was created in the programming language Python with package modules, pyfftw and numpy.
@@
 We model the transient phase as $\lambda(t)=\lambda(0)(1-\beta t)$.
-Therefore, we theorise that the critical transition time is $t_{c}=\frac{1}{\beta}(1 -\lambda_{U}/\lambda(0)) = \frac{1}{\beta}(1 - 1/Pe)$ with $Pe> 1$ (If $Pe \leq 1$, there is not transient phase) for the energy case.
+Therefore, we theorise that the critical transition time is $t_{c}=\frac{1}{\beta}(1 -\lambda_{U}/\lambda(0)) = \frac{1}{\beta}(1 - 1/Pe)$ with $Pe> 1$ (If $Pe \leq 1$, there is no transient phase) for the energy case.
 Thus, it is true that on can still achieve an earlier onset of the long-term mixing behaviour by choosing a smaller $Pe$.
@@
 
-%Our numerical study of local-in-time optimization suggest that there is a limiting length scale given by $\lambda_{\Gamma} = 1/\sqrt{Pe}$ (in dimensional form, $\sqrt{\kappa/\Gamma}$) for fixed enstrophy and $\lambda_{U} = 1/Pe$ (in dimensional form $\kappa/U$) for fixed energy.
-The study also suggests a long-term mixing rate given by  $r_{\Gamma} = 1 $ (in dimensional form, $\Gamma$) for fixed enstrophy and $r_{U} = Pe$ (in dimensional form, $U^2/\kappa$) for fixed energy.
-
-%
-%Define the spectral variance as
-%%
-%\begin{equation}
-%		\left[ 
-%			\frac{\hone{\theta}^2\hmone{\theta}^2}
-%			{\ltwo{\theta}^4}  
-%			- 1
-%		\right].
-%\end{equation}
-%%
-%By using this definition with H\"older's inequality provided that  $\linf{\nabla\vec{u}}\leq \Gamma$, we find that
-%%
-%\begin{equation}
-%\label{eq:length_ineq_rate-of-strain}
-%	\ddt{\lambda^2} \geq 2 1/Pe \sigma^2 - 2 \Gamma \lambda^2 .
-%\end{equation}
-%%
-%By taking the long-time average (noted as $\langle \cdot \rangle \equiv\lim_{T\rightarrow\infty}\frac{1}{T}\int_{0}^T \,\, \cdot \,\, dt $ ) of the inequality above, we find that 
-%%
-%\begin{equation}
-%	0 \geq  2 \kappa \tavg{\sigma^2} - 2 \Gamma \tavg{\lambda^2}.
-%\end{equation}
-%%
-%The left hand side is zero since $\lambda^2$ is bounded by Poincar\'e's inequality. Thus, we find that
-%%
-%\begin{equation}
-%	\tavg{\lambda^2} \geq   \lambda_{B}^2 \tavg{\sigma^2} 
-%\end{equation}
-%%
-%where the Batchelor scale is given by $\lambda_{B} = \sqrt{\kappa/\Gamma}.$ 
-%
-%
-%We conclude that ...
-%
-%By a dimensional analysis, we conjecture that the velocity field with $\hmone{\u}$=1 may be capable decreasing $\lambda$ past the Batchelor scale.
-
-%\appendix
-%\section{Mixing time of modified checkerboard flow}
-%\label{appendix:checkerboard}
-%We consider a similar  the checkerboard flow from \cite{JMP2012}.
-Suppose one starts with the initial `binary' dye concentration field where $\theta_{0}(\vec{x}) = 1$ for $x_{1}< 1/2$ and $\theta_{0}(\vec{x}) = -1$ for $x_{1}\geq 1/2$.
-We constrain $\vec{u}$ to be  $\ltwo{\vec{u}} = 1$.
-We consider a sheer flow as described by \cite{JMP2012}
-
-%\section{Numerical analysis}
-%\label{sec:num_analysis}
-%Our conclusions rely heavily on the accuracy of our numerical solutions to the advection diffusion equations.
-Careful numerical analysis is thus important to make sure the length resolution is sufficient and spectral amplitudes are computed to sufficient numerical accuracy.
-
-\bibliographystyle{unsrt.bst}
+\section*{References}
+\bibliographystyle{iopart-num}
 \bibliography{library}

### 2017-10-18 nonlinearity/manuscript.tex
removed commented old text
added requirements file for pip

@@
 Incompressible flows can be effective mixers by appropriately advecting a passive tracer to produce small filamentation length scales.
-In addition, diffusion is generally perceived as beneficial to mixing due to its ability to homogenize a passive tracer.
+In addition, diffusion is generally perceived as beneficial to mixing due to its ability to homogenise a passive tracer.
 However in the case where advection and diffusion are both actively present, we provide numerical evidence that diffusion in quite general cases produce nearly neutral or even {\it negative} effects by limiting the mixing effectiveness of incompressible optimal flows.
-The underlying mechanism causing this limitation appears to be due to the presence of a limiting length scale given by a generalized Batchelor length \cite{Batchelor1959a}.
+The underlying mechanism causing this limitation appears to be due to the presence of a limiting length scale given by a generalised Batchelor length \cite{Batchelor1959a}.
 This length scale limitation in turn affects long-term mixing rates.
@@
 \section{Introduction}
+\label{sec:introduction}
 
-%%%%%
-
-%
-
-%
-
-% Furthermore, we believe that the study of determining the smallest length scales achievable demands more attention.
-This assumption is used today throughout the computational fluid dynamics community to provide a heuristic for the grid resolutions necessary.
-Thus, it is important to determine what conditions on $\mathbf{u}$ are necessary to justify this assumption.
-
-% We explore this question and study the impact of molecular diffusion.
-We address this topic by considering an incompressible flow with mild physical constraints in a periodic box with side length $L$ in $d$ dimensions.
-We consider a mean-zero tracer concentration field $\theta$ that evolves according to the advection-diffusion equation,
-%\begin{equation}
-%	\label{eq:PDE_advection}
-%	\ppt{\theta}+\mathbf{u}\cdot \nabla \theta=\kappa \lap\theta,
-%\end{equation}
-%with initial data $\theta(\mathbf{x},0)=\theta_{0}(\mathbf{x})$, where $\kappa$ is the molecular diffusion coefficient and $\mathbf{u}(\mathbf{x},t)$ is a incompressible ($\nabla\,\cdot\, \vec{u}=0$) flow field.
-
-%%%%%
-
-% -- Introduction of the advection-diffusion equation and inherent nonlinearities
-%%% 
-%%% Furthermore, the complexity of $u$ can be inherently complicated as solutions to the Navier-Stokes equations.
-Futhermore, when concerned with optimal mixing one must make a decision on which velocity field to  prescribe based on the the current scalar concentration field.
-
-% -- Motivation for fluid dynamicists / physicists
-%%% Impact on turbulence theory and Batchelor length.
-
-% -- Motivation for computionational fluid dynamics practioners
-%%% Impact considerations for smallest lengths in grid discretizations.
-
-% -- Motivation for industrial process engineers
-%%% Industrial processes as a motivation for studying mixing
-
-%-- Motivation for mathematicians
-%%% The approach taken here may apeal to the mathematician as an abstraction of the mixing process and focuses on the core transportation equation --- advection-diffusion.
-We ask how qualities (cecay of functional norms) of the solution depend on which function space $u$ belongs to.
-%%% Fundamental insights into a core partial differential equation
-
-%
-%%-- Motivation for mathematicians
-%The approach taken here may apeal to the mathematician as an abstraction of the mixing process and focuses on the core transportation equation --- advection-diffusion.
-We ask how qualities (cecay of functional norms) of the solution depend on which function space $\vec{u}$ belongs to.
-%%%% Fundamental insights into a core partial differential equation 
-%
-%By `mixing', we mean the combined influence of advection or stirring of bulk fluid motion and molecular diffusion of a tracer concentration which could take the form of temperature, salinity, solute, or any scalar quantity.
-%
-%of a passive tracer concentration via an incompressible fluid flow
-
-Mixing of a passive tracer quantity, such as temperature, solute cocentration, or salinity, by an incompressible flow is a fundamental fluid process.
+Mixing of a passive tracer quantity, such as temperature, solute concentration, or salinity, by an incompressible flow is a fundamental fluid process.
 It is relevant to many domains such as turbulence theory \cite{Dimotakis2005,Violeau2000a}, aerospace engineering, oceanography \cite{Wunsch2004}, and atmospheric sciences.
@@
 
-The effect of diffusion and advection on the rate of fluid mixing depends on the particular mixing situation characterized by the unique fluid properties, specific mixing flow, and boundary geometry.
+The effect of diffusion and advection on the rate of fluid mixing depends on the particular mixing situation characterised by the unique fluid properties, specific mixing flow, and boundary geometry.
 In view of the vast complexity of the mixing situation, general principles of mixing underlying these various situations would be beneficial.
@@
 
-The $H^{-1}$ norm or mix-norm \cite{GM2005} is also a common measure of mixing used throughout the literature and will be used here as well.
+The $H^{-1}$ norm or mix-norm \cite{GM2005} is also a common measure of mixing used throughout the literature and will be used here.
+The $L^{2}$ norm $\ltwo{\theta}$ and the $H^{1}$ norm $\hone{\theta}$ are also common measures of mixing and will be considered here as well.
 For those interested in other measures of mixing, see \cite{JLT2012}.
@@
 The first way is to decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ for $\vec{k}\neq 0$.
-This matches our first sense of mixing --- {\it homogenization}.
+This matches our first sense of mixing --- {\it homogenisation}.
 The second way is by transferring spectral mass from the lower wave numbers to the higher wave numbers to take advantage of the $1/|\vec{k}|^2$ dependence.
@@
 Note that $H^{-1}$ mix-norm will surely decay monotonically.
-Diffusion is incapable of transferring spectral mass from the low wave number modes to the high wave number modes and thus is incapable of filamentation.
-Thus the pure diffusion case solely exploits homogenization.
+Diffusion is unable to transfer spectral mass from the low wave number modes to the high wave number modes and thus is incapable of filamentation.
+Thus the pure diffusion case solely exploits homogenisation.
 Also notice the unequal weighting attach to each mode.
@@
 In the case without diffusion ($\kappa = 0$), pure advection of the flow is the only method of mixing or colloquially known as stirring.
-For a flow that is constrained by enstrophy, the mix-norm decays at most exponentially where the exponential rate depends on the support of the initial data and is proportional to $\Gamma$ \cite{GI2014,CS2013}.
+For a flow that is constrained by enstrophy, the mix-norm decays at most exponentially where the exponential rate is proportional to $\Gamma$ \cite{GI2014,CS2013}.
 This was mathematically proven by two separate approaches: G.
@@
 Seis \cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
-Furthermore, enstrophy-constrained flows that realize this exponential decay rate have been constructed analytically \cite{Alberti2014a}.
+Furthermore, enstrophy-constrained flows that realise this exponential decay rate have been constructed analytically \cite{Alberti2014a}.
 On the other hand, energy-constrained flows can achieve even faster mixing rates.
@@
 This can be demonstrated by a `chequerboard' flow \cite{JMP2012} where the mix-norm achieves perfect mixing in finite time by a linear decay rate.
-In either flow intensity constraint, note that $H^{-1}$ mix-norm decreases by exclusively exploiting filamentation without homogenization.
+In either flow intensity constraint, note that $H^{-1}$ mix-norm decreases by exclusively exploiting filamentation without homogenisation.
 This is  exactly opposite to the purely diffusive case.
@@
 These limitations on the length scale in turn controlled the long-run optimal mixing rates determined to be $\Gamma$ under the enstrophy constraint and $U^2/\kappa$ under the energy constraint up to $O(1)$ constants.
-In contrast to the `pure' cases mentioned earlier, it is important to note that the $H^{-1}$ can now decrease by the two avenues of homogenization and filamentation simultaneously.
+In contrast to the `pure' cases mentioned earlier, it is important to note that the $H^{-1}$ can now decrease by the two avenues of homogenisation and filamentation simultaneously.
 
@@
 Pure advection succeeds at filamentation by transferring spectral mass from the low wave number modes to the high wave number modes in a continuous fashion.
-However in the presence of diffusion, a once optimal pure advection flow exceptional at filamentation will be met with potential conflict since homogenization by diffusion may stifle its progress in progressing spectral mass to high wave number modes.
-Given that diffusion ubitquitous, we must come to terms with this conflict to promote more efficient mixing.
+However in the presence of diffusion, a once optimal pure advection flow exceptional at filamentation will be met with potential conflict since homogenisation by diffusion may stifle its progress in transferring spectral mass to high wave number modes.
+Given that diffusion is ubiquitous, we must come to terms with this conflict to produce efficient mixing.
 
-In this paper, we make progress towards answering ``What is the most optimal mixing rate in the presence of diffusion for an enstrophy or energy constrained flow?'' This question was also asked in the question of the shell model.
+In this paper, we make progress towards answering ``What is the most optimal mixing rate in the presence of diffusion for an enstrophy or energy constrained flow?'' This question was also asked in the context of the shell model.
 We would like to determine if the predictions of the shell model hold in the partial differential equation setting.
@@
 We approach the posed question by considering the general setup introduced of the evolution of passive scalar in a periodic box.
-We consider the local-in-time optimization problem first introduced by Z.
+We consider the local-in-time optimisation problem first introduced by Z.
 Lin {\it et.
 al.} \cite{JFM2011} in the context of diffusion.
-Local-in-time optimization seeks to find the optimal flow that achieves the best instantaneous mixing rate.
+Local-in-time optimisation seeks to find the optimal flow that achieves the best instantaneous mixing rate.
 We will see that the best choice leads to a $\vec{u}$ that depends on $\theta$.
@@
 
-%These results also imply that the filamentation length scale $\lambda$ also decays exponentially to zero over time given by the observation that the denominator of \eref{eq:length} is constant in time (this can be shown directly from \eref{eq:PDE_advection}).
-Since the filamentation length scale $\lambda$ is proportional $H^{-1}$ for $\kappa = 0$, we know that the $\lambda$ can become arbitrarily small as well.
-
-%On the other hand, diffusion is generally perceived to enhance mixing rates of a passive tracer.
-It is a reasonable expectation since molecular diffusion of a dye can lead to a more homogeneous mixture as seen in everyday experience from allowing cream in coffee to diffusion over time without actively stirring --- diffusion surely benefits mixing in this case.
-However, the case where advection and diffusion processes are both relevant with the goal of enhance mixing rates must be treated with care and is the topic of this paper.
-
-%We use the $H^{-1}$ norm to define the (exponential) rate of mixing as
-%\begin{equation}
-%\label{eq:rate}
-%r(t) = -  \frac{\ddt{}\hmone{\theta}}{\hmone{\theta}}.
-%\end{equation}
-%The $L^{2}$ norm $\ltwo{\theta}$ and the $H^{1}$ norm $\hone{\theta}$ are also common measures of mixing and will be considered here as well.
-
-%In particular, we explore the impact of molecular diffusion on mixing through analytic and computational means. 
-%
-%
-% \cite{JFM2011} showed numerical evidence that the filament width $\lambda$ seemingly decreased continually by instantaneous flow optimisation.
-This type of optimisation will be considered in this work as well.
-Self-similar flows can realise a decreasing $\lambda$ over time as shown analytically by \cite{Alberti2014a}.
-It was rigorously proven independently by \cite{GI2014} and \cite{CS2013} that $\lambda$ decreased at most exponentially --- consistent with \cite{JFM2011} and \cite{Alberti2014a}.
-The work of \cite{GI2014} relied on PDE regularisation results of \cite{Crippa} while the approach of \cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
-%
-%For $Pe = \infty$ energy-constrained problem, \cite{JMP2012} showed that a `chequerboard' flow can also provide continually decreasing length scales.
-Moreover, $\lambda$ decreased at a fast enough rate to approach zero in finite time in contrast to the enstrophy-constrained problem where $\lambda$ decreases to zero in infinite time.
-%
-%The inclusion of diffusion ($Pe <\infty$) with the objective of optimal mixing has been explored.
-\cite{DF2014} investigated optimal mixing and study the evolution of the mentioned measures ($H^{-1}, L^2,$ and $H^1$ norms) of mixing under the chequerboard flow introduced by \cite{JMP2012}.
-They show that the $H^{-1}$ and $L^2$ norms decrease monotonically under this flow while the $H^{1}$ increases until it reaches a peak and then decreases.
-This peak corresponds to a  time when the length scales developed are small enough for diffusion to effectively act on steep gradients.
-\cite{Miles2017a} explored this phenomena further in the context of a shell model, a reduced model using ordinary differential equations that mimic the spectral dynamics of the advection-diffusion equation.
-The authors concluded that shell-model mixing could not surpass length scales given by $\sqrt{\kappa/ \Gamma}$ for enstrophy-constrained flows and $\kappa/U$ for energy-constrained flows up to $O(1)$ constants.
-These length scales can be identified as a generalised Batchelor scale \cite{Batchelor1959a}, introduced in the context of turbulence theory.
-%
-
-%Diffusion is generally perceived as a beneficiary to the goal of enhanced mixing rates of a passive tracer.
-It is a reasonable expectation since molecular diffusion of a dye can lead to a more homogeneous mixture as seen in everyday experience from allowing cream in coffee to diffusion over time without actively stirring --- diffusion surely benefits mixing in this case.
-However every coffee drinker knows that they can accelerate the mixing process by stirring or in other words advecting the fluid appropriately.
-Note that if diffusion were completely absent, then advection is the only way to enhance mixing.
-Pure advection is undoubtedly beneficial in this case.
-However, the case where advection and diffusion processes are both relevant with the goal of enhance mixing rates must be treated with care and is the topic of this paper.
-
-%The length scales achievable within a passive scalar can also be affected by the same fluid properties and environmental conditions. It has
-%
-% 
-%
-
-In this work, we will demonstrate that homogenization via diffusion and filamentation via advection can sometimes be in conflict and collectively produce a negative impact on mixing.
-We explore how diffusion impacts the evolution of the filament width $\lambda$ over time and mixing rates.
-We show numerical evidence that $\lambda$ appears to be limited by the Batchelor scale as seen in the shell model.
-Even when actively trying to choose the most optimal flow to minimise filamentation length.
+We will demonstrate that homogenisation via diffusion and filamentation via advection can sometimes be in conflict and collectively produce a negative impact on mixing.
+We show numerical evidence that filamentation length scale appears to be limited by the Batchelor scale as seen in the shell model.
+Even when actively trying to choose the most optimal flow to enhance filamentation.
 Thus, this may suggest that the Batchelor scale does not only limit turbulent flows but also all incompressible flows under the flow constraints considered here.
@@
 \label{sec:theory}
-\subsection{Local-in-time optimisation}
+\subsection{Local-in-time flow optimisation}
 
-We use the $H^{-1}$ norm to define the (exponential) rate of mixing as
-\begin{equation}
-\label{eq:rate}
-r(t) = -  \frac{\ddt{}\hmone{\theta}}{\hmone{\theta}}.
-\end{equation}
-The $L^{2}$ norm $\ltwo{\theta}$ and the $H^{1}$ norm $\hone{\theta}$ are also common measures of mixing and will be considered here as well.
-
-We define the following ratio as a measure of the characteristic filamentation length scale:
-\begin{equation}
-\lambda(t)\equiv  2\pi \frac{\|\nabla^{-1}\theta(\,\cdot\,,t)\|_{L^{2}}}{\|\theta(\,\cdot\,,t)\|_{L^{2}}}.
-\end{equation}
-Note that $\lambda(t)$ returns the wavelength of the wave number $\vec{k}$ for a tracer concentration field composed only of the Fourier mode with wave number $\vec{k}$ (i.e.
-$\theta(\vec{x},t) = Re[ A e^{-i\vec{k}\cdot \vec{x}}]$ where $A$ is a complex constant).
-In general, $\lambda$ is the weighted root mean square wavelength with weights given by $|\theta_{\vec{k}}|/\ltwo{\theta}$.
+We will consider the evolution of a tracer quantity $\theta$ governed by equation \ref{eq:PDE_advection} under an the incompressible flow $\vec{u}$.
+Recall the flow is constrained by $\ltwo{\nabla\u} = \Gamma L^{d/2}$ or energy $\ltwo{\u} = UL^{d/2}$ where $\Gamma$ is the root mean square rate-of-strain and $U$ is the root mean square speed.
 
@@
 where $Pe=  \frac{\Gamma L^2}{\kappa}$ for the enstrophy-constrained case and $Pe= \frac{UL}{\kappa}$ for the energy-constrained case.
-The constraints on the flow become $\ltwo{\nabla\u} = 1$ or $\ltwo{\u} = 1$.
 
@@
 We find that this strategy generalises to the case with diffusion.
-The local-in-time optimal velocity fields maximise the instantaneous mixing rate by minimising $\ddt{}\hmone{\theta}^2$ or equivalently minimising $\ddt{\lambda^2}$ .
+The local-in-time optimal velocity fields maximise the instantaneous mixing rate by minimising $\ddt{}\hmone{\theta}^2$.
 The optimal velocity fields are given instantaneously by (in non-dimensional form)
@@
 These flows will be studied numerically later and is the main focus of this paper.
+
+We introduce the following measures as useful observables of mixing over time. we use the $H^{-1}$ norm to define the (exponential) rate of mixing as
+\begin{equation}
+\label{eq:rate}
+r(t) = -  \frac{\ddt{}\hmone{\theta}}{\hmone{\theta}}.
+\end{equation}
+We define the following ratio as a measure of the characteristic filamentation length scale:
+\begin{equation}
+\lambda(t)\equiv  2\pi \frac{\|\nabla^{-1}\theta(\,\cdot\,,t)\|_{L^{2}}}{\|\theta(\,\cdot\,,t)\|_{L^{2}}}.
+\end{equation}
+Note that $\lambda(t)$ returns the wavelength of the wave number $\vec{k}$ for a tracer concentration field composed only of the Fourier mode with wave number $\vec{k}$ (i.e.
+$\theta(\vec{x},t) = Re[ A e^{-i\vec{k}\cdot \vec{x}}]$ where $A$ is a complex constant).
+In general, $\lambda$ is the weighted root mean square wavelength with weights given by $|\theta_{\vec{k}}|/\ltwo{\theta}$.
 
@@
 
+Note that the pure diffusive case discussed in the introduction can always be employed as a mixing strategy by simply not having a flow field at all ($\vec{u} =\vec{0}$) provided that the flow intensity constraints are generalised to inequalities such as $\|\vec{u}\| \leq UL^{d/2}$ and $\|\nabla \vec{u}\| \leq \Gamma L^{d/2}$.
+ This is a valuable strategy if one is content with mixing at a long-term rate of $\kappa k_{\min}^2$ where $k_{\min} = \min \{ |\vec{k}|  :  |\hat{\theta}_{\vec{k}}(0)| > 0  \}$.
+This may be advised in fact if $k_{\min} > 2 \pi / \lambda_{B}$.
+This may well be the most optimal strategy.
+Invoking a flow may cause the lower wave number modes to become `populated' and therefore may limit the mixing rate.
+It is important to keep this simple strategy in mind when trying to rigorously prove bounds on the mix-norm.
+The existence of this strategy has an important implication.
+There does not exist a lower bound on the mix-norm of the form $\hmone{\theta} \geq A e^{-rt}$ where  $r$ is independent of the initial data.
+
 In future work, we would like to consider the optimal control problem with finite-time optimisation to minimise the filamentation width at the end time rather than instantaneously attempting to minimise its decay rate.
@@
 Our numerical study of local-in-time optimisation suggests that there is a limiting length scale, a generalised Batchelor length scale, which in turn determines a long-term mixing ``Batchelor rate".
+In dimensional form, this Batchelor rate was found to be proportional to $\Gamma$ for the fixed enstrophy case and $U^{2}/\kappa$ for the fixed energy case.
+These rates are consistent with those found in the context of the shell model.
 Although the Batchelor scale has been a theorised lower bound on the length scales present on turbulent flows, it has not been shown rigorously.
-We hope this numerical study provides insight and promotes investigation into proving what conditions are necessary on the flow for this to be the case.
+We hope this numerical study provides insight and promotes investigation into mathematically proving what conditions are necessary on the flow for this to be the case.
+Especially given that this limiting length scale is central cause of the mixing rate limitations.
 Furthermore, we showed that these limitations imply that (1), for fixed enstrophy optimal flows, strong diffusion can benefit from an early onset of a long-term mixing rate (where the rate itself however is independent of diffusion strength) while (2), for energy fixed optimal flows, strong diffusion weakens the long-term mixing rate.

### 2017-10-18 post_processing.py

@@ -71,4 +71,4 @@ def movie(time, scalar_hist, N, L, output_path='output/'):
     os.system("ffmpeg -y -framerate 20 -i " + output_path + 'images/'
               "image%04d.png -c:v libx264 -pix_fmt yuv420p " + output_path + "movies.mp4")
 
-    os.system('rm -r ' + output_path + 'images/')
+    # os.system('rm -r ' + output_path + 'images/')

### 2017-10-23 test/test_integrators.py
fixed bug with dt _cfl function. I initially introduced a prefactor to the function dt_cfl. This change propogated to functions which called it. This caused the time step to be too small when measuring the global error exponent. The errors for 1 time step and 2 time steps were on the order of machine error precision. Thus, RK4 algorithm was not capable of displaying the 4th order convergence. It might be useful to construct a function that makes sure that dt is not too small given this restriction placed by machine error. In other words, you can not make any further improvements by decreasing

@@ -75,6 +75,7 @@ def test_that_RK4_timestepper_has_fourth_order_convergence():
 
     # largest time step given by CFL condition
     dt0 = dt_cfl(N, L, kappa, U)
+    print("dt0 :", dt0)
     dt_list = dt0 * 2.0**(-np.arange(0, 3, 1))
     timesteps = 2**(np.arange(0, 3, 1))
     finalth_list = []
@@ -91,6 +92,8 @@ def test_that_RK4_timestepper_has_fourth_order_convergence():
 
     p = np.log2(error_large_small / error_medium_small - 1)
     print('p = ', p)
+    print('error_large_small=', error_large_small)
+    print('error_medium_small=', error_medium_small)
     assert abs(p - 4) < 0.1
 
 
@@ -109,7 +112,7 @@ def test_that_RK4_timestepper_using_hatted_formulation_has_fourth_order_converge
         return okit.sin_flow_op_hat(th_hat)
 
     # largest time step given by CFL condition
-    dt0 = dt_cfl(N, L, kappa, U)
+    dt0 = 0.1 * dt_cfl(N, L, kappa, U)
     dt_list = dt0 * 2.0**(-np.arange(0, 3, 1))
     timesteps = 2**(np.arange(0, 3, 1))
     finalth_list = []
@@ -126,6 +129,8 @@ def test_that_RK4_timestepper_using_hatted_formulation_has_fourth_order_converge
 
     p = np.log2(error_large_small / error_medium_small - 1)
     print('p = ', p)
+    print('error_large_small=', error_large_small)
+    print('error_medium_small=', error_medium_small)
     assert abs(p - 4) < 0.1
 
 

### 2017-10-23 run_simulations_on_flux.py
fixed bug with dt _cfl function. I initially introduced a prefactor to the function dt_cfl. This change propogated to functions which called it. This caused the time step to be too small when measuring the global error exponent. The errors for 1 time step and 2 time steps were on the order of machine error precision. Thus, RK4 algorithm was not capable of displaying the 4th order convergence. It might be useful to construct a function that makes sure that dt is not too small given this restriction placed by machine error. In other words, you can not make any further improvements by decreasing

@@ -3,10 +3,10 @@ from simulations import lit_enstrophy_sim
 
 if __name__ == "__main__":
     python_file = 'lit_enstrophy.py'
-    flux_folder_name = 'lit_enstrophy/'
+    flux_folder_name = 'lit_enstrophy2/'
     dict_of_parameter_lists = {'Pe': [8.0, 16.0, 32.0, 64.0, 128.0, 256.0,
                                       512.0, 1024.0, 2048.0, 4096.0, 8192.0, 16384.0],
-                               'N': [64, 128, 256, 512]}
+                               'N': [512]}
 
     fluxtools.run_python_file(
         python_file, dict_of_parameter_lists, flux_folder_name)

### 2017-10-23 test/test_tools.py

@@ -4,18 +4,12 @@ import math
 from tools import N_boyd
 
 
-# def test_N_boyd_should_return_50_given_M_10():
-#     assert N_boyd(10) == 50
-#
-#
-# def test_N_boyd_should_return_14_given_M_1():
-#     assert N_boyd(1) == 14
 def test_that_dt_cfl_works_for_kappa_0():
     N = 128
     L = 2.0
     kappa = 0.0
     U = 3.0
-    assert dt_cfl(N, L, kappa, U) == L / (N * U)
+    assert math.isclose(dt_cfl(N, L, kappa, U), L / (N * U))
 
 
 def test_that_l2norm_of_sinx_on_domain_with_L_of_2pi_equals_sqrt_of_half_of_Lsq():
@@ -212,14 +206,6 @@ def test_ifft_of_fft_equals_original_vector_function():
 
     vt = VectorTool(N, L)
     assert np.allclose(vt.ifft(vt.fft(u)), u)
-
-
-def test_particular_case_of_parameters_for_dt_cfl():
-    N = 128
-    L = 2.0
-    U = 1
-    kappa = 0.5
-    assert np.isclose(dt_cfl(N, L, kappa, U), 0.00048828125)
 
 
 def test_that_l2norm_of_vector_with_siny_for_xcomponent_equals_sqrt_of_half_of_Lsq():

### 2017-10-23 tools.py

@@ -20,11 +20,10 @@ def create_grid(N, L):
 
 
 def dt_cfl(N, L, kappa, U):
-    prefactor = 0.10
     if kappa == 0:
-        dt = prefactor * L / (N * U)
+        dt = L / (N * U)
     else:
-        dt = prefactor * min(L / (N * U), L**2 / (N**2 * kappa))
+        dt = min(L / (N * U), L**2 / (N**2 * kappa))
 
     return dt
 

### 2017-10-23 test/test_integrators.py
forgot to update python file. all test passed and dt_cfl bug is fixed

@@ -112,7 +112,7 @@ def test_that_RK4_timestepper_using_hatted_formulation_has_fourth_order_converge
         return okit.sin_flow_op_hat(th_hat)
 
     # largest time step given by CFL condition
-    dt0 = 0.1 * dt_cfl(N, L, kappa, U)
+    dt0 = dt_cfl(N, L, kappa, U)
     dt_list = dt0 * 2.0**(-np.arange(0, 3, 1))
     timesteps = 2**(np.arange(0, 3, 1))
     finalth_list = []

### 2017-10-23 fluxtools.py
about to create branch

@@ -117,6 +117,7 @@ def run_python_file(python_file, dict_of_parameter_lists, flux_folder_name, jobn
     os.system("mkdir " + flux_folder_name)
 
     # add all necessary python files
+    os.system("cp " + python_file + " " + flux_folder_name)
     os.system("cp operators.py " + flux_folder_name)
     os.system("cp post_processing.py " + flux_folder_name)
     os.system("cp sol_checking.py " + flux_folder_name)

### 2017-10-23 integrators.py

@@ -1,6 +1,5 @@
 import numpy as np
 import pyfftw
-import pdb
 
 
 def FE_timestepper(op, th0, dt):

### 2017-10-23 lit_enstrophy.py

@@ -7,7 +7,6 @@ import numpy as np
 import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
-import pdb
 
 import time
 import pickle
@@ -17,8 +16,6 @@ import sys
 if __name__ == "__main__":
     Pe = float(sys.argv[1])
     N = int(float(sys.argv[2]))
-    M = int(float(sys.argv[2]))
-
     # Parameters
     L = 1.0
     gamma = 1.0
@@ -28,7 +25,7 @@ if __name__ == "__main__":
     print('Pe = ', Pe)
     print('N = ', N)
 
-    [time_array, th] = lit_enstrophy_sim(N, L, Pe, T, M, cfl=True)
+    [time_array, th] = lit_enstrophy_sim(N, L, Pe, T, cfl=True)
 
     # Output
     output_folder = 'output-pe=%d' % Pe + '-N=%d' % N + '/'

### 2017-10-23 simulations.py

@@ -2,10 +2,9 @@ from integrators import RK4_timestepper, mega_RK4_timestepper, integrator2, inte
 from tools import create_grid, dt_cfl
 from operators import OperatorKit
 import numpy as np
-import pdb
 
 
-def lit_enstrophy_sim(N, L, Pe, T, reported_num_time_pts=100,  gamma=1.0, cfl=True):
+def lit_enstrophy_sim(N, L, Pe, T, reported_num_time_pts=100, gamma=1.0, cfl=True):
     kappa = 1.0 / Pe
 
     # Create tool box
@@ -21,14 +20,13 @@ def lit_enstrophy_sim(N, L, Pe, T, reported_num_time_pts=100,  gamma=1.0, cfl=Tr
     def sin_op(scalar):
         return okit.sin_flow_op(scalar)
 
-    # Perform simulation
     time_array = np.linspace(0, T, reported_num_time_pts)
 
     # perform perturbation
     th0 = RK4_timestepper(sin_op, th0, 0.001 * T)
+
     if cfl is True:
-        dt0_cfl = dt_cfl(N, L, kappa, gamma * L)
-        pdb.set_trace()
+        dt0_cfl = 0.01 * dt_cfl(N, L, kappa, gamma * L)
         th = integrator2(lit_enstrophy_op, mega_RK4_timestepper,
                          th0, time_array, dt0_cfl)
     else:

### 2017-10-23 lit_enstrophy.py
updated lit_enstrophy based on working version from scripts from earlier flux run

@@ -14,36 +14,65 @@ import os
 import sys
 
 if __name__ == "__main__":
-    Pe = float(sys.argv[1])
-    N = int(float(sys.argv[2]))
     # Parameters
     L = 1.0
-    gamma = 1.0
-    T = 6.0
-    kappa = 1.0 / Pe
-
+    Pe = float(sys.argv[1])
     print('Pe = ', Pe)
+    kappa = 1.0 / Pe
+    gamma = 1.0
+    T = 2.0
+
+    lb = (kappa / gamma)**0.5
+    l_smallest = lb
+    print('lb = ', lb)
+
+    M = L / l_smallest
+    print('N_boyd = ', N_boyd(M))
+    # N = min(N_boyd(M), 512)
+    # N = 64
+    N = 512
     print('N = ', N)
 
-    [time_array, th] = lit_enstrophy_sim(N, L, Pe, T, cfl=True)
+    # Create tool box
+    okit = OperatorKit(N, L, kappa)
+    st = ScalarTool(N, L)
+
+    # Initial condition
+    X = create_grid(N, L)
+    th0 = np.sin((2.0 * np.pi / L) * X[0])
+
+    # Create operators: d th / dt = operator (th)
+    def lit_enstrophy_op(scalar):
+        return okit.lit_enstrophy_op(scalar, gamma)
+
+    def sin_op(scalar):
+        return okit.sin_flow_op(scalar)
+
+    # Perform simulation
+    time_array = np.linspace(0, T, 200)
+    th0 = RK4_timestepper(sin_op, th0, 0.001)
+    start_time = time.time()
+    dt0_cfl = 0.25 * dt_cfl(N, L, kappa, gamma * L)
+    th = integrator2(lit_enstrophy_op, mega_RK4_timestepper,
+                     th0, time_array, dt0_cfl)
+
+    print(time.time() - start_time)
 
     # Output
-    output_folder = 'output-pe=%d' % Pe + '-N=%d' % N + '/'
+    output_folder = 'output-pe=%d' % Pe + '/'
     os.system('mkdir ' + output_folder)
     os.system('cp lit_enstrophy.py ' + output_folder)
 
     plt.figure()
-    st = ScalarTool(N, L)
     st.plot(th[-1])
-    plt.savefig(output_folder + 'plot_final_frame-pe=%d' %
-                Pe + '-N=%d' % N + '.png')
[…]

### 2017-10-23 lit_enstrophy.py
committing last changes before pulling

@@ -30,7 +30,7 @@ if __name__ == "__main__":
     print('N_boyd = ', N_boyd(M))
     # N = min(N_boyd(M), 512)
     # N = 64
-    N = 512
+    N = float(sys.argv[2])
     print('N = ', N)
 
     # Create tool box

### 2017-10-23 fluxtools.py
updated flux

@@ -118,6 +118,7 @@ def run_python_file(python_file, dict_of_parameter_lists, flux_folder_name, jobn
 
     # add all necessary python files
     os.system("cp " + python_file + " " + flux_folder_name)
+    os.system("cp simulations.py " + flux_folder_name)
     os.system("cp operators.py " + flux_folder_name)
     os.system("cp post_processing.py " + flux_folder_name)
     os.system("cp sol_checking.py " + flux_folder_name)

### 2017-10-23 lit_enstrophy.py

@@ -30,7 +30,7 @@ if __name__ == "__main__":
     print('N_boyd = ', N_boyd(M))
     # N = min(N_boyd(M), 512)
     # N = 64
-    N = float(sys.argv[2])
+    N = int(sys.argv[2])
     print('N = ', N)
 
     # Create tool box
@@ -50,9 +50,9 @@ if __name__ == "__main__":
 
     # Perform simulation
     time_array = np.linspace(0, T, 200)
-    th0 = RK4_timestepper(sin_op, th0, 0.001)
+    th0 = RK4_timestepper(sin_op, th0, 0.0001)
     start_time = time.time()
-    dt0_cfl = 0.25 * dt_cfl(N, L, kappa, gamma * L)
+    dt0_cfl = 0.1 * dt_cfl(N, L, kappa, gamma * L)
     th = integrator2(lit_enstrophy_op, mega_RK4_timestepper,
                      th0, time_array, dt0_cfl)
 

### 2017-10-24 fluxtools.py
removed fluxtools

@@ -1,173 +1,0 @@
-import numpy as np
-import os
-import sys
-
-
-def create_flux_pbs_script(path_to_place_pbs_script, script_file_name, python_file, dict_of_parameter_lists, jobname='flux_job', procs=1, memory_mb=4000, walltime='6:00:00', email='cmiless@umich.edu'):
-    """ creates a flux pbs script as output to enclosed folder. It will take in a function and lists of parameters to sweep over as input. """
-
-    # create file
-    f = open(path_to_place_pbs_script + script_file_name, 'w')
-
-    # Create PBS preamble and cd commands
-    f.write("""# !/bin/sh
-#### PBS preamble
-
-#PBS -N %s""" % jobname + """
-
-# Your email:
-#PBS -M  %s""" % email + """
-#PBS -m a
-#PBS -V
-
-# Change the number of cores (ppn=1), amount of memory, and walltime:
-#PBS -l procs=%s""" % str(procs) + "," + "pmem=%s" % str(memory_mb) + "mb,walltime=%s" % walltime + """
-
-# Change "example_flux" to the name of your Flux allocation:
-#PBS -A lsa_flux
-#PBS -q flux
-#PBS -l qos=flux
-
-# End PBS preamble
-
-
-#  Show list of CPUs you ran on, if you're running under PBS
-if [ -n "$PBS_NODEFILE" ]; then cat $PBS_NODEFILE; fi
-
-#  Change to the directory you submitted from
-if [ -n "$PBS_O_WORKDIR" ]; then cd $PBS_O_WORKDIR; fi
-
-#  Put your job commands here:
-
-description=("sim_number = $PBS_ARRAYID")
-echo $description
-
-""")
-
-    # Create parameter lists
-    for parameter_name, parameter_list in dict_of_parameter_lists.items():
-        f.write(str(parameter_name) + "_list=(")
-        for parameter in parameter_list:
-            f.write(" " + str(parameter))
-        f.write(" )\n")
-
-    # Create empty argments list and initialize counter
-    f.write("params=()\n")
-    f.write("count=1\n")
-    f.write("\n")
-
-    # create necessary for-loop statements in script file
-    single_indentation = "   "
-    for i, (parameter_name, parameter_list) in enumerate(dict_of_parameter_lists.items()):
-        indentation = single_indentation * i
-        f.write(indentation + "for %s" % parameter_name +
-                " in ${" + parameter_name + "_list[@]}\n")
-        f.write(indentation + "do\n")
-
[…]

### 2017-10-24 lit_enstrophy.py

@@ -28,9 +28,9 @@ if __name__ == "__main__":
 
     M = L / l_smallest
     print('N_boyd = ', N_boyd(M))
-    # N = min(N_boyd(M), 512)
+    N = min(N_boyd(M), 512)
     # N = 64
-    N = int(sys.argv[2])
+    # N = int(sys.argv[2])
     print('N = ', N)
 
     # Create tool box

### 2017-10-24 run_simulations_on_flux.py

@@ -5,8 +5,7 @@ if __name__ == "__main__":
     python_file = 'lit_enstrophy.py'
     flux_folder_name = 'lit_enstrophy2/'
     dict_of_parameter_lists = {'Pe': [8.0, 16.0, 32.0, 64.0, 128.0, 256.0,
-                                      512.0, 1024.0, 2048.0, 4096.0, 8192.0, 16384.0],
-                               'N': [512]}
+                                      512.0, 1024.0, 2048.0, 4096.0, 8192.0, 16384.0]}
 
     fluxtools.run_python_file(
         python_file, dict_of_parameter_lists, flux_folder_name)

### 2017-10-24 nonlinearity/manuscript.tex
removed fluxtools

@@
 In addition, diffusion is generally perceived as beneficial to mixing due to its ability to homogenise a passive tracer.
-However in the case where advection and diffusion are both actively present, we provide numerical evidence that diffusion in quite general cases produce nearly neutral or even {\it negative} effects by limiting the mixing effectiveness of incompressible optimal flows.
+However in the case where advection and diffusion are both actively present, we provide numerical evidence that diffusion produce nearly neutral or even {\it negative} effects by limiting the mixing effectiveness of incompressible optimal flows.
 The underlying mechanism causing this limitation appears to be due to the presence of a limiting length scale given by a generalised Batchelor length \cite{Batchelor1959a}.
@@
 The estimated costs due to poor industrial mixing in 1989 was \$1 -- \$10 billion US dollars for the chemical industry alone \cite{paul2004handbook}.
-Although mixing is highly prevalent and used, its fundamental principles are still not fully known especially concerning how the interplay of advection and diffusion processes affect mixing rates and achievable filamentation length scales.
+Although mixing is highly prevalent and used, its fundamental principles are still not fully known.
 
 The effect of diffusion and advection on the rate of fluid mixing depends on the particular mixing situation characterised by the unique fluid properties, specific mixing flow, and boundary geometry.
-In view of the vast complexity of the mixing situation, general principles of mixing underlying these various situations would be beneficial.
+Thus general principles of mixing underlying these various situations would be beneficial.
 In particular, it is valuable to determine how the mixing rate (typically the most optimal mixing rate) depends on aggregate flow intensity measures such as energy and enstrophy.
@@
 
-With these goals in mind, a common approach taken throughout the literature is to consider the evolution of a tracer quantity $\theta$ advected by an incompressible ($\nabla \cdot\vec{u}=0$) flow $\vec{u}$ with mild physical constraints within a periodic box  of side length $L$ in $d$ dimensions.
+With these goals in mind, a common approach taken throughout the literature is to consider the evolution of a tracer quantity $\theta (\vec{x},t)$ advected by an incompressible ($\nabla \cdot\vec{u}=0$) flow $\vec{u}$ with mild physical constraints within a periodic box  of side length $L$ in $d$ dimensions.
 The tracer concentration field $\theta$ evolves according to the advection-diffusion equation,
@@
 
-The $H^{-1}$ norm or mix-norm \cite{GM2005} is also a common measure of mixing used throughout the literature and will be used here.
-The $L^{2}$ norm $\ltwo{\theta}$ and the $H^{1}$ norm $\hone{\theta}$ are also common measures of mixing and will be considered here as well.
-For those interested in other measures of mixing, see \cite{JLT2012}.
-The $H^{-1}$ norm is given by
+The $H^{-1}$ norm or mix-norm \cite{GM2005} is a common measure of mixing used throughout the literature and will be used here. The $H^{-1}$ norm is given by  
 %
@@
 Thus we can see that the $H^{-1}$ embodies both senses.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{images/scale-and-intensity}
+	\caption{Top transformation is a reduction in the scale of segregation. Bottom transformation is a reduction in the intensity of segregation}
+\end{figure}
+
+The $L^{2}$ norm $\ltwo{\theta}$ and the $H^{1}$ norm $\hone{\theta}$ are also common measures of mixing and will be considered here as well.
+For those interested in other measures of mixing, see \cite{JLT2012}.
 
@@
 %
-\begin{equation}
+\begin{equation*}
 	\ddt{\lambda^2} = \frac{2}{Pe}
@@
 					  {\ltwo{\theta}^{2}}
-\end{equation}
+\end{equation*}
 and by H\"older's inequality, we deduce
-\begin{equation}
+\begin{equation*}
 \label{eq:length_ineq_rate-of-strain}
@@
 		\right] - 2  \lambda^2 .
-\end{equation}
+\end{equation*}
 This establishes a lower bound on $\lambda$ at each instant: by apply Gr\"onwall's inequality and the fact that the bracketed term is greater than or equal to zero, it follows that
@@
 %
-\numparts \begin{eqnarray}
+ \begin{eqnarray*}
 \frac{d}{dt}\left(\frac{\|\nabla\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}\right) &= \frac{\|\theta\|_{L^{2}}^2\frac{d}{dt}\|\nabla\theta\|_{L^{2}}^2-\|\nabla\theta\|_{L^{2}}^2\frac{d}{dt}\|\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^4}\\
 &= \frac{-2\int \partial_{i}u_{j}\partial_{i}\theta\partial_{j}\theta - \frac{2}{Pe} \|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}+\frac{2}{Pe}\frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \\
-&=-\frac{2}{Pe}\left(\frac{\|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2} - \frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \right) - 2\frac{\sint{\nabla\theta \cdot \nabla\vec{u} \cdot 
-							\nabla\theta  }}{\|\theta\|_{L^{2}}^2} 
+&=-\frac{2}{Pe}\left(\frac{\|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2} - \frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \right) \\
+& \qquad \qquad \qquad \qquad \qquad 
+- 2\frac{\sint{\nabla\theta \cdot \nabla\vec{u} \cdot \nabla\theta  }}{\|\theta\|_{L^{2}}^2} 
 \\
 &\leq 2 \frac{\hone{\theta}^2}{\ltwo{\theta}^2}
-\end{eqnarray} \endnumparts
+\end{eqnarray*}
 %
@@
 %
-\begin{eqnarray}
+\begin{eqnarray*}
 	 \hone{\theta}^2 &=& - 2\sint{\theta \lap \theta} \\
@@
 	 									+\frac{1}{Pe}\lap \theta\right)},
-\end{eqnarray}
+\end{eqnarray*}
 %
-\begin{eqnarray}
+\begin{eqnarray*}
 	\ddt{}\ltwo{\theta}^2 &=& 2\sint{\theta\ppt{\theta}} \\
@@
 	 									+\frac{1}{Pe}\lap \theta\right)} ,
-\end{eqnarray}
+\end{eqnarray*}
 %
@@
 %
-\begin{eqnarray}
+\begin{eqnarray*}
 	\ddt{}\hone{\theta}^2 &=& -2\sint{\ppt{\theta}\lap \theta} \\
@@
 	 									+\frac{1}{Pe}\lap \theta\right)^2} .
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 			}\\
-			&=& \frac{1}{\ltwo{\theta}^4}
-			\sbrac{
-				\ltwo{\theta}^2
-				\pbrac{
-					Pe \sint{\left(\ppt{\theta}
-	 									-\frac{1}{Pe}\lap \theta\right)^2} 
- 					-Pe\sint{\left(\ppt{\theta}
-	 									+\frac{1}{Pe}\lap \theta\right)^2} 
-				}
-			}\\
+			&=& \frac{1}{\ltwo{\theta}^2}
+			 \Bigg[ Pe \sint{\left(\ppt{\theta} -\frac{1}{Pe}\lap \theta\right)^2}  \\
+ 				& & \qquad\qquad\qquad \qquad \qquad 
+				-Pe\sint{\left(\ppt{\theta}+\frac{1}{Pe}\lap \theta\right)^2} 
+			\Bigg]\\
 		        &-&\frac{1}{\ltwo{\theta}^4}
-			\sbrac{
-				Pe
-				\pbrac{
-					 \sint{\theta\left(\ppt{\theta}
-	 									-\frac{1}{Pe}\lap \theta\right)} 
- 				}^2		
- 				-
- 				Pe
- 				\pbrac{
+			\Bigg[ 
+				Pe \pbrac{\sint{\theta\left(\ppt{\theta}-\frac{1}{Pe}\lap \theta\right)} }^2\\
+ 				& & \qquad\qquad\qquad \qquad
+				-Pe\pbrac{
 					 \sint{\theta\left(\ppt{\theta}
@@
  				}^2					
-			}.
+			\Bigg].
 \end{eqnarray*}
@@
 %
-\begin{equation}
+\begin{equation*}
 		\frac{\hone{\theta}}{\ltwo{\theta}} 
@@
 		\exp{\pbrac{\frac{Pe}{2} t}}.
-\end{equation}
+\end{equation*}
 %
@@
 %
-\begin{equation}
+\begin{equation*}
 \ltwo{\theta}\geq \ltwo{\theta_{0}}\exp\left[-\frac{1}{Pe^2}\frac{\hone{\theta_0}^2}{\ltwo{\theta_0}^2}\left(e^{Pe \, \, t}-1\right)\right]
-\end{equation}
+\end{equation*}
 %

### 2017-10-24 nonlinearity/manuscript.tex
added some of uriahs edits

@@
 
-The $H^{-1}$ norm or mix-norm \cite{GM2005} is a common measure of mixing used throughout the literature and will be used here. The $H^{-1}$ norm is given by  
+We now would like to measure the `mixed-ness' of $\theta$.
+In the pioneering work of P.
+V.
+Danckwerts (1952)\cite{Danckwerts1952}, the author identifies two measures of mixedness: the scale of segregation and the intensity of segregation.
+The {\it scale of segregation } quantifies the characteristic length scale present in the tracer concentration $\theta$.
+For instance, the process of thinning, elongating, and folding of a blob, as seen in the top graphic of figure \ref{fig:scale-and-intensity}, reduces the scale of segregation by creating a rich maze-like pattern with thin strands of dye.
+We will refer to mixing by the reduction of the scale of segregation as {\it filamentation}.
+On the other hand, the {\it intensity of segregation } quantifies the variation of the concentration amplitude.
+The bottom graphic of figure \ref{fig:scale-and-intensity} shows a reduction in the overall variation and the concentration tends towards a state with uniform concentration.
+We will refer to the reduction of the intensity of segregation as {\it homogenisation}.
+
+The scale and intensity of segregation are both quantified by a single mixing measure known as $H^{-1}$ norm or mix-norm \cite{GM2005}.
+This is a common measure of mixing throughout the literature and is defined by
 %
@@
 %
-where $\nabla^{-1}=\nabla \Delta^{-1}$, the operator $\Delta^{-1}$ acting on  a function $\rho$ returns the solution $\phi$ of the Poisson equation $ \Delta \phi = \rho $, and $\hat{\theta}_{\vec{k}}(t) =  \frac{1}{L^{d}}\sint{\theta(\vec{x},t)e^{-i\vec{k}\cdot\vec{x}}}$.
+where $\nabla^{-1}=\nabla \Delta^{-1}$, the operator $\Delta^{-1}$ acting on  a function $\rho$ returns the solution $\phi$ of the Poisson equation $ \Delta \phi = \rho $, $\hat{\theta}_{\vec{k}}(t) =  \frac{1}{L^{d}}\sint{\theta(\vec{x},t)e^{-i\vec{k}\cdot\vec{x}}}$, and $\vec{k}$ is the wave number.
 Lower values of the  $H^{-1}$ norm correspond to a more mixed state.
 Note that $H^{-1}$ norm can decrease in two ways.
-The first way is to decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ for $\vec{k}\neq 0$.
-This matches our first sense of mixing --- {\it homogenisation}.
-The second way is by transferring spectral mass from the lower wave numbers to the higher wave numbers to take advantage of the $1/|\vec{k}|^2$ dependence.
-This produces a scalar field with sharp gradients and small length scales which matches our second sense of mixing --- {\it filamentation}.
-Thus we can see that the $H^{-1}$ embodies both senses.
+The first way is by transferring spectral mass from the lower wave numbers to the higher wave numbers to take advantage of the $1/|\vec{k}|^2$ dependence.
+This produces a scalar field with sharp gradients and small length scales.
+This corresponds to the reduction of scale of segregation or filamentation.
+The second way is to decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ for $\vec{k}\neq 0$.
+This corresponds to a reduction in the intensity of segregation, or homogenisation.
+Thus we can see that the $H^{-1}$ embodies both senses of mixing.
 
@@
 	\includegraphics[width=0.5\textwidth]{images/scale-and-intensity}
-	\caption{Top transformation is a reduction in the scale of segregation. Bottom transformation is a reduction in the intensity of segregation}
+	\caption{Filamentation is the reduction of the scale of segregation as illustrated by the top transformation.
+Homogenisation is the reduction of the intensity of segregation as illustrated by the bottom transformation.}
+	\label{fig:scale-and-intensity}
 \end{figure}
@@
 
-In the case without advection ($\vec{u}=\vec{0}$), equation \eref{eq:PDE_advection} reduces to the classical heat equation \cite{Evans2010}.
-The Fourier modes evolve according to $\hat{\theta}_{\vec{k}}(t)=\hat{\theta}_{\vec{k}}(0)e^{-\kappa|\vec{k}|^2t}$.
+In the case without advection ($\vec{u}=\vec{0}$), equation \eref{eq:PDE_advection} reduces to the classical heat equation \cite{Evans2010} and the Fourier modes evolve according to $\hat{\theta}_{\vec{k}}(t)=\hat{\theta}_{\vec{k}}(0)e^{-\kappa|\vec{k}|^2t}$.
 Thus we have explicit analytical results for the decay of the $H^{-1}$ mix-norm by simply substituting this result.
@@
 
-In the case without diffusion ($\kappa = 0$), pure advection of the flow is the only method of mixing or colloquially known as stirring.
+In the case without diffusion ($\kappa = 0$), pure advection of the flow is the only method of mixing, colloquially known as stirring.
 For a flow that is constrained by enstrophy, the mix-norm decays at most exponentially where the exponential rate is proportional to $\Gamma$ \cite{GI2014,CS2013}.
@@
 In fact they can achieve {\it perfect mixing in finite time} which means that the $H^{-1}$ mix-norm approaches zero in finite time as opposed to approaching zero in infinite time as in the case for enstrophy-constrained mixing.
-This can be demonstrated by a `chequerboard' flow \cite{JMP2012} where the mix-norm achieves perfect mixing in finite time by a linear decay rate.
+This can be demonstrated by a `chequerboard' flow \cite{JMP2012} where the mix-norm achieves perfect mixing in finite time with a linear decay rate.
 In either flow intensity constraint, note that $H^{-1}$ mix-norm decreases by exclusively exploiting filamentation without homogenisation.
@@
 We will demonstrate that homogenisation via diffusion and filamentation via advection can sometimes be in conflict and collectively produce a negative impact on mixing.
-We show numerical evidence that filamentation length scale appears to be limited by the Batchelor scale as seen in the shell model.
-Even when actively trying to choose the most optimal flow to enhance filamentation.
+We show numerical evidence that filamentation length scale appears to be limited by the Batchelor scale as seen in the shell model, even when actively trying to choose the most optimal flow to enhance filamentation.
 Thus, this may suggest that the Batchelor scale does not only limit turbulent flows but also all incompressible flows under the flow constraints considered here.
@@
 We will consider the evolution of a tracer quantity $\theta$ governed by equation \ref{eq:PDE_advection} under an the incompressible flow $\vec{u}$.
-Recall the flow is constrained by $\ltwo{\nabla\u} = \Gamma L^{d/2}$ or energy $\ltwo{\u} = UL^{d/2}$ where $\Gamma$ is the root mean square rate-of-strain and $U$ is the root mean square speed.
+Recall the flow is constrained by enstrophy $\ltwo{\nabla\u} = \Gamma L^{d/2}$ or energy $\ltwo{\u} = UL^{d/2}$ where $\Gamma$ is the root mean square rate-of-strain and $U$ is the root mean square speed.
 
@@
 
-We consider the local-in-time optimisation strategy first introduced by \cite{JFM2011} in the diffusion-less case.
+We consider the local-in-time optimisation strategy first introduced by \cite{JFM2011} in the case without diffusion.
 We find that this strategy generalises to the case with diffusion.
 The local-in-time optimal velocity fields maximise the instantaneous mixing rate by minimising $\ddt{}\hmone{\theta}^2$.
-The optimal velocity fields are given instantaneously by (in non-dimensional form)
+The optimal velocity fields are given instantaneously for the enstrophy case by (in non-dimensional form)
+%
+\begin{equation}
+\mathbf{u}= \frac{-\invlap\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\nabla^{-1}\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
+\end{equation}
+%
+and for the energy case by 
 % 
@@
 %
-for the energy constraint and by 
-%
-\begin{equation}
-\mathbf{u}= \frac{-\invlap\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\nabla^{-1}\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
-\end{equation}
-%
-for the enstrophy constraint where $\mathds{P}$ is the Leray divergence-free projector given by $\mathds{P}(\vec{v}) = \vec{v} - \nabla \Delta^{-1}(\nabla \cdot \vec{v})$.
+where $\mathds{P}$ is the Leray divergence-free projector given by $\mathds{P}(\vec{v}) = \vec{v} - \nabla \Delta^{-1}(\nabla \cdot \vec{v})$ and $\langle \cdot \rangle$ is the spatial average.
 These flows will be studied numerically later and is the main focus of this paper.
@@
 \end{equation}
-Note that $\lambda(t)$ returns the wavelength of the wave number $\vec{k}$ for a tracer concentration field composed only of the Fourier mode with wave number $\vec{k}$ (i.e.
-$\theta(\vec{x},t) = Re[ A e^{-i\vec{k}\cdot \vec{x}}]$ where $A$ is a complex constant).
+Note that if the tracer concentration field is composed of only one Fourier mode with wave number $\vec{k}$ (i.e.
+$\theta(\vec{x},t) = Re[ A e^{-i\vec{k}\cdot \vec{x}}]$ where $A$ is a complex constant), then $\lambda(t)$ returns the wavelength of the wave number $\vec{k}$.
 In general, $\lambda$ is the weighted root mean square wavelength with weights given by $|\theta_{\vec{k}}|/\ltwo{\theta}$.
@@
 
-The shell model is a reduced model of the spectral dynamics present in the advection-diffusion equation.
+The shell model is a reduced model but still represents the spectral dynamics present in the advection-diffusion equation.
 The model consists of a system of ordinary differential equations with nearest-neighbour coupling between `shells' in wave number space.
@@
 &= \frac{-2\int \partial_{i}u_{j}\partial_{i}\theta\partial_{j}\theta - \frac{2}{Pe} \|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}+\frac{2}{Pe}\frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \\
-&=-\frac{2}{Pe}\left(\frac{\|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2} - \frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \right) \\
-& \qquad \qquad \qquad \qquad \qquad 
-- 2\frac{\sint{\nabla\theta \cdot \nabla\vec{u} \cdot \nabla\theta  }}{\|\theta\|_{L^{2}}^2} 
+&=-\frac{2}{Pe}\left(\frac{\|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2} - \frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \right) - 2\frac{\sint{\nabla\theta \cdot \nabla\vec{u} \cdot \nabla\theta  }}{\|\theta\|_{L^{2}}^2}
 \\
@@
 
-We solve \eref{eq:nd_ade} by using a Fourier basis to represent the $512 \times 512$ discretised spatial domain with a 4th order Runge-Kutta time-stepping method.
+We solve \eref{eq:nd_ade} by using a Fourier basis to represent the discretised spatial domain with a 4th order Runge-Kutta time-stepping method.
 All simulation code was created in the programming language Python with package modules, pyfftw and numpy.
@@
 The time evolution is initially similar but soon diverges over time.
-Figure \ref{fig:energy_film} shows the evolution for the energy case.
+Figure \ref{fig:energy_film} shows the evolution for the energy constraint.
 The top film strip corresponds to $Pe =\infty$ while the bottom is $Pe = 32$.

### 2017-11-01 paper/manuscript.tex
updated pos_processing and renamed journal article folder

--- 2017-10-24 nonlinearity/manuscript.tex
@@
 In addition, diffusion is generally perceived as beneficial to mixing due to its ability to homogenise a passive tracer.
-However in the case where advection and diffusion are both actively present, we provide numerical evidence that diffusion produce nearly neutral or even {\it negative} effects by limiting the mixing effectiveness of incompressible optimal flows.
-The underlying mechanism causing this limitation appears to be due to the presence of a limiting length scale given by a generalised Batchelor length \cite{Batchelor1959a}.
+However we provided numerical evidence that, in the case where advection and diffusion are both actively present, diffusion produces nearly neutral or even {\it negative} effects by limiting the mixing effectiveness of incompressible optimal flows.
+This limitation appears to be due to the presence of a limiting length scale given by a generalised Batchelor length \cite{Batchelor1959a}.
 This length scale limitation in turn affects long-term mixing rates.
@@
 We provide analytical lower bounds on mixing rates and length scales achievable under related constraints (point-wise bounded speed and rate-of-strain) by extending the work of Z.
-Lin {\it et.
-al.} \cite{JFM2011} and C.-C.
+Lin {\it et al.} \cite{JFM2011} and C.-C.
 Poon \cite{Chi-Cheu1996}.
-
 \end{abstract}
@@
 % Uncomment for Submitted to journal title message
-\submitto{\NL}
+% \submitto{\NL}
 %
@@
 It also serves as a key industrial process within the food, pharmaceutical, petrochemical, and other industries \cite{paul2004handbook}.
-The estimated costs due to poor industrial mixing in 1989 was \$1 -- \$10 billion US dollars for the chemical industry alone \cite{paul2004handbook}.
 Although mixing is highly prevalent and used, its fundamental principles are still not fully known.
 
-The effect of diffusion and advection on the rate of fluid mixing depends on the particular mixing situation characterised by the unique fluid properties, specific mixing flow, and boundary geometry.
-Thus general principles of mixing underlying these various situations would be beneficial.
+The effect of diffusion and advection on the rate of fluid mixing depends on the unique fluid properties, specific mixing flow, and boundary geometry.
+Thus general principles of mixing applicable to the vast variety of mixing situations would be beneficial.
 In particular, it is valuable to determine how the mixing rate (typically the most optimal mixing rate) depends on aggregate flow intensity measures such as energy and enstrophy.
@@
 
-We now would like to measure the `mixed-ness' of $\theta$.
+We also need a measure of `mixed-ness'.
 In the pioneering work of P.
@@
 On the other hand, the {\it intensity of segregation } quantifies the variation of the concentration amplitude.
-The bottom graphic of figure \ref{fig:scale-and-intensity} shows a reduction in the overall variation and the concentration tends towards a state with uniform concentration.
-We will refer to the reduction of the intensity of segregation as {\it homogenisation}.
+We will refer to mixing by the reduction of the intensity of segregation as {\it homogenisation}.
+This process is illustrated by the bottom graphic of figure \ref{fig:scale-and-intensity}.
 
-The scale and intensity of segregation are both quantified by a single mixing measure known as $H^{-1}$ norm or mix-norm \cite{GM2005}.
+ $H^{-1}$ norm or mix-norm \cite{GM2005} is a single measure of mixing that accounts for both the scale and intensity of segregation.
 This is a common measure of mixing throughout the literature and is defined by
@@
 This corresponds to the reduction of scale of segregation or filamentation.
-The second way is to decreasing the amplitudes of $|\hat{\theta}_{\vec{k}}|$ for $\vec{k}\neq 0$.
+The second way is to decrease the Fourier amplitudes $|\hat{\theta}_{\vec{k}}|$ for $\vec{k}\neq 0$.
 This corresponds to a reduction in the intensity of segregation, or homogenisation.
@@
 Thus we have explicit analytical results for the decay of the $H^{-1}$ mix-norm by simply substituting this result.
-Note that $H^{-1}$ mix-norm will surely decay monotonically.
+Note that $H^{-1}$ mix-norm will decay monotonically.
 Diffusion is unable to transfer spectral mass from the low wave number modes to the high wave number modes and thus is incapable of filamentation.
@@
 This was mathematically proven by two separate approaches: G.
-Iyer {\it et.
-al.} \cite{GI2014} used regularisation results of partial differential equations \cite{Crippa} while C.
+Iyer {\it et al.} \cite{GI2014} used regularisation results \cite{Crippa} of partial differential equations  while C.
 Seis \cite{CS2013} used methods from optimal transportation theory \cite{villani2003topics}.
@@
 Finally, the case with diffusion and advection is the least explored in this framework and the focus of this paper.
-It is known that the evolution of the $H^{-1}$ and $L^2$ norms decrease monotonically under the chequerboard flow introduced by \cite{JMP2012}
- while the $H^{1}$ increases until it reaches a peak and then decreases \cite{DF2014}.
+D.
+Foures {\it et al.} \cite{DF2014} showed that the evolution of the $H^{-1}$ and $L^2$ norms decrease monotonically under the chequerboard flow introduced by E.
+Lunasin {\it et al.} \cite{JMP2012} while the $H^{1}$ increases until it reaches a peak and then decreases.
 This peak corresponds to a  time when the length scales developed are small enough for diffusion to effectively act on steep gradients.
@@
 These length scales can be identified as a generalised Batchelor scale \cite{Batchelor1959a}, introduced in the context of turbulence theory.
-These limitations on the length scale in turn controlled the long-run optimal mixing rates determined to be $\Gamma$ under the enstrophy constraint and $U^2/\kappa$ under the energy constraint up to $O(1)$ constants.
+The limitations on the length scale controlled the long-run optimal mixing rates determined to be $\Gamma$ under the enstrophy constraint and $U^2/\kappa$ under the energy constraint up to $O(1)$ constants.
 In contrast to the `pure' cases mentioned earlier, it is important to note that the $H^{-1}$ can now decrease by the two avenues of homogenisation and filamentation simultaneously.
@@
 
-We approach the posed question by considering the general setup introduced of the evolution of passive scalar in a periodic box.
+We approach the posed question by considering the general setup introduced earlier of the evolution of passive scalar in a periodic box.
 We consider the local-in-time optimisation problem first introduced by Z.
-Lin {\it et.
-al.} \cite{JFM2011} in the context of diffusion.
+Lin {\it et al.} \cite{JFM2011}, but now in the context of diffusion.
 Local-in-time optimisation seeks to find the optimal flow that achieves the best instantaneous mixing rate.
@@
 
-We consider the local-in-time optimisation strategy first introduced by \cite{JFM2011} in the case without diffusion.
+We consider the local-in-time optimisation strategy first introduced by Lin {\it et al.} \cite{JFM2011} in the case without diffusion.
 We find that this strategy generalises to the case with diffusion.
@@
 
-The shell model is a reduced model but still represents the spectral dynamics present in the advection-diffusion equation.
+The shell model is a model that mimics the spectral dynamics present in the advection-diffusion equation.
 The model consists of a system of ordinary differential equations with nearest-neighbour coupling between `shells' in wave number space.
@@
 The non-dimensional versions are given by $\lambda_{\Gamma}= \frac{1}{\sqrt{Pe}}$ and $\lambda_{U} = \frac{1}{Pe}$.
-Also from here forward, we will refer to the Batchelor scale to mean either $\lambda_{\Gamma}$ or its generalisation $\lambda_{U}$.
-The predicted long-term rates (after reaching the Batchelor scale) are given by $R_{\Gamma} =\kappa/\lambda_{\Gamma}^2 $  and  $R_{U}=\kappa/\lambda_{U}^2$  The non-dimensional versions are given by $r_{\Gamma} =1$ and $r_{U} = Pe $.
+From here forward, we will refer to the Batchelor scale to mean either $\lambda_{\Gamma}$ or its generalisation $\lambda_{U}$.
+The predicted long-term rates (after reaching the Batchelor scale) are given by $R_{\Gamma} =\kappa/\lambda_{\Gamma}^2 $  and  $R_{U}=\kappa/\lambda_{U}^2$.
+The non-dimensional versions are given by $r_{\Gamma} =1$ and $r_{U} = Pe $.
 
@@
 
-%
 \section{Numerical experiment: local-in-time optimisation}
@@
 \begin{figure}
+\includegraphics[width=\textwidth]{images/enstrophy_norms}
+\caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal enstrophy-constrained flow.  }
+\label{fig:enstrophy_norms}
+\end{figure}
+%
+\begin{figure}
+\includegraphics[width=\textwidth]{images/energy_norms}
+\caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal energy-constrained flow.}
+\label{fig:energy_norms}
+\end{figure}
+
+We now investigate the mixing performance under the local-in-time optimal flows.
+Figure \ref{fig:enstrophy_norms} and \ref{fig:energy_norms} show how the different mixing measures ($H^{-1}$, $L^2$, and $H^{1}$ norms) vary in time for different values of $Pe$ for the enstrophy and energy constrained cases respectively.
+Notice how the long-term mixing rate appears to be exponential for all three mixing measures.
+This exponential rate is consistent with shell model predictions, yet weaker than the double-exponential decay rate derived by the $L^{\infty}$ constrained flow analysis.
+
+\begin{figure}
 \includegraphics[width=\textwidth]{images/enstrophy_film}
@@
 Note that the grey-scale for the $Pe=\infty$ is constant in time while it is adjusted to show the tracer concentration structure in the finite $Pe$ case.
-}
+The numerical computation is truncated at time $t=0.34$ due to length scales rapidly decreasing past the grid size resolution immediately after $t=0.34$.
+Fixed energy constrained flows that produce infinitesimally small lengths in finite time have been constructed \cite{JMP2012}.
+We suspect that the same phenomena may be occurring here.}
 \label{fig:energy_film}
-\end{figure}
-%
-\begin{figure}
-\includegraphics[width=\textwidth]{images/enstrophy_norms}
-\caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal enstrophy-constrained flow.  }
-\label{fig:enstrophy_norms}
-\end{figure}
-%
-\begin{figure}
-\includegraphics[width=\textwidth]{images/energy_norms}
-\caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal energy-constrained flow.}
-\label{fig:energy_norms}
 \end{figure}
@@
 
-Figure \ref{fig:enstrophy_rate} shows the mixing rates for the enstrophy case.
+The mixing rates for the enstrophy case are shown in Figure \ref{fig:enstrophy_rate}.
 The rate during the transient phase is $\Gamma$ which is consistent with rates expected from $Pe=\infty$ mixing studies.
@@
 
-Although it should be noted that the onset of the long-term rate is affected by the value of $Pe$.
+It should be noted that the onset of the long-term rate is affected by the value of $Pe$.
 When there is strong diffusion (small $Pe$), the Batchelor scale is reached quickly.
-From the work of \cite{GI2014} and \cite{CS2013}, we know that $\lambda$ decreases at most exponentially for $Pe = \infty$.
+From the work of G.
+Iyer {\it et al.} \cite{GI2014} and C.
+Seis \cite{CS2013}, we know that $\lambda$ decreases at most exponentially for $Pe = \infty$.
 If we assume that the local-in-time optimal flows nearly saturate this bound in the transient phase, we model $\lambda$ as  $\lambda (t) = \lambda(0)\exp(- \alpha t) $ during this time.
@@
 
- For the enstrophy case, we saw a benefit of picking a lower $Pe$ to result in a earlier onset of the long-term mixing behaviour.
-The fixed energy case however is different.
-The onset of the long run-mixing behaviour can be determined by the following model.
-From the work of \cite{JMP2012} on the fixed energy case, $\lambda(t)$ can decrease linearly in time to produce perfect mixing in finite time.
+For the energy case, the onset of the long run-mixing behaviour can be determined by the following model.
+From the work of E.
+Lunasin {\it et al.} \cite{JMP2012} on the fixed energy case, $\lambda(t)$ can decrease linearly in time to produce perfect mixing in finite time.
 We model the transient phase as $\lambda(t)=\lambda(0)(1-\beta t)$.
@@
 \label{sec:discussion}
-The local-in-time optimisation results suggest that there is a limiting length scale for passive tracer mixing whenever flows are optimised to decrease the mix-norm.
-The bounds derived under the $L^{\infty}$ constrained flow assumption did not result in proving either of these observations, but they did definitively rule out the possibility of perfect mixing in finite time for either constraint.
-These bounds could be drastically improved: we surmise that the deficiencies in these analyses may be due to not fully exploiting the incompressibility condition in the estimates.
-It remains to be shown that $\liminf_{t\rightarrow \infty} \lambda (t)\geq C\lambda_{\Gamma}$ where C is constant dependent on domain and initial condition under an enstrophy constrained flow.
-A similar problem remains open for the fixed energy case.
-If these statements can be shown, then many of the results demonstrated here computationally will hold more generally.
+%
+The local-in-time optimisation results suggest that there is a limiting length scale for passive tracer mixing whenever $L^{2}$ flows are instantaneously optimised to decrease the mix-norm.
+The bounds derived under the $L^{\infty}$ constrained flow assumption did not result in proving this observation, but they did definitively rule out the possibility of perfect mixing in finite time for $L^{\infty}$ flow constraints.
 
-Note that the pure diffusive case discussed in the introduction can always be employed as a mixing strategy by simply not having a flow field at all ($\vec{u} =\vec{0}$) provided that the flow intensity constraints are generalised to inequalities such as $\|\vec{u}\| \leq UL^{d/2}$ and $\|\nabla \vec{u}\| \leq \Gamma L^{d/2}$.
- This is a valuable strategy if one is content with mixing at a long-term rate of $\kappa k_{\min}^2$ where $k_{\min} = \min \{ |\vec{k}|  :  |\hat{\theta}_{\vec{k}}(0)| > 0  \}$.
+We suspect that the bounds obtained for $L^{\infty}$ flows are not sharp and could be improved further.
+The $L^{\infty}$ flow analysis produced a double-exponential lower bound on the $H^{-1}$ mix-norm rather than exponential as possibly expected given the numerical results for local-in-time optimal $L^2$ flows.
+The double-exponential bounds arise from the use of exponential upper bounds on the quantity $\frac{\hone{\theta}}{\ltwo{\theta}}$ in time for both $L^{\infty}$ flow constraints considered.
+We surmise that $\frac{\hone{\theta}}{\ltwo{\theta}} < C$ (where $C$ is a constant) for all time $t$ as supported by our numerical results and may be proven by exploiting the incompressiblity condition.
+If this is true generally for all $L^{\infty}$  flows, then our previous analysis would demonstrate that the $H^{-1}$ mix-norm is bounded below by an exponential.
+
+Note that the pure diffusive case discussed in the introduction can always be employed as a mixing strategy by simply not having a flow field at all ($\vec{u} =\vec{0}$) provided that the flow intensity constraints are generalised to inequalities such as $\|\vec{u}\| \leq UL^{d/2}$ and $\|\nabla \vec{u}\| \leq \Gamma L^{d/2}$.This is a valuable strategy if one is content with mixing at a long-term rate of $\kappa k_{\min}^2$ where $k_{\min} = \min \{ |\vec{k}|  :  |\hat{\theta}_{\vec{k}}(0)| > 0  \}$.
 This may be advised in fact if $k_{\min} > 2 \pi / \lambda_{B}$.
@@
 It is important to keep this simple strategy in mind when trying to rigorously prove bounds on the mix-norm.
-The existence of this strategy has an important implication.
-There does not exist a lower bound on the mix-norm of the form $\hmone{\theta} \geq A e^{-rt}$ where  $r$ is independent of the initial data.
+This strategy has an important implication --- there does not exist a lower bound on the mix-norm of the form $\hmone{\theta} \geq A e^{-rt}$ where  $r$ is independent of the initial data.
 
-In future work, we would like to consider the optimal control problem with finite-time optimisation to minimise the filamentation width at the end time rather than instantaneously attempting to minimise its decay rate.
-This might lead to flows that are able to extend to even smaller length scales.
-Finite-time optimisation was explored in \cite{Miles2017a} in the context of the shell model where it was found that global-in-time and local-in-time optimisation appeared to give similar mixing rates.
-Fore the shell model, however, the analysis was consistent with computation.
-In the PDE case the gap between analysis and computation remains to be closed.
+In future work, we would like to consider the optimal control problem with finite-time optimisation to minimise the $H^{-1}$ mix-norm at the end time rather than instantaneously attempting to minimise its decay rate.
+This might lead to flows that can produce even smaller length scales.
+In Miles and Doering \cite{Miles2017a}, finite-time optimisation was explored in the context of the shell model where it was found that global-in-time and local-in-time optimisation appeared to give similar mixing rates.
+For the shell model, however, the analysis was consistent with computation.
+In the partial differential equation case, the gap between analysis and computation remains to be closed.
 
@@
 These rates are consistent with those found in the context of the shell model.
-Although the Batchelor scale has been a theorised lower bound on the length scales present on turbulent flows, it has not been shown rigorously.
-We hope this numerical study provides insight and promotes investigation into mathematically proving what conditions are necessary on the flow for this to be the case.
-Especially given that this limiting length scale is central cause of the mixing rate limitations.
-Furthermore, we showed that these limitations imply that (1), for fixed enstrophy optimal flows, strong diffusion can benefit from an early onset of a long-term mixing rate (where the rate itself however is independent of diffusion strength) while (2), for energy fixed optimal flows, strong diffusion weakens the long-term mixing rate.
+Although the Batchelor scale has been a theorised lower bound on the length scales present on turbulent flows, it has not been proven rigorously.
+We hope this numerical study provides insight and promotes investigation into mathematically proving what conditions are necessary on the flow for a length scale limitation.
+This is especially important since it plays a crucial role in the achievable mixing rates.
+Furthermore, we provided numerical evidence that (1), for fixed enstrophy optimal flows, strong diffusion can benefit from an early onset of a long-term mixing rate (where the rate itself however is independent of diffusion strength) while (2), for energy fixed optimal flows, strong diffusion weakens the long-term mixing rate.
 
 \section*{Acknowledgements}
-We gratefully acknowledge helpful comments from Hongjie Done, Luis Escauriaza, Guatum Iyer, Alexander Kiselev, Anna Mazzucato, Christian Seis, Ian Tobasco, and Karen Zaya.
+We gratefully acknowledge helpful comments from Hongjie Dong, Luis Escauriaza, Guatum Iyer, Alexander Kiselev, Anna Mazzucato, Christian Seis, Ian Tobasco, and Karen Zaya.
 This work was supported in part by NSF Awards PHY-1205219 and DMS-1515161.

### 2018-02-14 paper/manuscript.tex
added reviewer 1 changes

@@
 Incompressible flows can be effective mixers by appropriately advecting a passive tracer to produce small filamentation length scales.
-In addition, diffusion is generally perceived as beneficial to mixing due to its ability to homogenise a passive tracer.
+In addition, diffusion is generally perceived as beneficial to mixing due to its ability to homogenize a passive tracer.
 However we provided numerical evidence that, in the case where advection and diffusion are both actively present, diffusion produces nearly neutral or even {\it negative} effects by limiting the mixing effectiveness of incompressible optimal flows.
@@
 On the other hand, the {\it intensity of segregation } quantifies the variation of the concentration amplitude.
-We will refer to mixing by the reduction of the intensity of segregation as {\it homogenisation}.
+We will refer to mixing by the reduction of the intensity of segregation as {\it homogenization}.
 This process is illustrated by the bottom graphic of figure \ref{fig:scale-and-intensity}.
@@
 The second way is to decrease the Fourier amplitudes $|\hat{\theta}_{\vec{k}}|$ for $\vec{k}\neq 0$.
-This corresponds to a reduction in the intensity of segregation, or homogenisation.
+This corresponds to a reduction in the intensity of segregation, or homogenization.
 Thus we can see that the $H^{-1}$ embodies both senses of mixing.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{images/scale-and-intensity}
+	\includegraphics[width=0.5\textwidth]{scale-and-intensity}
 	\caption{Filamentation is the reduction of the scale of segregation as illustrated by the top transformation.
-Homogenisation is the reduction of the intensity of segregation as illustrated by the bottom transformation.}
+homogenization is the reduction of the intensity of segregation as illustrated by the bottom transformation.}
 	\label{fig:scale-and-intensity}
@@
 Diffusion is unable to transfer spectral mass from the low wave number modes to the high wave number modes and thus is incapable of filamentation.
-Thus the pure diffusion case solely exploits homogenisation.
-Also notice the unequal weighting attach to each mode.
+Thus the pure diffusion case solely exploits homogenization.
+Also notice the unequal weighting attached to each mode.
 The Fourier modes with large wave number $|\vec{k}|$ decay at a faster rate relative to the decay of those with small wave number.
@@
 This can be demonstrated by a `chequerboard' flow \cite{JMP2012} where the mix-norm achieves perfect mixing in finite time with a linear decay rate.
-In either flow intensity constraint, note that $H^{-1}$ mix-norm decreases by exclusively exploiting filamentation without homogenisation.
+In either flow intensity constraint, note that $H^{-1}$ mix-norm decreases by exclusively exploiting filamentation without homogenization.
 This is  exactly opposite to the purely diffusive case.
@@
 The limitations on the length scale controlled the long-run optimal mixing rates determined to be $\Gamma$ under the enstrophy constraint and $U^2/\kappa$ under the energy constraint up to $O(1)$ constants.
-In contrast to the `pure' cases mentioned earlier, it is important to note that the $H^{-1}$ can now decrease by the two avenues of homogenisation and filamentation simultaneously.
+In contrast to the `pure' cases mentioned earlier, it is important to note that the $H^{-1}$ can now decrease by the two avenues of homogenization and filamentation simultaneously.
 
@@
 Pure advection succeeds at filamentation by transferring spectral mass from the low wave number modes to the high wave number modes in a continuous fashion.
-However in the presence of diffusion, a once optimal pure advection flow exceptional at filamentation will be met with potential conflict since homogenisation by diffusion may stifle its progress in transferring spectral mass to high wave number modes.
+However in the presence of diffusion, a once optimal pure advection flow exceptional at filamentation will be met with potential conflict since homogenization by diffusion may stifle its progress in transferring spectral mass to high wave number modes.
 Given that diffusion is ubiquitous, we must come to terms with this conflict to produce efficient mixing.
@@
 
-We will demonstrate that homogenisation via diffusion and filamentation via advection can sometimes be in conflict and collectively produce a negative impact on mixing.
+We will demonstrate that homogenization via diffusion and filamentation via advection can sometimes be in conflict and collectively produce a negative impact on mixing.
 We show numerical evidence that filamentation length scale appears to be limited by the Batchelor scale as seen in the shell model, even when actively trying to choose the most optimal flow to enhance filamentation.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{images/enstrophy_norms}
+\includegraphics[width=\textwidth]{enstrophy_norms}
 \caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal enstrophy-constrained flow.  }
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{images/energy_norms}
+\includegraphics[width=\textwidth]{energy_norms}
 \caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal energy-constrained flow.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{images/enstrophy_film}
+\includegraphics[width=\textwidth]{enstrophy_film}
 \caption{Local-in-time optimisation with enstrophy constraint.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{images/energy_film}
+\includegraphics[width=\textwidth]{energy_film}
 \caption{Local-in-time optimisation with energy constraint.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{images/enstrophy_length}
+\includegraphics[width=\textwidth]{enstrophy_length}
 \caption{The left subplot shows the filament length $\lambda$ over time subject to the optimal enstrophy-constrained flow.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{images/energy_length}
+\includegraphics[width=\textwidth]{energy_length}
 \caption{The left subplot shows the filament length $\lambda$ over time subject to the optimal energy-constrained flow.
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/enstrophy_rate}
+\includegraphics[width=0.5\textwidth]{enstrophy_rate}
 \caption{Mixing rate $r(t)$ over time when subject to the optimal enstrophy-constrained flow.}
@@
 \centering
-\includegraphics[width=\textwidth]{images/energy_rate}
+\includegraphics[width=\textwidth]{energy_rate}
 \caption{The left subplot shows the mixing rate $r(t)$ over time when subject to the optimal energy-constrained flow. The right subplot is the same data except scaled: $r(t)/r_{U} = r(t)/Pe$.}

### 2018-02-14 paper/manuscript.tex
added revisions

@@
 In particular, it is valuable to determine how the mixing rate (typically the most optimal mixing rate) depends on aggregate flow intensity measures such as energy and enstrophy.
-This is the objective of the research program encompassing many efforts \cite{CS2013,GI2014,JLT2012,JFM2011, Miles2017a,  JLT2012, DF2014, GM2005} in last decade.
+This is the objective of the research program encompassing many efforts \cite{CS2013,GI2014,JLT2012,JFM2011, Miles2017a,  JLT2012, DF2014, GM2005,Cortelezzi2008} in the last decade.
 
@@
 This produces a scalar field with sharp gradients and small length scales.
-This corresponds to the reduction of scale of segregation or filamentation.
+This corresponzds to the reduction of scale of segregation or filamentation.
 The second way is to decrease the Fourier amplitudes $|\hat{\theta}_{\vec{k}}|$ for $\vec{k}\neq 0$.
@@
 The local-in-time optimal velocity fields maximise the instantaneous mixing rate by minimising $\ddt{}\hmone{\theta}^2$.
+We highlight that local-in-time optimization is not the same as global-in-time or finite-time optimization where the objective is to minimise $\|\theta(\,\cdot\, , T)\|_{H^{-1}}$ at the final time $T$.
+These objectives generally produce different results.
+In the context of the shell model, however, these strategies yielded similar decay rates.
+The differences between these two objectives under the evolution of  \eref{eq:nd_ade}  will be the focus of a future study.
+
 The optimal velocity fields are given instantaneously for the enstrophy case by (in non-dimensional form)
@@
 \end{eqnarray*}
-%
+%t
 and using $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, it follows that
@@
 \subsubsection{Results for $\linf{\u}= 1$}
-Here we extend the result of \cite{Chi-Cheu1996} to show that the presence of diffusion rules out perfect mixing in finite time for bounded velocity flows.  First note that
+Here we follow and refine an analysis of Poon \cite{Chi-Cheu1996} to show that the presence of diffusion rules out perfect mixing in finite time for bounded velocity flows.  First note that
 %
@@
 %
-Using H\"older's inequality and \eref{eq:PDE_advection}, this simplifies to
+Using H\"older's inequality and \eref{eq:PDE_advection}, this simplifies to a observation originally noted by Poon \cite{Chi-Cheu1996}:
 %
-\begin{eqnarray*}
+\begin{eqnarray}
 	\ddt{} \pbrac{ \frac{\hone{\theta}^2}{\ltwo{\theta}^2} } 
@@
 			}.
-\end{eqnarray*}
+\end{eqnarray}
 Again applying H\"older's inequality we have
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{enstrophy_norms}
+\includegraphics[width=\textwidth]{images/enstrophy_norms}
 \caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal enstrophy-constrained flow.  }
@@
 \centering
-\includegraphics[width=0.5\textwidth]{enstrophy_rate}
+\includegraphics[width=1.0\textwidth]{images/enstrophy_rate}
 \caption{Mixing rate $r(t)$ over time when subject to the optimal enstrophy-constrained flow.}
@@
 %
-The local-in-time optimisation results suggest that there is a limiting length scale for passive tracer mixing whenever $L^{2}$ flows are instantaneously optimised to decrease the mix-norm.
-The bounds derived under the $L^{\infty}$ constrained flow assumption did not result in proving this observation, but they did definitively rule out the possibility of perfect mixing in finite time for $L^{\infty}$ flow constraints.
+The local-in-time optimisation results suggest that there is a limiting length scale for passive tracer mixing whenever $L^{2}$ flows (either $\ltwo{\mathbf{u}}$ or $\ltwo{\nabla\mathbf{u}}$) are instantaneously optimised to decrease the mix-norm.
+The bounds derived under both $L^{\infty}$ constrained flow assumptions did not result in proving this observation, but they did definitively rule out the possibility of perfect mixing in finite time for these $L^{\infty}$ flow constraints.
 
@@
 The double-exponential bounds arise from the use of exponential upper bounds on the quantity $\frac{\hone{\theta}}{\ltwo{\theta}}$ in time for both $L^{\infty}$ flow constraints considered.
-We surmise that $\frac{\hone{\theta}}{\ltwo{\theta}} < C$ (where $C$ is a constant) for all time $t$ as supported by our numerical results and may be proven by exploiting the incompressiblity condition.
-If this is true generally for all $L^{\infty}$  flows, then our previous analysis would demonstrate that the $H^{-1}$ mix-norm is bounded below by an exponential.
+We surmise that in fact $\frac{\hone{\theta}}{\ltwo{\theta}} < C$ (where $C$ is a constant) for all time $t$ as suggested by the numerical results.
+If this is true generally for the $L^{\infty}$  flows, then our previous analysis would demonstrate that the $H^{-1}$ mix-norm is bounded below by a single exponential instead of a double exponential.
 

### 2018-02-15 paper/manuscript.tex
added missing square and minor sytlistic changes

@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{scale-and-intensity}
+	\includegraphics[width=0.5\textwidth]{images/scale-and-intensity}
 	\caption{Filamentation is the reduction of the scale of segregation as illustrated by the top transformation.
@@
 \frac{d}{dt}\left(\frac{\|\nabla\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}\right) &= \frac{\|\theta\|_{L^{2}}^2\frac{d}{dt}\|\nabla\theta\|_{L^{2}}^2-\|\nabla\theta\|_{L^{2}}^2\frac{d}{dt}\|\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^4}\\
-&= \frac{-2\int \partial_{i}u_{j}\partial_{i}\theta\partial_{j}\theta - \frac{2}{Pe} \|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}+\frac{2}{Pe}\frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \\
+&= \frac{-2\sint{\nabla\theta \cdot \nabla\vec{u} \cdot \nabla\theta  } - \frac{2}{Pe} \|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2}+\frac{2}{Pe}\frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \\
 &=-\frac{2}{Pe}\left(\frac{\|\Delta\theta\|_{L^{2}}^2}{\|\theta\|_{L^{2}}^2} - \frac{\|\nabla\theta\|_{L^{2}}^4}{\|\theta\|_{L^{2}}^4} \right) - 2\frac{\sint{\nabla\theta \cdot \nabla\vec{u} \cdot \nabla\theta  }}{\|\theta\|_{L^{2}}^2}
@@
 \begin{equation}
-\hmone{\theta} \geq  \hmone{\theta_{0}} \exp\left[- t -\frac{1}{2 Pe}\frac{\hone{\theta_{0}}^2}{\ltwo{\theta_{0}}}\left(e^{2 t} -1\right)\right].
+\hmone{\theta} \geq  \hmone{\theta_{0}} \exp\left[- t -\frac{1}{2 Pe}\frac{\hone{\theta_{0}}^2}{\ltwo{\theta_{0}}^2}\left(e^{2 t} -1\right)\right].
 \end{equation}
@@
 
-Then compute:
+Then simply after substitution:
 %
@@
 %
-Using H\"older's inequality and \eref{eq:PDE_advection}, this simplifies to a observation originally noted by Poon \cite{Chi-Cheu1996}:
+Using H\"older's inequality and \eref{eq:nd_ade}, this simplifies to a observation originally noted by Poon \cite{Chi-Cheu1996}:
 %
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{energy_norms}
+\centering
+\includegraphics[]{images/energy_norms}
 \caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal energy-constrained flow.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{enstrophy_film}
+\includegraphics[]{images/enstrophy_film}
 \caption{Local-in-time optimisation with enstrophy constraint.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{energy_film}
+\includegraphics[]{images/energy_film}
 \caption{Local-in-time optimisation with energy constraint.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{images/enstrophy_length}
+\includegraphics[]{images/enstrophy_length}
 \caption{The left subplot shows the filament length $\lambda$ over time subject to the optimal enstrophy-constrained flow.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{energy_length}
+\includegraphics[]{images/energy_length}
 \caption{The left subplot shows the filament length $\lambda$ over time subject to the optimal energy-constrained flow.
@@
 \centering
-\includegraphics[width=1.0\textwidth]{images/enstrophy_rate}
+\includegraphics[]{images/enstrophy_rate}
 \caption{Mixing rate $r(t)$ over time when subject to the optimal enstrophy-constrained flow.}
@@
 \centering
-\includegraphics[width=\textwidth]{energy_rate}
+\includegraphics[]{images/energy_rate}
 \caption{The left subplot shows the mixing rate $r(t)$ over time when subject to the optimal energy-constrained flow. The right subplot is the same data except scaled: $r(t)/r_{U} = r(t)/Pe$.}

### 2018-02-20 paper/manuscript.tex
removed file

@@
 In the case without advection ($\vec{u}=\vec{0}$), equation \eref{eq:PDE_advection} reduces to the classical heat equation \cite{Evans2010} and the Fourier modes evolve according to $\hat{\theta}_{\vec{k}}(t)=\hat{\theta}_{\vec{k}}(0)e^{-\kappa|\vec{k}|^2t}$.
-Thus we have explicit analytical results for the decay of the $H^{-1}$ mix-norm by simply substituting this result.
-Note that $H^{-1}$ mix-norm will decay monotonically.
+Thus we have explicit analytical results for the decay of the $H^{-1}$ norm by simply substituting this result.
+Note that $H^{-1}$ norm will decay monotonically.
 Diffusion is unable to transfer spectral mass from the low wave number modes to the high wave number modes and thus is incapable of filamentation.
@@
 In the case without diffusion ($\kappa = 0$), pure advection of the flow is the only method of mixing, colloquially known as stirring.
-For a flow that is constrained by enstrophy, the mix-norm decays at most exponentially where the exponential rate is proportional to $\Gamma$ \cite{GI2014,CS2013}.
+For a flow that is constrained by enstrophy, the $H^{-1}$ norm decays at most exponentially where the exponential rate is proportional to $\Gamma$ \cite{GI2014,CS2013}.
 This was mathematically proven by two separate approaches: G.
@@
 On the other hand, energy-constrained flows can achieve even faster mixing rates.
-In fact they can achieve {\it perfect mixing in finite time} which means that the $H^{-1}$ mix-norm approaches zero in finite time as opposed to approaching zero in infinite time as in the case for enstrophy-constrained mixing.
-This can be demonstrated by a `chequerboard' flow \cite{JMP2012} where the mix-norm achieves perfect mixing in finite time with a linear decay rate.
-In either flow intensity constraint, note that $H^{-1}$ mix-norm decreases by exclusively exploiting filamentation without homogenization.
+In fact they can achieve {\it perfect mixing in finite time} which means that the $H^{-1}$ norm approaches zero in finite time as opposed to approaching zero in infinite time as in the case for enstrophy-constrained mixing.
+This can be demonstrated by a `chequerboard' flow \cite{JMP2012} where the  $H^{-1}$ norm achieves perfect mixing in finite time with a linear decay rate.
+In either flow intensity constraint, note that $H^{-1}$ norm decreases by exclusively exploiting filamentation without homogenization.
 This is  exactly opposite to the purely diffusive case.
@@
 \begin{equation}
+\label{eq:u_lit_enstrophy}
 \mathbf{u}= \frac{-\invlap\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\nabla^{-1}\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
@@
 \begin{equation}
+\label{eq:u_lit_energy}
 \mathbf{u}= \frac{\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
@@
 \end{eqnarray*}
-
-Then simply after substitution:
+%
+Then simplify and compute:
 %
@@
 
-We solve \eref{eq:nd_ade} by using a Fourier basis to represent the discretised spatial domain with a 4th order Runge-Kutta time-stepping method.
+We solve \eref{eq:nd_ade} with either flow \eref{eq:u_lit_enstrophy} or \eref{eq:u_lit_energy} by using a Fourier basis to represent the discretised spatial domain with a 4th order Runge-Kutta time-stepping method.
 All simulation code was created in the programming language Python with package modules, pyfftw and numpy.
@@
 %
-The local-in-time optimisation results suggest that there is a limiting length scale for passive tracer mixing whenever $L^{2}$ flows (either $\ltwo{\mathbf{u}}$ or $\ltwo{\nabla\mathbf{u}}$) are instantaneously optimised to decrease the mix-norm.
+The local-in-time optimisation results suggest that there is a limiting length scale for passive tracer mixing whenever $L^{2}$ flows (either $\ltwo{\mathbf{u}}$ or $\ltwo{\nabla\mathbf{u}}$) are instantaneously optimised to decrease the $H^{-1}$ norm.
 The bounds derived under both $L^{\infty}$ constrained flow assumptions did not result in proving this observation, but they did definitively rule out the possibility of perfect mixing in finite time for these $L^{\infty}$ flow constraints.
@@
 We suspect that the bounds obtained for $L^{\infty}$ flows are not sharp and could be improved further.
-The $L^{\infty}$ flow analysis produced a double-exponential lower bound on the $H^{-1}$ mix-norm rather than exponential as possibly expected given the numerical results for local-in-time optimal $L^2$ flows.
+The $L^{\infty}$ flow analysis produced a double-exponential lower bound on the $H^{-1}$ norm rather than exponential as possibly expected given the numerical results for local-in-time optimal $L^2$ flows.
 The double-exponential bounds arise from the use of exponential upper bounds on the quantity $\frac{\hone{\theta}}{\ltwo{\theta}}$ in time for both $L^{\infty}$ flow constraints considered.
 We surmise that in fact $\frac{\hone{\theta}}{\ltwo{\theta}} < C$ (where $C$ is a constant) for all time $t$ as suggested by the numerical results.
-If this is true generally for the $L^{\infty}$  flows, then our previous analysis would demonstrate that the $H^{-1}$ mix-norm is bounded below by a single exponential instead of a double exponential.
+If this is true generally for the $L^{\infty}$  flows, then our previous analysis would demonstrate that the $H^{-1}$ norm is bounded below by a single exponential instead of a double exponential.
 
@@
 Invoking a flow may cause the lower wave number modes to become `populated' and therefore may limit the mixing rate.
-It is important to keep this simple strategy in mind when trying to rigorously prove bounds on the mix-norm.
-This strategy has an important implication --- there does not exist a lower bound on the mix-norm of the form $\hmone{\theta} \geq A e^{-rt}$ where  $r$ is independent of the initial data.
+It is important to keep this simple strategy in mind when trying to rigorously prove bounds on the $H^{-1}$ norm.
+This strategy has an important implication --- there does not exist a lower bound on the  $H^{-1}$ norm of the form $\hmone{\theta} \geq A e^{-rt}$ where  $r$ is independent of the initial data.
 
-In future work, we would like to consider the optimal control problem with finite-time optimisation to minimise the $H^{-1}$ mix-norm at the end time rather than instantaneously attempting to minimise its decay rate.
+In future work, we would like to consider the optimal control problem with finite-time optimisation to minimise the $H^{-1}$ norm at the end time rather than instantaneously attempting to minimise its decay rate.
 This might lead to flows that can produce even smaller length scales.

### 2018-02-26 tools.py
fixed curl error int ools

@@ -304,7 +304,8 @@ class VectorTool(object):
         self.vector_input_test(vector)
         vector_hat = self.fft(vector)
         w = fft.irfftn(
-            1j * self.K[1] * vector_hat[0] - 1j * self.K[0] * vector_hat[1], threads=self.num_threads)
+            1j * self.K[0] * (2.0 * np.pi / self.L) * vector_hat[1]
+            - 1j * self.K[1] * (2.0 * np.pi / self.L) * vector_hat[0], threads=self.num_threads)
         return w
 
     def invlap(self, vector):

### 2018-02-28 flux/lit_enstrophy_inf.py
added new files

@@ -1,76 +1,0 @@
-from integrators import RK4_timestepper, mega_RK4_timestepper, integrator2
-from tools import ScalarTool, create_grid, dt_cfl, N_boyd
-from post_processing import plot_norms, movie
-from operators import OperatorKit
-import numpy as np
-import matplotlib
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-
-import time
-import pickle
-import os
-import sys
-
-if __name__ == "__main__":
-    # Parameters
-    L = 1.0
-
-    kappa = 0.0
-    gamma = 1.0
-    T = 6.0
-
-    # lb = (kappa / gamma)**0.5
-    # l_smallest = lb
-    # print('lb = ', lb)
-    #
-    # M = L / l_smallest
-    # print('N_boyd = ', N_boyd(M))
-    # N = min(N_boyd(M), 512)
-    # N = 64
-    N = 1024
-    print('N = ', N)
-
-    # Create tool box
-    okit = OperatorKit(N, L, kappa)
-    st = ScalarTool(N, L)
-
-    # Initial condition
-    X = create_grid(N, L)
-    th0 = np.sin((2.0 * np.pi / L) * X[0])
-
-    # Create operators: d th / dt = operator (th)
-    def lit_enstrophy_op(scalar):
-        return okit.lit_enstrophy_op(scalar, gamma)
-
-    def sin_op(scalar):
-        return okit.sin_flow_op(scalar)
-
-    # Perform simulation
-    time_array = np.linspace(0, T, 200)
-    th0 = RK4_timestepper(sin_op, th0, 0.001)
-    start_time = time.time()
-    dt0_cfl = 0.25 * dt_cfl(N, L, kappa, gamma * L)
-    th = integrator2(lit_enstrophy_op, mega_RK4_timestepper,
-                     th0, time_array, dt0_cfl)
-
-    print(time.time() - start_time)
-
-    # Output
-    output_folder = 'output-pe=inf/'
-    os.system('mkdir ' + output_folder)
-    os.system('cp lit_enstrophy_inf.py ' + output_folder)
-
-    plt.figure()
-    st.plot(th[-1])
-    plt.savefig(output_folder + 'plot_final_frame-pe=inf.png')
-
-    plt.figure()
-    plot_norms(time_array, th, N, L)
-    plt.savefig(output_folder + 'plot_norms-pe=inf.png')
-
-    movie(time_array, th, N, L, output_path=output_folder)
-
[…]

### 2018-02-28 lit_enstrophy.py

@@ -20,10 +20,10 @@ if __name__ == "__main__":
     print('Pe = ', Pe)
     kappa = 1.0 / Pe
     gamma = 1.0
-    T = 2.0
+    T = 13.0
 
     lb = (kappa / gamma)**0.5
-    l_smallest = lb
+    l_smallest = 0.2 * lb
     print('lb = ', lb)
 
     M = L / l_smallest

### 2018-02-28 test/test_operators.py

@@ -134,6 +134,20 @@ def test_that_LIT_enstrophy_flow_satisfies_budget_constraint():
         st.l2norm(vt.curl(okit.u_lit_enstrophy(th, gamma))), gamma * L)
 
 
+def test_that_LIT_enstrophy_flow_satisfies_budget_constraint_2nd():
+    L = 10.0
+    N = 128
+    kappa = 0.1
+    gamma = 2.0
+    vt = VectorTool(N, L)
+    st = ScalarTool(N, L)
+    th = np.exp(np.sin((2 * np.pi / L) *
+                       st.X[0]) * np.cos((2 * np.pi / L) * st.X[1]))
+    okit = OperatorKit(N, L, kappa)
+    assert np.isclose(
+        vt.h1norm(okit.u_lit_enstrophy(th, gamma)), gamma * L)
+
+
 def test_that_LIT_enstrophy_flow_is_incompressible():
     L = 10.0
     N = 128

### 2018-02-28 test/test_tools.py

@@ -4,6 +4,47 @@ import math
 from tools import N_boyd
 
 
+def test_h1normsq_of_vector_is_spatial_integral_neg_lapvec_times_vec():
+    N = 128
+    L = 2.0
+    kappa = 0.0
+    gamma = 1.0
+    v = np.random.random((2, N, N))
+    st = ScalarTool(N, L)
+    vt = VectorTool(N, L)
+    v = vt.div_free_proj(v)
+    v = vt.dealias(v)
+
+    a = vt.h1norm(v)**2
+    b = st.sint(np.sum(-vt.lap(v) * v, 0))
+    assert np.allclose(a, b)
+
+
+def test_h1norm_of_sin_flow():
+    N = 128
+    L = 2.0
+    vt = VectorTool(N, L)
+    X = np.mgrid[:N, :N].astype(float) * (L / N)
+    u = np.zeros((2, N, N))
+    u[0] = np.sin(2. * np.pi / L * X[1])
+    assert np.isclose(vt.h1norm(u)**2., 2. * np.pi**2.)
+
+
+def test_curl_is_equal_to_curl_computed_with_grad_function():
+    N = 128
+    L = 2.0
+    kappa = 0.0
+    gamma = 1.0
+    v = np.random.random((2, N, N))
+    # print(np.shape(v))
+    st = ScalarTool(N, L)
+    vt = VectorTool(N, L)
+    v = vt.div_free_proj(v)
+    v = vt.dealias(v)
+    c = st.grad(v[1])[0] - st.grad(v[0])[1]
+    assert np.allclose(c, vt.curl(v))
+
+
 def test_l2norm_squared_of_curl_of_vector_is_spatial_integral_of_neg_vector_times_lap_vector():
     N = 128
     L = 2.0

### 2018-02-28 tools.py

@@ -99,7 +99,7 @@ class ScalarTool(object):
         integrand = np.ravel(grad_invlap_scalar_sq)
         return np.sum(integrand * self.h**2.0)**0.5
 
-    def plot(self, scalar, high_quality=False, vmin=-1, vmax=1):
+    def plot(self, scalar, high_quality=False, fixed_vertical_axis=False):
 
         if high_quality:
             plt.rc('text', usetex=True)
@@ -108,6 +108,12 @@ class ScalarTool(object):
             plt.rc('text', usetex=False)
             plt.rc('font', family='sans-serif', size=12)
 
+        if fixed_vertical_axis:
+            vmin = -1
+            vmax = 1
+        else:
+            vmin = np.amin(scalar)
+            vmax = np.amax(scalar)
         self.scalar_input_test(scalar)
         im = plt.imshow(np.transpose(scalar),
                         cmap=plt.cm.gray,
@@ -271,6 +277,20 @@ class VectorTool(object):
         """ L2 norm of a vector field """
         self.vector_input_test(vector)
         integrand = np.sum(vector * vector, 0)
+
+        return np.sum(np.ravel(integrand) * self.h**2)**0.5
+
+    def h1norm(self, vector):
+        """ L2 norm of a vector field """
+        self.vector_input_test(vector)
+        vector_hat = self.fft(vector)
+        grad_vx = fft.irfftn(1.0j * self.K * (2 * np.pi / self.L)
+                             * vector_hat[0], axes=(1, 2), threads=self.num_threads)
+        grad_vy = fft.irfftn(1.0j * self.K * (2 * np.pi / self.L)
+                             * vector_hat[1], axes=(1, 2), threads=self.num_threads)
+
+        integrand = (grad_vx[0]**2.0 + grad_vx[1]**2.0
+                     + grad_vy[0]**2.0 + grad_vy[1]**2.0)
 
         return np.sum(np.ravel(integrand) * self.h**2)**0.5
 

### 2018-02-28 paper/revisions_2132018/reply.tex
adding paper

\documentclass[]{article}

\newcommand{\ddt}[1]{\frac{d #1}{dt}}
%\newcommand{\hmone}[1]{\|#1\|_{H^{-1}}}
\newcommand{\hmone}[1]{\|\nabla^{-1} #1\|_{L^{2}}}
\newcommand{\ltwo}[1]{\|#1\|_{L^{2}}}
%\newcommand{\hone}[1]{\|#1\|_{H^{1}}}
\newcommand{\hone}[1]{\| \nabla #1\|_{L^{2}}}
\newcommand{\htwo}[1]{\|#1\|_{H^{2}}}
\newcommand{\sint}[1]{\int_{D} #1 \, d^{d}\mathbf{x}}
\newcommand{\tint}[1]{\int_{0}^{T} #1 \, dt}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\linf}[1]{\| #1 \|_{L^{\infty}}}
\newcommand{\tavg}[1]{\langle  #1 \rangle}
\renewcommand{\u}{\mathbf{u}}
%\newcommand{\ppt}[1]{\frac{\partial #1}{\partial t}}
\newcommand{\ppt}[1]{\partial_{t} #1}
\newcommand{\lap}{\Delta }
\newcommand{\invlap}{\Delta^{-1}}
%\newcommand{\lap}{\nabla^{2}}
%\newcommand{\invlap}{\nabla^{-2}}
\newcommand{\pbrac}[1]{\left( #1 \right)}
\newcommand{\sbrac}[1]{\left[ #1 \right]}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\title{Reply to Referee and Editor Reports}
\date{}
\begin{document}
%\maketitle

\begin{flushleft}
Dear Editors and Referees,
\end{flushleft}

Thank you for taking the time to read and provide important feedback on our manuscript. Below you will find the changes made to the revised version.

\begin{flushleft}
Best Regards, 
\end{flushleft}

\begin{flushleft}
Christopher J. Miles \\
Charles R. Doering
\end{flushleft}

\vspace{1cm}

\noindent\rule{\textwidth}{1pt}

\vspace{1cm}

{\bf Changes made in response to Referee \#1:} Below you will find the original comment of the referee with our changes and comments immediately after each.
\begin{enumerate}
\item  ``{\it In citation [2] Thiffeault has too many initials.}'' \\
\\
This error has been corrected.

\item {\it ``Homogenization is more conventional spelling than homogenisation.''}\\
\\
This change has been made. However, the original spelling choice ``homogenisation" was based off of the guidelines of the journal. The guidelines state UK spelling.

\item  {\it ``On p.3 should `attached' instead of `attach'.''} \\
\\
This has been corrected.

\end{enumerate}

{\bf Changes made in response to Referee \#2:} Below you will find the original comment of the referee with our changes and comments immediately after each.

\begin{enumerate}
\item {\it ``On chapter 2 of this paper (theory part), the authors mainly provide two proofs of the
lower bound of  $\lambda(t)$ and upper bound of $r(t)$, the proofs seem to be standard and the results
are about some properties of standard parabolic equation, is there any literature to refer for
these results? I'm very curious about this.''} \\
\\
We agree that both proofs utilize familiar energy methods, however we have every reason to believe that both calculations are original in the context of the problems at hand. For the enstrophy-constrained problem, the proof is particularly straightforward but it is desirable to include it for both clarity and completeness. The energy-constrained problem requires somewhat more clever analysis and in this regard we were inspired by the previous work of Poon (1996) that was brought to our attention by A. Kiselev (whom we gratefully acknowledged!).

\item {\it ``All the prediction about the $r(t)$ as well as the $\lambda(t)$ are based on the local-in-time optimisation flow, however there is no literature about whether this kind of flow is global optimisation mixing flow or not, could the authors clearify this?''} \\
\\
We thoroughly recognize that the relationship between local- and global-in-time optimization is not fully understood beyond the fact that local-in-time optimization is the short-time-horizon limit of global-in-time optimization. In order to stress this, in the theory section when local-in-time optimization is introduced we added ``We highlight that local-in-time optimization is not the same as global-in-time or finite-time optimization where the objective is to minimise $\|\theta(\,\cdot\, , T)\|_{H^{-1}}$ at the final time $T$. These objectives generally produce different results.  In the context of the shell model, however, these strategies yielded similar decay rates. The differences between these two objectives under the evolution of  (3)  will be the focus of a future study.''

\item {\it ``In this paper, the authors studied the ratio $r(t)$, in the previous work of the same authors, another ratio $\frac{\|\theta\|_{H^{1}}}{\|\theta\|_{L^2}}$ is also considered. It seems that both of the numerical results show they both reached the constant as time goes to infinity under optimal enstrophy-constrained flow. Physically they are of the same scale (up to a minus one power), is there any reason for this paper to consider $H^{-1}$ instead of $H^1$? Is there more connection between these two ratios other than Holder's inequality? Please ignore this question if it is impossible to answer shortly.''}\\
\\
The $H^{1}$ and $H^{-1}$ norms formally scale as reciprocal powers of a length scale, and exactly so for narrow Fourier-band functions. However, generally the $H^{1}$ norm could diverge leaving the $H^{-1}$ finite as may be the case for mixing without diffusion. In the presence of diffusion as considered here, the $H^{1}$ increases before it decreases while the $H^{-1}$ norm decreases monotonically in time. It is the asymptotic state induced by sustained mixing that results in their scaling the same up to the expected $-1$ power because of the emergence of the Batchelor scale dominating the spectrum.

The referee is thus correct that the $\|\theta\|_{H^{1}}/\|\theta\|_{L^2}$ also reaches a constant --- essentially the reciprocal of the previous constant. We could also provide a plot of this ratio in time if necessary. For the sake of brevity and minimizing repetition we decided to only provide $\|\theta\|_{H^{-1}}/\|\theta\|_{L^2}$ over time since this provides the same essential information as $\|\theta\|_{H^{1}}/\|\theta\|_{L^2}$ .

\end{enumerate}

{\bf Changes made in response to Editor-in-Chief and Associate Editor:} Below you will find the original comment of the referee with our changes and comments immediately after each.

\begin{enumerate}
\item {\it ``... the relation between the bounds presented in the analytical section 2 and the earlier work on these quantities be stated explicitly and fully, second that the authors should address (at least in a reply to the reviewer, if not also in the manuscript) the extent to which global-in-time mixing optimization might be possible, and third that the relative advantages of the two approaches (earlier work based on the $H^1$ norm of theta, and this work using the $H^{-1}$ norm) be discussed.''}

We fully addressed two of these three issues above, the remaining issue being the {\it extent} to which global-in-time mixing optimization might be possible. As discussed in detail in our previous paper on the shell model, global-in-time optimization requires finite-time-horizon optimal control techniques which are computationally challenging (although feasible) and analytically daunting (and the focus current research).

\item {\it ``The AE recommends that revisions are required and asks that the authors revise the manuscript to account for the comments of referee 2, including a detailed reply to the three comments of this reviewer, The AE asks that special attention be paid to adding statements about the relation of the analysis here and that of reference 3. The bases of the AE's recommendation are the two referee reports and the AE's reading of the manuscript. The AE thinks that it will be useful to have a suitably revised article on this topic in the journal, since there is considerable interest in understanding why the analytical results are as yet insufficiently sharp (involving double exponentials) to get close to the numerically observed exponential mixing rates in optimal mixing flows. In addition, the AE points out that the analytical and numerical results presented in a suitably revised manuscript would also constitute a good road map for future research in this topic.'' }

With regards to the relation between our analysis and that of Poon (1996), we have followed and refined the analysis of Poon to produce an upper bound on $\frac{d}{dt} \left(\frac{\hone{\theta}}{\ltwo{\theta}}\right)$ as shown in equation (11). To make this explicit, we added the introductory sentence to section 2.3.2 : ``Here we follow and refine an analysis of Poon [3] to show that the presence of diffusion rules out perfect mixing in finite time for bounded velocity flows''. In addition when arriving at (11), we say ``Using H\"older's inequality and (3), this simplifies to a observation originally noted by Poon [3].''

With regards to the gap between the derived analytical bound (involving a double exponential) and numerical results (suggesting single exponential decay), the second paragraph of the revised discussion section addresses this issue explicitly. There we say ``We suspect that the bounds obtained for $L^{\infty}$ flows are not sharp and could be improved further. The $L^{\infty}$ flow analysis produced a double-exponential lower bound on the $H^{-1}$ mix-norm rather than exponential as possibly expected given the numerical results for local-in-time optimal $L^2$ flows. The double-exponential bounds arise from the use of exponential upper bounds on the quantity $\frac{\hone{\theta}}{\ltwo{\theta}}$ in time for both $L^{\infty}$ flow constraints considered. We surmise that in fact $\frac{\hone{\theta}}{\ltwo{\theta}} < C$ (where $C$ is a constant) for all time $t$ as suggested by the numerical results. If this is true generally for the $L^{\infty}$  flows, then our previous analysis would demonstrate that the $H^{-1}$ mix-norm is bounded below by a single exponential instead of a double exponential.''

\item {\it ``Finally, please also make some editorial adjustments, including to increase the thickness of the curves in the figures in Section 3 and to increase the sizes of the labels and numbers on the axes in all of the figures.''}

This has been corrected.
\end{enumerate}

{\bf Changes made by Authors:} We made minor stylistic and grammatical changes. In addition, we changed the color scheme of plots to increase visibility.

\end{document}

### 2018-02-28 paper/submitted_10_25_2017/manuscript.tex
adding paper

--- 2018-02-14 paper/manuscript.tex
@@
 Incompressible flows can be effective mixers by appropriately advecting a passive tracer to produce small filamentation length scales.
-In addition, diffusion is generally perceived as beneficial to mixing due to its ability to homogenize a passive tracer.
+In addition, diffusion is generally perceived as beneficial to mixing due to its ability to homogenise a passive tracer.
 However we provided numerical evidence that, in the case where advection and diffusion are both actively present, diffusion produces nearly neutral or even {\it negative} effects by limiting the mixing effectiveness of incompressible optimal flows.
@@
 In particular, it is valuable to determine how the mixing rate (typically the most optimal mixing rate) depends on aggregate flow intensity measures such as energy and enstrophy.
-This is the objective of the research program encompassing many efforts \cite{CS2013,GI2014,JLT2012,JFM2011, Miles2017a,  JLT2012, DF2014, GM2005,Cortelezzi2008} in the last decade.
+This is the objective of the research program encompassing many efforts \cite{CS2013,GI2014,JLT2012,JFM2011, Miles2017a,  JLT2012, DF2014, GM2005} in last decade.
 
@@
 On the other hand, the {\it intensity of segregation } quantifies the variation of the concentration amplitude.
-We will refer to mixing by the reduction of the intensity of segregation as {\it homogenization}.
+We will refer to mixing by the reduction of the intensity of segregation as {\it homogenisation}.
 This process is illustrated by the bottom graphic of figure \ref{fig:scale-and-intensity}.
@@
 This produces a scalar field with sharp gradients and small length scales.
-This corresponzds to the reduction of scale of segregation or filamentation.
+This corresponds to the reduction of scale of segregation or filamentation.
 The second way is to decrease the Fourier amplitudes $|\hat{\theta}_{\vec{k}}|$ for $\vec{k}\neq 0$.
-This corresponds to a reduction in the intensity of segregation, or homogenization.
+This corresponds to a reduction in the intensity of segregation, or homogenisation.
 Thus we can see that the $H^{-1}$ embodies both senses of mixing.
@@
 	\caption{Filamentation is the reduction of the scale of segregation as illustrated by the top transformation.
-homogenization is the reduction of the intensity of segregation as illustrated by the bottom transformation.}
+Homogenisation is the reduction of the intensity of segregation as illustrated by the bottom transformation.}
 	\label{fig:scale-and-intensity}
@@
 Diffusion is unable to transfer spectral mass from the low wave number modes to the high wave number modes and thus is incapable of filamentation.
-Thus the pure diffusion case solely exploits homogenization.
-Also notice the unequal weighting attached to each mode.
+Thus the pure diffusion case solely exploits homogenisation.
+Also notice the unequal weighting attach to each mode.
 The Fourier modes with large wave number $|\vec{k}|$ decay at a faster rate relative to the decay of those with small wave number.
@@
 This can be demonstrated by a `chequerboard' flow \cite{JMP2012} where the mix-norm achieves perfect mixing in finite time with a linear decay rate.
-In either flow intensity constraint, note that $H^{-1}$ mix-norm decreases by exclusively exploiting filamentation without homogenization.
+In either flow intensity constraint, note that $H^{-1}$ mix-norm decreases by exclusively exploiting filamentation without homogenisation.
 This is  exactly opposite to the purely diffusive case.
@@
 The limitations on the length scale controlled the long-run optimal mixing rates determined to be $\Gamma$ under the enstrophy constraint and $U^2/\kappa$ under the energy constraint up to $O(1)$ constants.
-In contrast to the `pure' cases mentioned earlier, it is important to note that the $H^{-1}$ can now decrease by the two avenues of homogenization and filamentation simultaneously.
+In contrast to the `pure' cases mentioned earlier, it is important to note that the $H^{-1}$ can now decrease by the two avenues of homogenisation and filamentation simultaneously.
 
@@
 Pure advection succeeds at filamentation by transferring spectral mass from the low wave number modes to the high wave number modes in a continuous fashion.
-However in the presence of diffusion, a once optimal pure advection flow exceptional at filamentation will be met with potential conflict since homogenization by diffusion may stifle its progress in transferring spectral mass to high wave number modes.
+However in the presence of diffusion, a once optimal pure advection flow exceptional at filamentation will be met with potential conflict since homogenisation by diffusion may stifle its progress in transferring spectral mass to high wave number modes.
 Given that diffusion is ubiquitous, we must come to terms with this conflict to produce efficient mixing.
@@
 
-We will demonstrate that homogenization via diffusion and filamentation via advection can sometimes be in conflict and collectively produce a negative impact on mixing.
+We will demonstrate that homogenisation via diffusion and filamentation via advection can sometimes be in conflict and collectively produce a negative impact on mixing.
 We show numerical evidence that filamentation length scale appears to be limited by the Batchelor scale as seen in the shell model, even when actively trying to choose the most optimal flow to enhance filamentation.
@@
 The local-in-time optimal velocity fields maximise the instantaneous mixing rate by minimising $\ddt{}\hmone{\theta}^2$.
-We highlight that local-in-time optimization is not the same as global-in-time or finite-time optimization where the objective is to minimise $\|\theta(\,\cdot\, , T)\|_{H^{-1}}$ at the final time $T$.
-These objectives generally produce different results.
-In the context of the shell model, however, these strategies yielded similar decay rates.
-The differences between these two objectives under the evolution of  \eref{eq:nd_ade}  will be the focus of a future study.
-
 The optimal velocity fields are given instantaneously for the enstrophy case by (in non-dimensional form)
@@
 \end{eqnarray*}
-%t
+%
 and using $\ddt{}\ltwo{\theta}^2 = -\frac{2}{Pe} \hone{\theta}^2$, it follows that
@@
 \subsubsection{Results for $\linf{\u}= 1$}
-Here we follow and refine an analysis of Poon \cite{Chi-Cheu1996} to show that the presence of diffusion rules out perfect mixing in finite time for bounded velocity flows.  First note that
+Here we extend the result of \cite{Chi-Cheu1996} to show that the presence of diffusion rules out perfect mixing in finite time for bounded velocity flows.  First note that
 %
@@
 %
-Using H\"older's inequality and \eref{eq:PDE_advection}, this simplifies to a observation originally noted by Poon \cite{Chi-Cheu1996}:
+Using H\"older's inequality and \eref{eq:PDE_advection}, this simplifies to
 %
-\begin{eqnarray}
+\begin{eqnarray*}
 	\ddt{} \pbrac{ \frac{\hone{\theta}^2}{\ltwo{\theta}^2} } 
@@
 			}.
-\end{eqnarray}
+\end{eqnarray*}
 Again applying H\"older's inequality we have
@@
 \centering
-\includegraphics[width=1.0\textwidth]{images/enstrophy_rate}
+\includegraphics[width=0.5\textwidth]{enstrophy_rate}
 \caption{Mixing rate $r(t)$ over time when subject to the optimal enstrophy-constrained flow.}
@@
 %
-The local-in-time optimisation results suggest that there is a limiting length scale for passive tracer mixing whenever $L^{2}$ flows (either $\ltwo{\mathbf{u}}$ or $\ltwo{\nabla\mathbf{u}}$) are instantaneously optimised to decrease the mix-norm.
-The bounds derived under both $L^{\infty}$ constrained flow assumptions did not result in proving this observation, but they did definitively rule out the possibility of perfect mixing in finite time for these $L^{\infty}$ flow constraints.
+The local-in-time optimisation results suggest that there is a limiting length scale for passive tracer mixing whenever $L^{2}$ flows are instantaneously optimised to decrease the mix-norm.
+The bounds derived under the $L^{\infty}$ constrained flow assumption did not result in proving this observation, but they did definitively rule out the possibility of perfect mixing in finite time for $L^{\infty}$ flow constraints.
 
@@
 The double-exponential bounds arise from the use of exponential upper bounds on the quantity $\frac{\hone{\theta}}{\ltwo{\theta}}$ in time for both $L^{\infty}$ flow constraints considered.
-We surmise that in fact $\frac{\hone{\theta}}{\ltwo{\theta}} < C$ (where $C$ is a constant) for all time $t$ as suggested by the numerical results.
-If this is true generally for the $L^{\infty}$  flows, then our previous analysis would demonstrate that the $H^{-1}$ mix-norm is bounded below by a single exponential instead of a double exponential.
+We surmise that $\frac{\hone{\theta}}{\ltwo{\theta}} < C$ (where $C$ is a constant) for all time $t$ as supported by our numerical results and may be proven by exploiting the incompressiblity condition.
+If this is true generally for all $L^{\infty}$  flows, then our previous analysis would demonstrate that the $H^{-1}$ mix-norm is bounded below by an exponential.
 

### 2018-02-28 paper/manuscript.tex
fixed curl error int ools
performed massive cleanup

@@
 %
-\usepackage{ dsfont }
+%\usepackage{dsfont}
 \usepackage{hyperref}
 \usepackage{graphicx}
+\usepackage{amssymb}
 %
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{images/scale-and-intensity}
+	\includegraphics[width=0.5\textwidth]{scale-and-intensity}
 	\caption{Filamentation is the reduction of the scale of segregation as illustrated by the top transformation.
@@
 \label{eq:u_lit_enstrophy}
-\mathbf{u}= \frac{-\invlap\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\nabla^{-1}\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
+\mathbf{u}= \frac{-\invlap\mathbb{P}(\theta \nabla \invlap\theta)}{\langle |\nabla^{-1}\mathbb{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
 \end{equation}
@@
 \label{eq:u_lit_energy}
-\mathbf{u}= \frac{\mathds{P}(\theta \nabla \invlap\theta)}{\langle |\mathds{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
+\mathbf{u}= \frac{\mathbb{P}(\theta \nabla \invlap\theta)}{\langle |\mathbb{P}(\theta \nabla \invlap\theta)|^2\rangle^{1/2}}
 \end{equation} 
 %
-where $\mathds{P}$ is the Leray divergence-free projector given by $\mathds{P}(\vec{v}) = \vec{v} - \nabla \Delta^{-1}(\nabla \cdot \vec{v})$ and $\langle \cdot \rangle$ is the spatial average.
+where $\mathbb{P}$ is the Leray divergence-free projector given by $\mathbb{P}(\vec{v}) = \vec{v} - \nabla \Delta^{-1}(\nabla \cdot \vec{v})$ and $\langle \cdot \rangle$ is the spatial average.
 These flows will be studied numerically later and is the main focus of this paper.
@@
 \centering
-\includegraphics[]{images/energy_norms}
+\includegraphics[]{energy_norms}
 \caption{$H^{-1}, L^{2},$ and $H^{1}$ norms of the concentration field under the optimal energy-constrained flow.}
@@
 \begin{figure}
-\includegraphics[]{images/enstrophy_film}
+\includegraphics[]{enstrophy_film}
 \caption{Local-in-time optimisation with enstrophy constraint.
@@
 \begin{figure}
-\includegraphics[]{images/energy_film}
+\includegraphics[]{energy_film}
 \caption{Local-in-time optimisation with energy constraint.
@@
 \begin{figure}
-\includegraphics[]{images/enstrophy_length}
+\includegraphics[]{enstrophy_length}
 \caption{The left subplot shows the filament length $\lambda$ over time subject to the optimal enstrophy-constrained flow.
@@
 \begin{figure}
-\includegraphics[]{images/energy_length}
+\includegraphics[]{energy_length}
 \caption{The left subplot shows the filament length $\lambda$ over time subject to the optimal energy-constrained flow.
@@
 \centering
-\includegraphics[]{images/enstrophy_rate}
+\includegraphics[]{enstrophy_rate}
 \caption{Mixing rate $r(t)$ over time when subject to the optimal enstrophy-constrained flow.}
@@
 \centering
-\includegraphics[]{images/energy_rate}
+\includegraphics[]{energy_rate}
 \caption{The left subplot shows the mixing rate $r(t)$ over time when subject to the optimal energy-constrained flow. The right subplot is the same data except scaled: $r(t)/r_{U} = r(t)/Pe$.}

### 2018-02-28 flux/create_flux_pbs_script.py

@@ -1,113 +1,0 @@
-import numpy as np
-
-
-def create_flux_pbs_script(python_file, dict_of_parameter_lists, script_file_name='flux_pbs.sh', jobname='flux_job', procs=1, memory_mb=4000, walltime='6:00:00', email='cmiless@umich.edu'):
-    """ creates a flux pbs script as output to enclosed folder. It will take in a function and lists of parameters to sweep over as input. """
-
-    # create file
-    f = open(script_file_name, 'w')
-
-    # Create PBS preamble and cd commands
-    f.write("""# !/bin/sh
-#### PBS preamble
-
-#PBS -N %s""" % jobname + """
-
-# Your email:
-#PBS -M  %s""" % email + """
-#PBS -m a
-#PBS -V
-
-# Change the number of cores (ppn=1), amount of memory, and walltime:
-#PBS -l procs=%s""" % str(procs) + "," + "pmem=%s" % str(memory_mb) + "mb,walltime=%s" % walltime + """
-
-# Change "example_flux" to the name of your Flux allocation:
-#PBS -A lsa_flux
-#PBS -q flux
-#PBS -l qos=flux
-
-# End PBS preamble
-
-
-#  Show list of CPUs you ran on, if you're running under PBS
-if [ -n "$PBS_NODEFILE" ]; then cat $PBS_NODEFILE; fi
-
-#  Change to the directory you submitted from
-if [ -n "$PBS_O_WORKDIR" ]; then cd $PBS_O_WORKDIR; fi
-
-#  Put your job commands here:
-
-description=("sim_number = $PBS_ARRAYID")
-echo $description
-
-""")
-
-    # Create parameter lists
-    for parameter_name, parameter_list in dict_of_parameter_lists.items():
-        f.write(str(parameter_name) + "_list=(")
-        for parameter in parameter_list:
-            f.write(" " + str(parameter))
-        f.write(" )\n")
-
-    # Create empty argments list and initialize counter
-    f.write("params=()\n")
-    f.write("count=1\n")
-    f.write("\n")
-
-    # create necessary for-loop statements in script file
-    single_indentation = "   "
-    for i, (parameter_name, parameter_list) in enumerate(dict_of_parameter_lists.items()):
-        indentation = single_indentation * i
-        f.write(indentation + "for %s" % parameter_name +
-                " in ${" + parameter_name + "_list[@]}\n")
-        f.write(indentation + "do\n")
-
-    # Write if statement to match run with flux server queue number
-    indentation += single_indentation
-
[…]

### 2018-02-28 integrators.py

@@ -1,76 +1,0 @@
-import numpy as np
-import pyfftw
-
-
-def FE_timestepper(op, th0, dt):
-    th = th0 + dt * op(th0)
-    return th
-
-
-def RK4_timestepper(op, th0, dt):
-    k1 = op(th0)
-    k2 = op(th0 + 0.5 * dt * k1)
-    k3 = op(th0 + 0.5 * dt * k2)
-    k4 = op(th0 + dt * k3)
-    th = th0 + dt * (1.0 / 6.0) * (k1 + 2.0 * k2 + 2.0 * k3 + k4)
-    return th
-
-
-def FE(op, th0, tarray):
-    return integrator(op, FE_timestepper, th0, tarray)
-
-
-def RK4(op, th0, tarray):
-    return integrator(op, RK4_timestepper, th0, tarray)
-
-
-def integrator(op, timestepper, th0, tarray):
-    num_time_steps = len(tarray)
-    shape = np.shape(th0)
-    N = shape[0]
-    if np.iscomplexobj(th0):
-        th = pyfftw.empty_aligned(
-            (num_time_steps, N, N // 2 + 1), dtype=complex)
-    else:
-        th = pyfftw.empty_aligned(
-            (num_time_steps, N, N), dtype=float)
-    for i, t in enumerate(tarray):
-        if i == 0:
-            th[0] = th0
-        else:
-            dt = tarray[i] - tarray[i - 1]
-            th[i] = timestepper(op, th[i - 1], dt)
-        # print('Time: ', tarray[i])
-    return th
-
-
-def integrator2(op, timestepper, th0, tarray, dt0_cfl):
-    num_time_steps = len(tarray)
-    shape = np.shape(th0)
-    N = shape[0]
-    num_time_steps = len(tarray)
-    if np.iscomplexobj(th0):
-        th = pyfftw.empty_aligned(
-            (num_time_steps, N, N // 2 + 1), dtype=complex)
-    else:
-        th = pyfftw.empty_aligned(
-            (num_time_steps, N, N), dtype=float)
-    for i, t in enumerate(tarray):
-        if i == 0:
-            th[0] = th0
-        else:
-            dt = tarray[i] - tarray[i - 1]
-            M = np.ceil(dt / dt0_cfl).astype('int') if dt > dt0_cfl else 1
-            # print(M)
-            # pdb.set_trace()
-            th[i] = timestepper(op, th[i - 1], dt, M)
-
[…]

### 2018-02-28 operators.py

@@ -1,144 +1,0 @@
-import numpy as np
-from tools import ScalarTool, VectorTool
-import pyfftw
-
-
-class OperatorKit(object):
-    def __init__(self, N, L, kappa):
-        self.N = N
-        self.L = L
-        self.kappa = kappa
-        self.st = ScalarTool(N, L)
-        self.vt = VectorTool(N, L)
-        self.u_sin_flow = np.zeros((2, self.N, self.N))
-        self.u_sin_flow[0] = np.sin((2.0 * np.pi / self.L) * self.st.X[1])
-        self.u_sin_flow_hat = self.vt.fft(self.u_sin_flow)
-        self.u_uniform_flow = np.zeros((2, self.N, self.N))
-        self.u_uniform_flow[0] = np.ones((self.N, self.N))
-
-        # Temporary arrays
-        self.th = pyfftw.empty_aligned((self.N, self.N), dtype=float)
-        self.grad_invlap_th = pyfftw.empty_aligned(
-            (2, self.N, self.N), dtype=float)
-        self.v = pyfftw.empty_aligned((2, self.N, self.N), dtype=float)
-        self.grad_th = pyfftw.empty_aligned((2, self.N, self.N), dtype=float)
-        self.out_hat = pyfftw.empty_aligned((self.N, self.N), dtype=complex)
-
-    def adv_diff_op(self, u, th):
-        op = -np.sum(u * self.st.grad(th), 0) + self.kappa * self.st.lap(th)
-        op = np.real(op)
-        return op
-
-    def adv_diff_op_hat(self, u_hat, th_hat):
-        u = self.vt.ifft(u_hat)
-        th = self.st.ifft(th_hat)
-        op_hat = - self.st.fft(np.sum(u * self.st.grad(th), 0)) - \
-            self.kappa * self.st.K2 * (2 * np.pi / self.L)**2.0 * th_hat
-        return op_hat
-
-    def sin_flow_op(self, th):
-        return self.adv_diff_op(self.u_sin_flow, th)
-
-    def sin_flow_op_hat(self, th_hat):
-        return self.adv_diff_op_hat(self.u_sin_flow_hat, th_hat)
-
-    def uniform_flow_op(self, th):
-        return self.adv_diff_op(self.u_uniform_flow, th)
-
-    def lit_energy_op(self, th, U):
-
-        th_hat = self.st.fft(th)
-
-        grad_invlap_th = self.vt.ifft(-1.0j * self.st.KoverK2 *
[…]

### 2018-02-28 run_simulations_on_flux.py

@@ -1,11 +1,0 @@
-import fluxtools
-from simulations import lit_enstrophy_sim
-
-if __name__ == "__main__":
-    python_file = 'lit_enstrophy.py'
-    flux_folder_name = 'lit_enstrophy2/'
-    dict_of_parameter_lists = {'Pe': [8.0, 16.0, 32.0, 64.0, 128.0, 256.0,
-                                      512.0, 1024.0, 2048.0, 4096.0, 8192.0, 16384.0]}
-
-    fluxtools.run_python_file(
-        python_file, dict_of_parameter_lists, flux_folder_name)

### 2018-02-28 simulations.py

@@ -1,35 +1,0 @@
-from integrators import RK4_timestepper, mega_RK4_timestepper, integrator2, integrator
-from tools import create_grid, dt_cfl
-from operators import OperatorKit
-import numpy as np
-
-
-def lit_enstrophy_sim(N, L, Pe, T, reported_num_time_pts=100, gamma=1.0, cfl=True):
-    kappa = 1.0 / Pe
-
-    # Create tool box
-    okit = OperatorKit(N, L, kappa)
-    # Initial condition
-    X = create_grid(N, L)
-    th0 = np.sin((2.0 * np.pi / L) * X[0])
-
-    # Create operators: d th / dt = operator (th)
-    def lit_enstrophy_op(scalar):
-        return okit.lit_enstrophy_op(scalar, gamma, dealias=False)
-
-    def sin_op(scalar):
-        return okit.sin_flow_op(scalar)
-
-    time_array = np.linspace(0, T, reported_num_time_pts)
-
-    # perform perturbation
-    th0 = RK4_timestepper(sin_op, th0, 0.001 * T)
-
-    if cfl is True:
-        dt0_cfl = 0.01 * dt_cfl(N, L, kappa, gamma * L)
-        th = integrator2(lit_enstrophy_op, mega_RK4_timestepper,
-                         th0, time_array, dt0_cfl)
-    else:
-        th = integrator(lit_enstrophy_op, RK4_timestepper, th0, time_array)
-
-    return [time_array, th]

### 2018-02-28 sol_checking.py

@@ -1,183 +1,0 @@
-from termcolor import colored
-import numpy as np
-from tools import ScalarTool
-from post_processing import compute_norms
-import matplotlib.pyplot as plt
-from tools import ScalarTool
-
-
-def sol_lit_enstrophy_checker(sol_N_collection, sol_M_collection, Pe, L, gamma, T):
-    # last in collection is most resolved
-    best_sol = sol_N_collection[-1]
-    [_, best_sol_th_hist] = best_sol
-    [M, N, _] = np.shape(best_sol_th_hist)
-    [_, l2norm_best_sol, _] = compute_norms(best_sol_th_hist, N, L)
-
-    # Check each criterion
-    print('')
-    print('')
-    print(colored('====== Solution Checker Report ======', 'green'))
-    print('Peclet = ', Pe)
-    print('Box side length = ', L)
-    print('Rate of strain = ', gamma)
-    print('Final time = ', T)
-    print('Number of time steps: ', M)
-    print('Number of modes per side: ', N)
-    print('')
-
-    criteria = []
-
-    [criterion, abs_error_N, rel_error_N] = check_N_convergence(
-        sol_N_collection, L)
-    print('N convergence check: ' + _criterion_report_msg(criterion))
-    criteria.append(criterion)
-
-    [criterion, abs_error_M, rel_error_M] = check_M_convergence(
-        sol_M_collection, L)
-    print('Time step convergence: ' + _criterion_report_msg(criterion))
-    criteria.append(criterion)
-
-    criterion = check_no_spectral_blocking(best_sol, L)
-    print('No spectral blocking check: ' + _criterion_report_msg(criterion))
-    criteria.append(criterion)
-
-    criterion = check_solution_is_resolved_beyond_batchelor_scale(
-        best_sol, Pe)
-    print('Spatial resolution check: ' + _criterion_report_msg(criterion))
-    criteria.append(criterion)
-
-    criterion = check_solution_error_is_tolerable(
-        abs_error_N, rel_error_N, abs_error_M, rel_error_M)
-    print('Absolute and relative error tolerance check: ' +
-          _criterion_report_msg(criterion))
-    criteria.append(criterion)
-
-    criterion = check_L2_decay_relation(best_sol, L, Pe)
[…]

### 2018-02-28 test/test_integrators.py

@@ -1,305 +1,0 @@
-from operators import OperatorKit
-from integrators import FE_timestepper, FE, RK4_timestepper, RK4, mega_RK4_timestepper, integrator2
-import numpy as np
-from tools import ScalarTool, create_grid, dt_cfl
-from copy import copy
-
-
-def test_that_FE_timestepper_has_first_order_convergence():
-    L = 2.0
-    N = 128
-    kappa = 0.5
-    U = 1.0
-
-    X = create_grid(N, L)
-    th0 = np.sin((2.0 * np.pi / L) * X[0])
-    okit = OperatorKit(N, L, kappa)
-
-    def op(th):
-        return okit.sin_flow_op(th)
-
-    st = ScalarTool(N, L)
-
-    # largest time step given by CFL condition
-    dt0 = dt_cfl(N, L, kappa, U)
-    dt_list = dt0 * 2.0**(-np.arange(0, 3, 1))
-    timesteps = 2**(np.arange(0, 3, 1))
-    finalth_list = []
-    for i, dt in enumerate(dt_list):
-        th = copy(th0)
-        for step in range(timesteps[i]):
-            th = FE_timestepper(op, th, dt)
-        finalth_list.append(th)
-
-    error_large_small = abs(
-        st.l2norm(finalth_list[0] - finalth_list[2]))
-    error_medium_small = abs(
-        st.l2norm(finalth_list[1] - finalth_list[2]))
-
-    p = np.log2(error_large_small / error_medium_small - 1)
-    print('p = ', p)
-    assert abs(p - 1) < 0.1
-
-
-def test_mean_of_th_is_zero_at_end_time():
-    L = 2.0
-    N = 128
-    kappa = 0.1
-    X = create_grid(N, L)
-    th0 = np.sin((2.0 * np.pi / L) * X[0])
-    okit = OperatorKit(N, L, kappa)
-
-    def op(th):
-        return okit.sin_flow_op(th)
-
-    tarray = np.linspace(0, 0.01, 101)
-    th = FE(op, th0, tarray)
-
-    assert np.isclose(np.mean(th[-1]), 0)
-
-
-def test_that_RK4_timestepper_has_fourth_order_convergence():
-    L = 2.0
-    N = 128
-    kappa = 0.05
-    U = 1.0
-
-    X = create_grid(N, L)
-    th0 = np.sin((2.0 * np.pi / L) * X[0])
-    okit = OperatorKit(N, L, kappa)
-
[…]

### 2018-02-28 test/test_operators.py

@@ -1,161 +1,0 @@
-from tools import ScalarTool, create_grid, VectorTool
-from operators import OperatorKit
-import numpy as np
-import pytest
-
-
-def test_that_adv_diff_operator_output_is_real():
-    L = 10.0
-    N = 128
-    kappa = 0.1
-    X = create_grid(N, L)
-    u = np.zeros((2, N, N))
-    u[0] = np.sin((2.0 * np.pi / L) * X[1])
-    th = np.sin((2.0 * np.pi / L) * X[0])
-    op = OperatorKit(N, L, kappa)
-    assert np.all(np.isreal(op.adv_diff_op(u, th)))
-
-
-def test_that_average_of_adv_diff_operator_is_0():
-    L = 10.0
-    N = 128
-    kappa = 0.1
-    X = create_grid(N, L)
-    u = np.zeros((2, N, N))
-    u[0] = np.sin((2.0 * np.pi / L) * X[1])
-    th = np.sin((2.0 * np.pi / L) * X[0])
-    op = OperatorKit(N, L, kappa)
-    mean_op = np.mean(op.adv_diff_op(u, th))
-    assert np.isclose(mean_op, 0.0)
-
-
-def test_integral_of_theta_times_adv_diff_op_is_equal_to_neg_kappa_h1norm_sq():
-    L = 10.0
-    N = 256
-    kappa = 0.1
-    X = create_grid(N, L)
-    st = ScalarTool(N, L)
-    u = np.zeros((2, N, N))
-    u[0] = np.sin((2.0 * np.pi / L) * X[1])
-    th = np.sin((2.0 * np.pi / L) * X[0])
-    op = OperatorKit(N, L, kappa)
-    assert np.isclose(
-        st.sint(th * op.adv_diff_op(u, th)), - kappa * st.h1norm(th)**2.0)
-
-
-def test_that_adv_diff_operator_output_size():
-    L = 10.0
-    N = 128
-    kappa = 0.1
-    X = create_grid(N, L)
-    u = np.zeros((2, N, N))
-    u[0] = np.sin((2.0 * np.pi / L) * X[1])
-    th = np.sin((2.0 * np.pi / L) * X[0])
-    op = OperatorKit(N, L, kappa)
-    assert np.shape(op.adv_diff_op(u, th)) == (N, N)
-
-
-def test_that_average_of_adv_diff_operator_hat_is_0():
-    L = 10.0
[…]

### 2018-02-28 test/test_simulations.py

@@ -1,39 +1,0 @@
-from simulations import lit_enstrophy_sim
-from sol_checking import sol_lit_enstrophy_checker
-from tools import dt_cfl
-import numpy as np
-
-
-def test_lit_enstrophy_sim():
-    Pe = 128.0
-    L = 1.0
-    gamma = 1.0
-    kappa = 1. / Pe
-    T = 0.0001
-
-    N_largest = 128  # largest number of modes
-
-    dt_stable_for_N_largest = dt_cfl(N_largest, L, kappa, gamma * L)
-    M_smallest = int(np.ceil(T / dt_stable_for_N_largest))
-    # M_smallest = 1
-    M_largest = 16 * M_smallest  # largest number of time steps
-
-    sol_N_collection = []
-    for N in [N_largest // 16, N_largest // 8, N_largest // 4, N_largest // 2]:
-        # print(N)
-        sol_N_collection.append(lit_enstrophy_sim(
-            N, L, Pe, T, M_largest, cfl=False))
-
-    sol_M_collection = []
-    for M in [M_largest // 16, M_largest // 8, M_largest // 4, M_largest // 2]:
-        # print(M)
-        sol_M_collection.append(lit_enstrophy_sim(
-            N_largest, L, Pe, T, M, cfl=False))
-
-    best_solution = lit_enstrophy_sim(
-        N_largest, L, Pe, T, M_largest, cfl=False)
-    sol_N_collection.append(best_solution)
-    sol_M_collection.append(best_solution)
-
-    assert sol_lit_enstrophy_checker(
-        sol_N_collection, sol_M_collection, Pe=Pe, L=L, gamma=gamma, T=T)

### 2018-02-28 test/test_sol_checking.py

@@ -1,27 +1,0 @@
-from sol_checking import _sequence_converges_to_zero, _criterion_report_msg
-import numpy as np
-from tools import ScalarTool
-from termcolor import colored
-
-
-def test_convergent_sequence():
-    a = list(2.**(-1.0 * np.linspace(1., 100., 100.)))
-    assert _sequence_converges_to_zero(a)
-
-
-def test_divergent_sequence():
-    a = list(2.**(1.0 * np.linspace(1., 100., 100.)))
-    assert (not _sequence_converges_to_zero(a))
-
-
-def test_near_zero_sequence():
-    a = list(np.random.random(100) * 10. ** (-16))
-    assert _sequence_converges_to_zero(a)
-
-
-def test_criterion_report_msg_passed():
-    assert colored('PASSED', 'green') == _criterion_report_msg(True)
-
-
-def test_criterion_report_msg_failed():
-    assert colored('FAILED', 'red') == _criterion_report_msg(False)

### 2018-02-28 flux_pbs.sh
update gitignore and added new files

@@ -1,0 +1,46 @@
+# !/bin/sh
+#### PBS preamble
+
+#PBS -N lit_enstrophy
+
+# Your email:
+#PBS -M  cmiless@umich.edu
+#PBS -m a
+#PBS -V
+
+# Change the number of cores (ppn=1), amount of memory, and walltime:
+#PBS -l procs=1,pmem=8000mb,walltime=10:00:00
+
+# Change "example_flux" to the name of your Flux allocation:
+#PBS -A lsa_flux
+#PBS -q flux
+#PBS -l qos=flux
+
+# End PBS preamble
+
+
+#  Show list of CPUs you ran on, if you're running under PBS
+if [ -n "$PBS_NODEFILE" ]; then cat $PBS_NODEFILE; fi
+
+#  Change to the directory you submitted from
+if [ -n "$PBS_O_WORKDIR" ]; then cd $PBS_O_WORKDIR; fi
+
+#  Put your job commands here:
+
+description=("sim_number = $PBS_ARRAYID")
+echo $description
+
+Pe_list=(128.0 256.0 512.0 1024.0 2048.0 4096.0 8192.0 16384.0)
+params=()
+count=1
+
+for Pe in ${Pe_list[@]}
+do
+      if [ "$count" = "$PBS_ARRAYID" ]
+      then
+         description=("Pe=$Pe")
+         arguments=("$Pe ")
+         python lit_enstrophy.py $arguments -> log-$description.txt
+      fi
+      count=`expr $count + 1`
+done

### 2018-02-28 flux_pbs_inf.sh

@@ -1,0 +1,30 @@
+# !/bin/sh
+#### PBS preamble
+
+#PBS -N lit_enstrophy_inf
+
+# Your email:
+#PBS -M  cmiless@umich.edu
+#PBS -m a
+#PBS -V
+
+# Change the number of cores (ppn=1), amount of memory, and walltime:
+#PBS -l procs=4,pmem=8000mb,walltime=24:00:00
+
+# Change "example_flux" to the name of your Flux allocation:
+#PBS -A lsa_flux
+#PBS -q flux
+#PBS -l qos=flux
+
+# End PBS preamble
+
+
+#  Show list of CPUs you ran on, if you're running under PBS
+if [ -n "$PBS_NODEFILE" ]; then cat $PBS_NODEFILE; fi
+
+#  Change to the directory you submitted from
+if [ -n "$PBS_O_WORKDIR" ]; then cd $PBS_O_WORKDIR; fi
+
+#  Put your job commands here:
+
+python lit_enstrophy_inf.py

### 2018-02-28 lit_enstrophy_inf.py

@@ -1,0 +1,76 @@
+from integrators import RK4_timestepper, mega_RK4_timestepper, integrator2
+from tools import ScalarTool, create_grid, dt_cfl, N_boyd
+from post_processing import plot_norms, movie
+from operators import OperatorKit
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+import time
+import pickle
+import os
+import sys
+
+if __name__ == "__main__":
+    # Parameters
+    L = 1.0
+
+    kappa = 0.0
+    gamma = 1.0
+    T = 13.0
+
+    # lb = (kappa / gamma)**0.5
+    # l_smallest = lb
+    # print('lb = ', lb)
+    #
+    # M = L / l_smallest
+    # print('N_boyd = ', N_boyd(M))
+    # N = min(N_boyd(M), 512)
+    # N = 64
+    N = 1024
+    print('N = ', N)
+
+    # Create tool box
+    okit = OperatorKit(N, L, kappa)
+    st = ScalarTool(N, L)
+
+    # Initial condition
+    X = create_grid(N, L)
+    th0 = np.sin((2.0 * np.pi / L) * X[0])
+
+    # Create operators: d th / dt = operator (th)
+    def lit_enstrophy_op(scalar):
+        return okit.lit_enstrophy_op(scalar, gamma)
+
+    def sin_op(scalar):
+        return okit.sin_flow_op(scalar)
+
+    # Perform simulation
+    time_array = np.linspace(0, T, 200)
+    th0 = RK4_timestepper(sin_op, th0, 0.001)
+    start_time = time.time()
+    dt0_cfl = 0.25 * dt_cfl(N, L, kappa, gamma * L)
+    th = integrator2(lit_enstrophy_op, mega_RK4_timestepper,
+                     th0, time_array, dt0_cfl)
+
+    print(time.time() - start_time)
+
+    # Output
+    output_folder = 'output-pe=inf/'
+    os.system('mkdir ' + output_folder)
+    os.system('cp lit_enstrophy_inf.py ' + output_folder)
+
+    plt.figure()
+    st.plot(th[-1])
+    plt.savefig(output_folder + 'plot_final_frame-pe=inf.png')
+
+    plt.figure()
+    plot_norms(time_array, th, N, L)
+    plt.savefig(output_folder + 'plot_norms-pe=inf.png')
+
+    movie(time_array, th, N, L, output_path=output_folder)
+
[…]

### 2018-02-28 lit_rerun.py

@@ -1,0 +1,187 @@
+import tools
+import numpy as np
+import matplotlib.pyplot as plt
+import copy
+import time
+import os
+import pickle
+import pprint
+
+
+class sol(object):
+    def __init__(self):
+        self.M = 0  # Number of timepts
+        self.N = 0  # Number of spatial grid points in a single dimension
+        self.T = 0.  # Final time
+        self.dt = 0.
+        self.Pe = 0.  # Peclet
+        self.L = 0.  # Length of box side
+        self.hist_th_hm1 = []
+        self.hist_th_l2 = []
+        self.hist_th_h1 = []
+        self.hist_time = []
+        self.hist_th = []
+        self.hist_u = []
+        self.hist_u_h1 = []
+        self.hist_u_l2 = []
+
+
+def sim(N=128, M=10000, T=13.0, L=1.0, gamma=1.0, Pe=1024, T_kick=0.01,
+        save_every=100, pickle_file=None, plot=False):
+
+    def f(th, u):
+        return -1.0 * np.sum(vt.dealias(u) * st.grad(st.dealias(th)), 0) + kappa * st.lap(st.dealias(th))
+        # return -1.0*np.sum(u*st.grad(th),0) + kappa * st.lap(th)
+
+    def f_lit(th):
+        return f(th, u_lit(th))
+
+    def u_lit(th):
+        u_lit = st.dealias(th) * vt.dealias(st.grad_invlap(th))
+        u_lit = - vt.invlap(vt.div_free_proj(u_lit))
+        u_lit = gamma * L * u_lit / st.l2norm(vt.curl(u_lit))
+        return u_lit
+
+    # Parameters
+    h = L / N
+    kappa = 1. / Pe
+    print('Pe = ', Pe)
+    if np.isinf(Pe):
+        dt_cfl = (L / N) / (gamma * L)
+        print('dt (CFL) = ', dt_cfl)
+    else:
+        length_min = 0.25 * 1. / (Pe)**0.5
+        M_boyd = L / length_min
+        N_boyd = int(2**np.ceil(np.log2(4 * (M_boyd - 1) + 6)))
+        dt_cfl = min((L / N)**2. / kappa, (L / N) / (gamma * L))
+        print('dt (CFL) = ', dt_cfl)
+        print('N (Boyd) = ', N_boyd)
+    print('N =', N)
+
[…]

### 2018-02-28 lit_enstrophy.py
removed more files

@@ -1,78 +1,0 @@
-from simulations import lit_enstrophy_sim
-from integrators import RK4_timestepper, mega_RK4_timestepper, integrator2
-from tools import ScalarTool, create_grid, dt_cfl, N_boyd
-from post_processing import plot_norms, movie
-from operators import OperatorKit
-import numpy as np
-import matplotlib
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-
-import time
-import pickle
-import os
-import sys
-
-if __name__ == "__main__":
-    # Parameters
-    L = 1.0
-    Pe = float(sys.argv[1])
-    print('Pe = ', Pe)
-    kappa = 1.0 / Pe
-    gamma = 1.0
-    T = 13.0
-
-    lb = (kappa / gamma)**0.5
-    l_smallest = 0.2 * lb
-    print('lb = ', lb)
-
-    M = L / l_smallest
-    print('N_boyd = ', N_boyd(M))
-    N = min(N_boyd(M), 512)
-    # N = 64
-    # N = int(sys.argv[2])
-    print('N = ', N)
-
-    # Create tool box
-    okit = OperatorKit(N, L, kappa)
-    st = ScalarTool(N, L)
-
-    # Initial condition
-    X = create_grid(N, L)
-    th0 = np.sin((2.0 * np.pi / L) * X[0])
-
-    # Create operators: d th / dt = operator (th)
-    def lit_enstrophy_op(scalar):
-        return okit.lit_enstrophy_op(scalar, gamma)
-
-    def sin_op(scalar):
-        return okit.sin_flow_op(scalar)
-
-    # Perform simulation
-    time_array = np.linspace(0, T, 200)
-    th0 = RK4_timestepper(sin_op, th0, 0.0001)
-    start_time = time.time()
-    dt0_cfl = 0.1 * dt_cfl(N, L, kappa, gamma * L)
-    th = integrator2(lit_enstrophy_op, mega_RK4_timestepper,
-                     th0, time_array, dt0_cfl)
-
-    print(time.time() - start_time)
-
-    # Output
-    output_folder = 'output-pe=%d' % Pe + '/'
-    os.system('mkdir ' + output_folder)
-    os.system('cp lit_enstrophy.py ' + output_folder)
-
-    plt.figure()
-    st.plot(th[-1])
-    plt.savefig(output_folder + 'plot_final_frame-pe=%d' % Pe + '.png')
-
-    plt.figure()
[…]

### 2018-02-28 lit_enstrophy_inf.py

@@ -1,76 +1,0 @@
-from integrators import RK4_timestepper, mega_RK4_timestepper, integrator2
-from tools import ScalarTool, create_grid, dt_cfl, N_boyd
-from post_processing import plot_norms, movie
-from operators import OperatorKit
-import numpy as np
-import matplotlib
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-
-import time
-import pickle
-import os
-import sys
-
-if __name__ == "__main__":
-    # Parameters
-    L = 1.0
-
-    kappa = 0.0
-    gamma = 1.0
-    T = 13.0
-
-    # lb = (kappa / gamma)**0.5
-    # l_smallest = lb
-    # print('lb = ', lb)
-    #
-    # M = L / l_smallest
-    # print('N_boyd = ', N_boyd(M))
-    # N = min(N_boyd(M), 512)
-    # N = 64
-    N = 1024
-    print('N = ', N)
-
-    # Create tool box
-    okit = OperatorKit(N, L, kappa)
-    st = ScalarTool(N, L)
-
-    # Initial condition
-    X = create_grid(N, L)
-    th0 = np.sin((2.0 * np.pi / L) * X[0])
-
-    # Create operators: d th / dt = operator (th)
-    def lit_enstrophy_op(scalar):
-        return okit.lit_enstrophy_op(scalar, gamma)
-
-    def sin_op(scalar):
-        return okit.sin_flow_op(scalar)
-
-    # Perform simulation
-    time_array = np.linspace(0, T, 200)
-    th0 = RK4_timestepper(sin_op, th0, 0.001)
-    start_time = time.time()
-    dt0_cfl = 0.25 * dt_cfl(N, L, kappa, gamma * L)
-    th = integrator2(lit_enstrophy_op, mega_RK4_timestepper,
-                     th0, time_array, dt0_cfl)
-
-    print(time.time() - start_time)
-
-    # Output
-    output_folder = 'output-pe=inf/'
-    os.system('mkdir ' + output_folder)
-    os.system('cp lit_enstrophy_inf.py ' + output_folder)
-
-    plt.figure()
-    st.plot(th[-1])
-    plt.savefig(output_folder + 'plot_final_frame-pe=inf.png')
-
-    plt.figure()
-    plot_norms(time_array, th, N, L)
-    plt.savefig(output_folder + 'plot_norms-pe=inf.png')
-
-    movie(time_array, th, N, L, output_path=output_folder)
-
[…]

### 2018-02-28 lit_rerun.py

@@ -1,187 +1,0 @@
-import tools
-import numpy as np
-import matplotlib.pyplot as plt
-import copy
-import time
-import os
-import pickle
-import pprint
-
-
-class sol(object):
-    def __init__(self):
-        self.M = 0  # Number of timepts
-        self.N = 0  # Number of spatial grid points in a single dimension
-        self.T = 0.  # Final time
-        self.dt = 0.
-        self.Pe = 0.  # Peclet
-        self.L = 0.  # Length of box side
-        self.hist_th_hm1 = []
-        self.hist_th_l2 = []
-        self.hist_th_h1 = []
-        self.hist_time = []
-        self.hist_th = []
-        self.hist_u = []
-        self.hist_u_h1 = []
-        self.hist_u_l2 = []
-
-
-def sim(N=128, M=10000, T=13.0, L=1.0, gamma=1.0, Pe=1024, T_kick=0.01,
-        save_every=100, pickle_file=None, plot=False):
-
-    def f(th, u):
-        return -1.0 * np.sum(vt.dealias(u) * st.grad(st.dealias(th)), 0) + kappa * st.lap(st.dealias(th))
-        # return -1.0*np.sum(u*st.grad(th),0) + kappa * st.lap(th)
-
-    def f_lit(th):
-        return f(th, u_lit(th))
-
-    def u_lit(th):
-        u_lit = st.dealias(th) * vt.dealias(st.grad_invlap(th))
-        u_lit = - vt.invlap(vt.div_free_proj(u_lit))
-        u_lit = gamma * L * u_lit / st.l2norm(vt.curl(u_lit))
-        return u_lit
-
-    # Parameters
-    h = L / N
-    kappa = 1. / Pe
-    print('Pe = ', Pe)
-    if np.isinf(Pe):
-        dt_cfl = (L / N) / (gamma * L)
-        print('dt (CFL) = ', dt_cfl)
-    else:
-        length_min = 0.25 * 1. / (Pe)**0.5
-        M_boyd = L / length_min
-        N_boyd = int(2**np.ceil(np.log2(4 * (M_boyd - 1) + 6)))
-        dt_cfl = min((L / N)**2. / kappa, (L / N) / (gamma * L))
-        print('dt (CFL) = ', dt_cfl)
-        print('N (Boyd) = ', N_boyd)
-    print('N =', N)
-
[…]

### 2018-02-28 post_processing.py

@@ -1,75 +1,0 @@
-import numpy as np
-import matplotlib
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-
-from tools import ScalarTool, VectorTool
-import pyfftw
-
-import os
-
-
-def compute_norms(scalar_hist, N, L):
-    st = ScalarTool(N, L)
-    time_length, _, _ = np.shape(scalar_hist)
-
-    hm1norm_hist = np.zeros(time_length)
-    l2norm_hist = np.zeros(time_length)
-    h1norm_hist = np.zeros(time_length)
-
-    for i, scalar in enumerate(scalar_hist):
-        hm1norm_hist[i] = st.hm1norm(scalar)
-        l2norm_hist[i] = st.l2norm(scalar)
-        h1norm_hist[i] = st.h1norm(scalar)
-
-    return [hm1norm_hist, l2norm_hist, h1norm_hist]
-
-
-def plot_norms(time, scalar_hist, N, L, high_quality=False, graph='log'):
-    if high_quality:
-        plt.rc('text', usetex=True)
-        plt.rc('font', family='serif', size=12)
-    else:
-        plt.rc('text', usetex=False)
-        plt.rc('font', family='sans-serif', size=12)
-    hm1norm_hist, l2norm_hist, h1norm_hist = compute_norms(scalar_hist, N, L)
-
-    if graph == 'log':
-        plt.semilogy(time, hm1norm_hist,
-                     label=r'$H^{-1}$', linestyle='-', color='k')
-        plt.semilogy(time, l2norm_hist, label=r'$L^2$',
-                     linestyle='--', color='k')
-        plt.semilogy(time, h1norm_hist,
-                     label=r'$H^{1}$', linestyle=':', color='k')
-    elif graph == 'linear':
-        plt.plot(time, hm1norm_hist,
-                 label=r'$H^{-1}$', linestyle='-', color='k')
-        plt.plot(time, l2norm_hist, label=r'$L^2$',
-                 linestyle='--', color='k')
-        plt.plot(time, h1norm_hist,
-                 label=r'$H^{1}$', linestyle=':', color='k')
-
-    plt.legend()
-    plt.xlabel('Time')
-    plt.grid(alpha=0.5)
-
-
-def movie(time, scalar_hist, N, L, output_path='output/'):
-    os.system('mkdir ' + output_path)
-    os.system('mkdir ' + output_path + 'images/')
-    st = ScalarTool(N, L)
-    # st.plot(scalar_hist[i])
[…]

### 2018-02-28 lit.py
added mroe files

@@ -1,0 +1,253 @@
+import tools
+import numpy as np
+import matplotlib.pyplot as plt
+import copy
+import time
+import os
+import pickle
+import pprint
+
+
+class sol(object):
+    def __init__(self):
+        self.M = 0  # Number of timepts
+        self.N = 0  # Number of spatial grid points in a single dimension
+        self.T = 0.  # Final time
+        self.dt = 0.
+        self.Pe = 0.  # Peclet
+        self.L = 0.  # Length of box side
+        self.hist_th_hm1 = []
+        self.hist_th_l2 = []
+        self.hist_th_h1 = []
+        self.hist_time = []
+        self.hist_th = []
+        self.hist_u = []
+        self.hist_u_h1 = []
+        self.hist_u_l2 = []
+
+
+def sim(N=128, M=10000, T=13.0, L=1.0, gamma=1.0, Pe=1024, T_kick=0.01,
+        save_every=100, pickle_file=None, plot=False):
+
+    def f(th, u):
+        return -1.0 * np.sum(vt.dealias(u) * st.grad(st.dealias(th)), 0) + kappa * st.lap(st.dealias(th))
+        # return -1.0*np.sum(u*st.grad(th),0) + kappa * st.lap(th)
+
+    def f_lit(th):
+        return f(th, u_lit(th))
+
+    def u_lit(th):
+        u_lit = st.dealias(th) * vt.dealias(st.grad_invlap(th))
+        u_lit = - vt.invlap(vt.div_free_proj(u_lit))
+        u_lit = gamma * L * u_lit / st.l2norm(vt.curl(u_lit))
+        return u_lit
+
+    # Parameters
+    h = L / N
+    kappa = 1. / Pe
+    print('Pe = ', Pe)
+    if np.isinf(Pe):
+        dt_cfl = (L / N) / (gamma * L)
+        print('dt (CFL) = ', dt_cfl)
+    else:
+        length_min = 0.25 * 1. / (Pe)**0.5
+        M_boyd = L / length_min
+        N_boyd = int(2**np.ceil(np.log2(4 * (M_boyd - 1) + 6)))
+        dt_cfl = min((L / N)**2. / kappa, (L / N) / (gamma * L))
+        print('dt (CFL) = ', dt_cfl)
+        print('N (Boyd) = ', N_boyd)
+    print('N =', N)
+
+    # ## Double precision
+    ftype = np.float64
[…]

### 2018-02-28 flux_pbs.sh
removed flux file

@@ -40,7 +40,12 @@ do
       then
          description=("Pe=$Pe")
          arguments=("$Pe ")
-         python lit_enstrophy.py $arguments -> log-$description.txt
+         python lit.py $arguments -> log-$description.txt
       fi
       count=`expr $count + 1`
 done
+
+if [ "$PBS_ARRAYID" = 9 ]
+then
+   python lit.py "inf" -> log-$description.txt
+fi

### 2018-02-28 flux_pbs_inf.sh

@@ -1,30 +1,0 @@
-# !/bin/sh
-#### PBS preamble
-
-#PBS -N lit_enstrophy_inf
-
-# Your email:
-#PBS -M  cmiless@umich.edu
-#PBS -m a
-#PBS -V
-
-# Change the number of cores (ppn=1), amount of memory, and walltime:
-#PBS -l procs=4,pmem=8000mb,walltime=24:00:00
-
-# Change "example_flux" to the name of your Flux allocation:
-#PBS -A lsa_flux
-#PBS -q flux
-#PBS -l qos=flux
-
-# End PBS preamble
-
-
-#  Show list of CPUs you ran on, if you're running under PBS
-if [ -n "$PBS_NODEFILE" ]; then cat $PBS_NODEFILE; fi
-
-#  Change to the directory you submitted from
-if [ -n "$PBS_O_WORKDIR" ]; then cd $PBS_O_WORKDIR; fi
-
-#  Put your job commands here:
-
-python lit_enstrophy_inf.py

### 2018-02-28 lit.py

@@ -4,6 +4,7 @@ import matplotlib.pyplot as plt
 import copy
 import time
 import os
+import sys
 import pickle
 import pprint
 
@@ -77,9 +78,6 @@ def sim(N=128, M=10000, T=13.0, L=1.0, gamma=1.0, Pe=1024, T_kick=0.01,
 
     st = tools.ScalarTool(N, L)
     vt = tools.VectorTool(N, L)
-
-    temp_folder = 'temp/'
-    os.system('mkdir ' + temp_folder)
 
     th = np.zeros((total_time_pts, N, N))
     th0 = np.sin(2. * np.pi * X[0] / L)
@@ -180,7 +178,7 @@ def sim(N=128, M=10000, T=13.0, L=1.0, gamma=1.0, Pe=1024, T_kick=0.01,
 def movie(time, scalar_hist, N, L, output_path='output/'):
     os.system('mkdir ' + output_path)
     os.system('mkdir ' + output_path + 'images/')
-    st = ScalarTool(N, L)
+    st = tools.ScalarTool(N, L)
     # st.plot(scalar_hist[i])
     # plt.savefig(outputPath + "image%.4d.png" % i, format='png')
     for i in range(len(time)):
@@ -199,7 +197,7 @@ def movie(time, scalar_hist, N, L, output_path='output/'):
 
 
 def compute_norms(scalar_hist, N, L):
-    st = ScalarTool(N, L)
+    st = tools.ScalarTool(N, L)
     time_length, _, _ = np.shape(scalar_hist)
 
     hm1norm_hist = np.zeros(time_length)
@@ -245,9 +243,53 @@ def plot_norms(time, scalar_hist, N, L, high_quality=False, graph='log'):
 
 if __name__ == "__main__":
 
-    N = int(sys.argv[0])
-    Pe = int(sys.argv[1])
-    pickle_file = "pe=" + str(Pe) + ".pkl"
+    arg = sys.argv[1]
+    if arg == 'inf':
+        Pe = np.inf
+    else:
+        Pe = float(arg)
 
-    sim(N=N, M=1000, T=13.0, L=1.0, gamma=1.0, Pe=1024,
-        save_every=10, pickle_file=pickle_file, plot=False)
+    L = 1.0
+    kappa = 1.0 / Pe
+    gamma = 1.0
+    T = 0.01
+
+    if Pe == np.inf:
+        N = 512
+        dt_cfl = (L / N) / (gamma * L)
+    else:
+        lb = (kappa / gamma)**0.5
[…]

### 2018-02-28 test/test_lit.py

@@ -1,0 +1,34 @@
+import tools
+import lit
+import numpy as np
+import math
+
+
+def test_fourth_order_convergence_of_entrophy_constained_lit_simulation():
+    s = []
+    ss = []
+    N = 256
+    L = 1.0
+    M_list = [1, 2, 4]
+    T = 0.01
+    Pe = 512
+
+    dt_list = []
+    for M in M_list:
+        s.append(lit.sim(N=N, M=M, T=T, L=L, save_every=1,
+                         T_kick=0.01, Pe=Pe, plot=False))
+        dt_list.append(T / M)
+    error_list = []
+    st = tools.ScalarTool(N, L)
+    for i in range(len(M_list) - 1):
+        error_list.append(st.l2norm(s[i].hist_th[-1] - s[2].hist_th[-1]))
+
+    error_array = np.array(error_list)
+    dt_array = np.array(dt_list)
+    #print(st.l2norm(s[-3].hist_th[-1] - s[-2].hist_th[-1]))
+    #print(st.l2norm(s[-2].hist_th[-1] - s[-1].hist_th[-1]))
+    R = st.l2norm(s[0].hist_th[-1] - s[1].hist_th[-1]) / \
+        st.l2norm(s[1].hist_th[-1] - s[2].hist_th[-1])
+    p = np.log(R) / np.log(2)
+    print('p = ', p)
+    assert abs(p - 4) < 0.5

### 2018-02-28 flux_pbs.sh
fixed errors so compatible with flux

@@ -9,7 +9,7 @@
 #PBS -V
 
 # Change the number of cores (ppn=1), amount of memory, and walltime:
-#PBS -l procs=1,pmem=8000mb,walltime=10:00:00
+#PBS -l procs=1,pmem=8000mb,walltime=24:00:00
 
 # Change "example_flux" to the name of your Flux allocation:
 #PBS -A lsa_flux
@@ -47,5 +47,6 @@ done
 
 if [ "$PBS_ARRAYID" = 9 ]
 then
+    description=("Pe=inf")
    python lit.py "inf" -> log-$description.txt
 fi

### 2018-02-28 lit.py

@@ -46,18 +46,6 @@ def sim(N=128, M=10000, T=13.0, L=1.0, gamma=1.0, Pe=1024, T_kick=0.01,
     # Parameters
     h = L / N
     kappa = 1. / Pe
-    print('Pe = ', Pe)
-    if np.isinf(Pe):
-        dt_cfl = (L / N) / (gamma * L)
-        print('dt (CFL) = ', dt_cfl)
-    else:
-        length_min = 0.25 * 1. / (Pe)**0.5
-        M_boyd = L / length_min
-        N_boyd = int(2**np.ceil(np.log2(4 * (M_boyd - 1) + 6)))
-        dt_cfl = min((L / N)**2. / kappa, (L / N) / (gamma * L))
-        print('dt (CFL) = ', dt_cfl)
-        print('N (Boyd) = ', N_boyd)
-    print('N =', N)
 
     # ## Double precision
     ftype = np.float64
@@ -67,7 +55,6 @@ def sim(N=128, M=10000, T=13.0, L=1.0, gamma=1.0, Pe=1024, T_kick=0.01,
     print('dt = ', dt)
     final_time_ind = total_steps
     total_time_pts = total_steps + 1
-    time_array = np.linspace(0, T, total_time_pts, dtype=ftype)
 
     X = np.mgrid[:N, :N].astype(ftype) * h
     Nf = N // 2 + 1
@@ -79,71 +66,70 @@ def sim(N=128, M=10000, T=13.0, L=1.0, gamma=1.0, Pe=1024, T_kick=0.01,
     st = tools.ScalarTool(N, L)
     vt = tools.VectorTool(N, L)
 
-    th = np.zeros((total_time_pts, N, N))
     th0 = np.sin(2. * np.pi * X[0] / L)
-    th[0] = copy.copy(th0)
+    th = copy.copy(th0)
 
     # Initial kick
     # The default value for T_kick equal to 0.01 is sufficient to
     # initiate LIT optimization.
 
-    num_steps_kick = max(round(T_kick / dt), 10)
+    num_steps_kick = int(max(round(T_kick / dt), 10))
     dt_kick = T_kick / num_steps_kick
 
     u_kick = np.zeros((2, N, N), dtype=ftype)
     u_kick[0, :, :] = np.sin(2. * np.pi * X[1] / L)
 
     for i in range(num_steps_kick):
-        k1 = f(th[0], u_kick)
-        k2 = f(th[0] + 0.5 * dt_kick * k1, u_kick)
[…]

### 2018-02-28 lit.py
added energy constraint

@@ -27,23 +27,33 @@ class sol(object):
         self.hist_u_l2 = []
 
 
-def sim(N=128, M=10000, T=13.0, L=1.0, gamma=1.0, Pe=1024, T_kick=0.01,
-        save_every=100, pickle_file=None, plot=False):
+def sim(N=128, M=1000, T=1.0, L=1.0, gamma=1.0, U=1.0, Pe=1024, T_kick=0.01,
+        save_every=10, pickle_file=None, plot=False, constraint='enstrophy'):
 
     def f(th, u):
         return -1.0 * np.sum(vt.dealias(u) * st.grad(st.dealias(th)), 0) + kappa * st.lap(st.dealias(th))
-        # return -1.0*np.sum(u*st.grad(th),0) + kappa * st.lap(th)
 
     def f_lit(th):
         return f(th, u_lit(th))
 
-    def u_lit(th):
+    def u_lit_enstrophy(th):
         u_lit = st.dealias(th) * vt.dealias(st.grad_invlap(th))
         u_lit = - vt.invlap(vt.div_free_proj(u_lit))
         u_lit = gamma * L * u_lit / st.l2norm(vt.curl(u_lit))
         return u_lit
 
-    # Parameters
+    def u_lit_energy(th):
+        u_lit = st.dealias(th) * vt.dealias(st.grad_invlap(th))
+        u_lit = vt.div_free_proj(u_lit)
+        u_lit = U * L * u_lit / vt.l2norm(u_lit)
+        return u_lit
+
+    if constraint == 'enstrophy':
+        u_lit = u_lit_enstrophy
+    elif constraint == 'energy':
+        u_lit = u_lit_energy
+
+        # Parameters
     h = L / N
     kappa = 1. / Pe
 
@@ -237,20 +247,39 @@ if __name__ == "__main__":
 
     L = 1.0
     kappa = 1.0 / Pe
-    gamma = 1.0
-    T = 13.0
+    constraint = "energy"
+    U = 1.0
+    T = 2.0
 
-    if Pe == np.inf:
-        N = 512
-        dt_cfl = 0.25 * (L / N) / (gamma * L)
-    else:
-        lb = (kappa / gamma)**0.5
-        l_smallest = 0.25 * lb  # a quarter of batchelor scale
-        print('lb = ', lb)
-        num_wavelengths = L / l_smallest
-        print('N_boyd = ', tools.N_boyd(num_wavelengths))
-        N = min(tools.N_boyd(num_wavelengths), 512)
[…]

### 2018-02-28 test/test_tools.py

@@ -1,4 +1,4 @@
-from tools import ScalarTool, VectorTool, create_grid, dt_cfl
+from tools import ScalarTool, VectorTool
 import numpy as np
 import math
 from tools import N_boyd
@@ -60,14 +60,6 @@ def test_l2norm_squared_of_curl_of_vector_is_spatial_integral_of_neg_vector_time
     a = st.l2norm(curl)**2.
     b = st.sint(np.sum(-vt.lap(v) * v, 0))
     assert np.allclose(a, b)
-
-
-def test_that_dt_cfl_works_for_kappa_0():
-    N = 128
-    L = 2.0
-    kappa = 0.0
-    U = 3.0
-    assert math.isclose(dt_cfl(N, L, kappa, U), L / (N * U))
 
 
 def test_that_l2norm_of_sinx_on_domain_with_L_of_2pi_equals_sqrt_of_half_of_Lsq():
@@ -202,27 +194,6 @@ def test_laplacian_of_sinkx_is_neq_ksq_times_sinkx():
     lapth = st.lap(th)
 
     assert np.allclose(lapth, -k**2 * np.sin(k * X[0]))
-
-
-def test_create_grid_size():
-    L = 10.0
-    N = 15
-    assert np.shape(create_grid(N, L)) == (2, N, N)
-
-
-def test_xendpoint_of_grid():
-    # test for ij indexing of grid
-    L = 10.0
-    N = 15
-    grid = create_grid(N, L)
-    assert math.isclose(grid[0, -1, 0], L - L / N)
-
-
-def test_yendpoint_of_grid():
-    L = 10.0
-    N = 15
-    grid = create_grid(N, L)
-    assert math.isclose(grid[1, 0, -1], L - L / N)
 
 
 def test_integral_of_sinkx():

### 2018-02-28 tools.py

@@ -15,19 +15,6 @@ def N_boyd(M):
     return int(2**np.ceil(np.log2(4 * (M - 1) + 6)))
 
 
-def create_grid(N, L):
-    return np.mgrid[:N, :N].astype(float) * (L / N)
-
-
-def dt_cfl(N, L, kappa, U):
-    if kappa == 0:
-        dt = L / (N * U)
-    else:
-        dt = min(L / (N * U), L**2 / (N**2 * kappa))
-
-    return dt
-
-
 class ScalarTool(object):
     """
     Description:

### 2018-02-28 lit.py
added convergence reporting

@@ -20,15 +20,17 @@ class sol(object):
         self.hist_th_hm1 = []
         self.hist_th_l2 = []
         self.hist_th_h1 = []
-        self.hist_time = []
+        self.hist_th_time = []
         self.hist_th = []
+
         self.hist_u = []
+        self.hist_u_time = []
         self.hist_u_h1 = []
         self.hist_u_l2 = []
 
 
 def sim(N=128, M=1000, T=1.0, L=1.0, gamma=1.0, U=1.0, Pe=1024, T_kick=0.01,
-        save_every=10, pickle_file=None, plot=False, constraint='enstrophy'):
+        save_th_every=10, save_u_every=10, pickle_file=None, plot=False, constraint='enstrophy'):
 
     def f(th, u):
         return -1.0 * np.sum(vt.dealias(u) * st.grad(st.dealias(th)), 0) + kappa * st.lap(st.dealias(th))
@@ -97,15 +99,16 @@ def sim(N=128, M=1000, T=1.0, L=1.0, gamma=1.0, U=1.0, Pe=1024, T_kick=0.01,
         th = th + dt_kick * (1.0 / 6.0) * (k1 + 2.0 * k2 + 2.0 * k3 + k4)
 
     time = 0.0
-    hist_time = [time]
 
     hist_th = [th]
+    hist_th_time = [time]
     hist_th_hm1 = [st.hm1norm(th)]
     hist_th_l2 = [st.l2norm(th)]
     hist_th_h1 = [st.h1norm(th)]
 
     u = u_lit(th)
     hist_u = [u]
+    hist_u_time = [time]
     hist_u_h1 = [vt.h1norm(u)]
     hist_u_l2 = [vt.l2norm(u)]
     if plot:
@@ -124,18 +127,14 @@ def sim(N=128, M=1000, T=1.0, L=1.0, gamma=1.0, U=1.0, Pe=1024, T_kick=0.01,
         th = th + dt * (1.0 / 6.0) * (k1 + 2.0 * k2 + 2.0 * k3 + k4)
         time += dt
 
-        if np.mod(i, save_every) == 0 or i == total_steps - 1:
-            hist_time.append(time)
+        if np.mod(i, save_th_every) == 0 or i == total_steps - 1:
 
             hist_th.append(th)
+            hist_th_time.append(time)
             hist_th_hm1.append(st.hm1norm(th))
             hist_th_l2.append(st.l2norm(th))
[…]

### 2018-02-28 test/test_lit.py

@@ -6,27 +6,36 @@ import math
 
 def test_fourth_order_convergence_of_entrophy_constained_lit_simulation():
     s = []
-    ss = []
     N = 256
     L = 1.0
     M_list = [1, 2, 4]
     T = 0.01
     Pe = 512
 
-    dt_list = []
     for M in M_list:
         s.append(lit.sim(N=N, M=M, T=T, L=L, save_every=1,
                          T_kick=0.01, Pe=Pe, plot=False))
-        dt_list.append(T / M)
-    error_list = []
     st = tools.ScalarTool(N, L)
-    for i in range(len(M_list) - 1):
-        error_list.append(st.l2norm(s[i].hist_th[-1] - s[2].hist_th[-1]))
+    R = st.l2norm(s[0].hist_th[-1] - s[1].hist_th[-1]) / \
+        st.l2norm(s[1].hist_th[-1] - s[2].hist_th[-1])
+    p = np.log(R) / np.log(2)
+    print('p = ', p)
+    assert abs(p - 4) < 0.5
 
-    error_array = np.array(error_list)
-    dt_array = np.array(dt_list)
-    #print(st.l2norm(s[-3].hist_th[-1] - s[-2].hist_th[-1]))
-    #print(st.l2norm(s[-2].hist_th[-1] - s[-1].hist_th[-1]))
+
+def test_fourth_order_convergence_of_energy_constained_lit_simulation():
+    s = []
+    N = 256
+    L = 1.0
+    M_list = [1, 2, 4]
+    T = 0.001
+    Pe = 512
+    U = 1.0
+
+    for M in M_list:
+        s.append(lit.sim(N=N, M=M, U=U, T=T, L=L, save_every=1,
+                         T_kick=0.01, Pe=Pe, plot=False, constraint="energy"))
+    st = tools.ScalarTool(N, L)
     R = st.l2norm(s[0].hist_th[-1] - s[1].hist_th[-1]) / \
         st.l2norm(s[1].hist_th[-1] - s[2].hist_th[-1])
     p = np.log(R) / np.log(2)

### 2018-02-28 lit.py
removed convergence reporting

@@ -315,33 +315,3 @@ if __name__ == "__main__":
         plt.figure()
         plot_norms(solution.hist_time, solution.hist_th, N, L)
         plt.savefig(output_folder + 'plot_norms-pe=' + str(Pe) + '.png')
-
-    # # Test convergence
-    # f = open('convergence-report-pe=' + str(Pe) + '-M=' + str(M) + '.txt', 'w')
-    # s = []
-    # for M in M_list:
-    #     pickle_file = "output-pe=" + str(Pe) + "-M=" + str(M) + \
-    #         "/pe=" + str(Pe) + "-M=" + str(M) + ".pkl"
-    #
-    #     with open(pickle_file, 'rb') as f:
-    #         s.append(pickle.load(f, encoding='latin1'))
-    #
-    # dt_list = [item.T / item.M for item in s]
-    # st = tools.ScalarTool(N, L)
-    # low2med_res_error = st.l2norm(s[0].hist_th[-1] - s[1].hist_th[-1])
-    # med2high_res_error = st.l2norm(s[1].hist_th[-1] - s[2].hist_th[-1])
-    #
-    # for i, dt in enumerate(dt_list):
-    #     f.write('Simulation #' + str(i) + ': dt = ' + str(dt) + ' \n')
-    #     f.write('Simulation #' + str(i) +
-    #             ': Number of time steps = ' + str(M_list[i]) + ' \n')
-    #
-    # f.write('Absolute l2norm error difference between low and med res solutions: ' +
-    #         str(low2med_res_error) + '\n')
-    # f.write('Absolute l2norm error difference between med and high res solutions: ' +
-    #         str(med2high_res_error) + '\n')
-    # R = low2med_res_error / med2high_res_error
-    # p = np.log(R) / np.log(2)
-    # f.write(
-    #     'Verify 4-th order convergence of RK4 method: measured p =  ' + str(p) + ' \n')
-    # f.close()

### 2018-02-28 convergence_check.py
added convergence check script

@@ -1,0 +1,36 @@
+import tools
+import numpy as np
+import copy
+import time
+import os
+import pickle
+import pprint
+from lit import *
+
+M_list = [4096, 8192, 16384]
+Pe = 512.0
+s = []
+for M in M_list:
+    pickle_file = "output-pe=" + str(Pe) + "-M=" + str(M) + \
+    "/pe=" + str(Pe) + "-M=" + str(M) + ".pkl"
+
+    with open(pickle_file, 'rb') as f:
+        s.append(pickle.load(f, encoding='latin1'))
+
+
+N = s[0].N
+L = s[0].L
+dt_list = [item.T / item.M for item in s]
+error_list = []
+st = tools.ScalarTool(N, L)
+for i in range(len(M_list) - 1):
+    error_list.append(st.l2norm(s[i].hist_th[-1] - s[-1].hist_th[-1]))
+
+error_array = np.array(error_list)
+dt_array = np.array(dt_list)
+print(st.l2norm(s[-3].hist_th[-1] - s[-2].hist_th[-1]))
+print(st.l2norm(s[-2].hist_th[-1] - s[-1].hist_th[-1]))
+R = st.l2norm(s[-3].hist_th[-1] - s[-2].hist_th[-1]) / \
+    st.l2norm(s[-2].hist_th[-1] - s[-1].hist_th[-1])
+p = np.log(R) / np.log(2)
+print('p = ', p)

### 2018-02-28 lit.py

@@ -299,11 +299,14 @@ if __name__ == "__main__":
         os.system('mkdir ' + output_folder)
         pickle_file = output_folder + "pe=" + str(Pe) + "-M=" + str(M) + ".pkl"
 
-        save_every = int(round(M / 65))
-        solution = sim(N=N, M=M, T=T, L=L, U=U, gamma=gamma, Pe=Pe, constraint=constraint,
-                       save_every=save_every, pickle_file=pickle_file, plot=False)
+        save_th_every = int(round(M / 100))
+        save_u_every = int(round(M / 5))
 
-        movie(solution.hist_time, solution.hist_th,
+        solution = sim(N=N, M=M, T=T, L=L, U=U, gamma=gamma, Pe=Pe, constraint=constraint,
+                       save_th_every=save_th_every, save_u_every=save_u_every,
+                       pickle_file=pickle_file, plot=False)
+
+        movie(solution.hist_th_time, solution.hist_th,
               N, L, output_path=output_folder)
 
         plt.figure()
@@ -313,5 +316,5 @@ if __name__ == "__main__":
         plt.savefig(output_folder + 'plot_final_frame-pe=' + str(Pe) + '.png')
 
         plt.figure()
-        plot_norms(solution.hist_time, solution.hist_th, N, L)
+        plot_norms(solution.hist_th_time, solution.hist_th, N, L)
         plt.savefig(output_folder + 'plot_norms-pe=' + str(Pe) + '.png')

### 2018-02-28 test/test_lit.py

@@ -13,7 +13,7 @@ def test_fourth_order_convergence_of_entrophy_constained_lit_simulation():
     Pe = 512
 
     for M in M_list:
-        s.append(lit.sim(N=N, M=M, T=T, L=L, save_every=1,
+        s.append(lit.sim(N=N, M=M, T=T, L=L, save_th_every=1,
                          T_kick=0.01, Pe=Pe, plot=False))
     st = tools.ScalarTool(N, L)
     R = st.l2norm(s[0].hist_th[-1] - s[1].hist_th[-1]) / \
@@ -33,7 +33,7 @@ def test_fourth_order_convergence_of_energy_constained_lit_simulation():
     U = 1.0
 
     for M in M_list:
-        s.append(lit.sim(N=N, M=M, U=U, T=T, L=L, save_every=1,
+        s.append(lit.sim(N=N, M=M, U=U, T=T, L=L, save_th_every=1,
                          T_kick=0.01, Pe=Pe, plot=False, constraint="energy"))
     st = tools.ScalarTool(N, L)
     R = st.l2norm(s[0].hist_th[-1] - s[1].hist_th[-1]) / \

### 2018-02-28 lit.py
updated ntoebooks

@@ -253,12 +253,12 @@ if __name__ == "__main__":
 
     L = 1.0
     kappa = 1.0 / Pe
-    constraint = "energy"
+    constraint = "enstrophy"
     U = 1.0
-    T = 0.01
+    #T = 1.0
 
     gamma = 1.0
-    #T = 13.0
+    T = 13.0
 
     if constraint == "enstrophy":
         if Pe == np.inf:

### 2018-03-01 test/test_tools.py
added test for dealias and invlap of scalar

@@ -4,6 +4,77 @@ import math
 from tools import N_boyd
 
 
+def test_dealias_of_sinkx_where_k_is_above_two_thirds_dealias_boundary_is_zero():
+    L = 2.0 * np.pi
+    N = 128
+    st = ScalarTool(N, L)
+
+    kabove = np.ceil(st.kmax_dealias) + 1
+    th = np.sin(2. * np.pi / L * kabove * st.X[0])
+    z = np.zeros(th.shape)
+
+    assert np.allclose(st.dealias(th), z)
+
+
+def test_dealias_of_sinkx_where_k_is_above_two_thirds_dealias_boundary_is_zero_y_direction():
+    L = 2.0 * np.pi
+    N = 128
+    st = ScalarTool(N, L)
+
+    kabove = np.ceil(st.kmax_dealias) + 1
+    th = np.sin(2. * np.pi / L * kabove * st.X[1])
+    z = np.zeros(th.shape)
+
+    assert np.allclose(st.dealias(th), z)
+
+
+def test_dealias_of_sinkx_where_k_is_below_two_thirds_dealias_boundary_is_zero():
+    L = 2.0 * np.pi
+    N = 128
+    st = ScalarTool(N, L)
+
+    k = np.floor(st.kmax_dealias) - 1
+    th = np.sin(2. * np.pi / L * k * st.X[0])
+    z = np.zeros(th.shape)
+
+    assert not np.allclose(st.dealias(th), z)
+
+
+def test_dealias_of_sinkx_where_k_is_below_two_thirds_dealias_boundary_is_zero_y_direction():
+    L = 2.0 * np.pi
+    N = 128
+    st = ScalarTool(N, L)
+
+    k = np.floor(st.kmax_dealias) - 1
+    th = np.sin(2. * np.pi / L * k * st.X[1])
+    z = np.zeros(th.shape)
+
+    assert not np.allclose(st.dealias(th), z)
+
+
+def test_lap_invlap_of_th_is_th_minus_mean_value():
+    L = 2.0 * np.pi
+    N = 128
+    st = ScalarTool(N, L)
+
+    th = np.random.random((N, N))
+
+    assert np.allclose(st.lap(st.invlap(th)), st.subtract_mean(th))
+
+
+def test_spatial_integral_of_neg_invlap_th_time_th_equals_hm1_norm_sq():
+    L = 2.0 * np.pi
+    N = 128
+    st = ScalarTool(N, L)
+
[…]

### 2018-03-01 tools.py

@@ -73,6 +73,12 @@ class ScalarTool(object):
         scalar_hat = self.fft(scalar)
         return self.ifft((-1.0) * self.K2 * (2 * np.pi / self.L)**2.0 * scalar_hat)
 
+    def invlap(self, scalar):
+        self.scalar_input_test(scalar)
+        scalar_hat = self.fft(scalar)
+        return np.real(self.ifft(-1.0 * (2.0 * np.pi / self.L)**(-2.0) *
+                                 self.oneoverK2 * self.mean_zero_array * scalar_hat))
+
     def grad_invlap(self, scalar):
         self.scalar_input_test(scalar)
         scalar_hat = self.fft(scalar)

### 2018-03-01 test/test_tools.py
added test for dealias and invlap of scalar

@@ -7,6 +7,20 @@ from tools import N_boyd
 def test_dealias_of_sinkx_where_k_is_above_two_thirds_dealias_boundary_is_zero():
     L = 2.0 * np.pi
     N = 128
+    vt = ScalarTool(N, L)
+
+    kabove = np.ceil(st.kmax_dealias) + 1
+    v = np.zeros((2, N, N))
+    v[0] = np.sin(2. * np.pi / L * kabove * st.X[0])
+    v[0] = np.sin(2. * np.pi / L * kabove * st.X[1])
+    z = np.zeros(v.shape)
+
+    assert np.allclose(st.dealias(th), z)
+
+
+def test_dealias_of_sinkx_where_k_is_above_two_thirds_dealias_boundary_is_zero():
+    L = 2.0 * np.pi
+    N = 128
     st = ScalarTool(N, L)
 
     kabove = np.ceil(st.kmax_dealias) + 1

### 2018-03-10 convergence_check.py
added git.py and git notebook

@@ -1,36 +1,0 @@
-import tools
-import numpy as np
-import copy
-import time
-import os
-import pickle
-import pprint
-from lit import *
-
-M_list = [4096, 8192, 16384]
-Pe = 512.0
-s = []
-for M in M_list:
-    pickle_file = "output-pe=" + str(Pe) + "-M=" + str(M) + \
-    "/pe=" + str(Pe) + "-M=" + str(M) + ".pkl"
-
-    with open(pickle_file, 'rb') as f:
-        s.append(pickle.load(f, encoding='latin1'))
-
-
-N = s[0].N
-L = s[0].L
-dt_list = [item.T / item.M for item in s]
-error_list = []
-st = tools.ScalarTool(N, L)
-for i in range(len(M_list) - 1):
-    error_list.append(st.l2norm(s[i].hist_th[-1] - s[-1].hist_th[-1]))
-
-error_array = np.array(error_list)
-dt_array = np.array(dt_list)
-print(st.l2norm(s[-3].hist_th[-1] - s[-2].hist_th[-1]))
-print(st.l2norm(s[-2].hist_th[-1] - s[-1].hist_th[-1]))
-R = st.l2norm(s[-3].hist_th[-1] - s[-2].hist_th[-1]) / \
-    st.l2norm(s[-2].hist_th[-1] - s[-1].hist_th[-1])
-p = np.log(R) / np.log(2)
-print('p = ', p)

### 2018-03-10 git.py

@@ -1,0 +1,209 @@
+import tools
+import numpy as np
+import matplotlib.pyplot as plt
+import copy
+import time
+import os
+import pickle
+import pprint
+import lit
+
+
+def increase_res(scalar, N_grid):
+    st_grid = tools.ScalarTool(N_grid, L)
+    th_hat = np.fft.rfft(scalar, axis=1)
+
+    th_hat1 = np.zeros((N, N_grid // 2 + 1), dtype=ctype)
+    th_hat1[:, 0:(N // 2 + 1)] = N_grid / N * th_hat
+
+    th_hat2 = np.fft.fft(th_hat1, axis=0)
+
+    th_hat3 = np.zeros((N_grid, N_grid // 2 + 1), dtype=ctype)
+    th_hat3[0:N // 2, :] = N_grid / N * th_hat2[0:N // 2, :]
+    th_hat3[(N_grid - N // 2):, :] = N_grid / N * th_hat2[N // 2:, :]
+    th_new = st_grid.ifft(th_hat3)
+    return th_new
+
+
+def f(th, u):
+    th_d = st.dealias(th)
+    return st.dealias(-1.0 * np.sum(vt.dealias(u) * st.grad(th_d), 0)
+                      + kappa * st.lap(th_d))
+
+
+def g(phi, u):
+    phi_d = st.dealias(phi)
+    return st.dealias(-1.0 * np.sum(vt.dealias(u) * st.grad(phi_d), 0)
+                      - kappa * st.lap(phi_d))
+
+
+def line_search(u, d, eta_array):
+    J_array = np.zeros(np.shape(eta_array))
+    for i, eta in enumerate(eta_array):
+        J_array[i] = get_obj(normalize(div_free_proj(dealias(u + eta * d))))
+    plt.figure()
+    plt.loglog(eta_array, J_array)
+    plt.show()
+    return eta_array[np.argmin(J_array)]
+
+
+def get_obj(u):
+    # Forward integration
+    th = integrate_forward(u, th0)
+    return 0.5 * st.hm1norm(th[M - 1])**2
+
+
+def integrate_forward(u, th0):
+    th = np.zeros((M, N, N))
+    th[0] = th0
+    for i in range(M - 1):
+        # Heun's method
+        k1 = f(th[i], u[i])
+        th_euler = th[i] + dt * k1
+        th[i + 1] = th[i] + 0.5 * dt * (k1 + f(th_euler, u[i + 1]))
+    return th
+
+
+def integrate_backward(u, phiT):
[…]

### 2018-03-10 lit.py

@@ -34,13 +34,16 @@ def sim(N=128, M=1000, T=1.0, L=1.0, gamma=1.0, U=1.0, Pe=1024,
         plot=False, constraint='enstrophy'):
 
     def f(th, u):
-        return -1.0 * np.sum(vt.dealias(u) * st.grad(st.dealias(th)), 0) + kappa * st.lap(st.dealias(th))
+        th_d = st.dealias(th)
+        return st.dealias(-1.0 * np.sum(vt.dealias(u) * st.grad(th_d), 0)
+                          + kappa * st.lap(th_d))
 
     def f_lit(th):
         return f(th, u_lit(th))
 
     def u_lit_enstrophy(th):
-        u_lit = st.dealias(th) * vt.dealias(st.grad_invlap(th))
+        th_d = st.dealias(th)
+        u_lit = th_d * st.grad_invlap(th_d)
         u_lit = - vt.invlap(vt.div_free_proj(u_lit))
         u_lit = gamma * L * u_lit / st.l2norm(vt.curl(u_lit))
         return u_lit
@@ -120,7 +123,8 @@ def sim(N=128, M=1000, T=1.0, L=1.0, gamma=1.0, U=1.0, Pe=1024,
 
     u0 = copy.copy(u)
     assert total_steps == M
-    for i in range(total_steps):
+
+    for i in range(1, total_steps + 1):
         k1 = f_lit(th)
         k2 = f_lit(th + 0.5 * dt * k1)
         k3 = f_lit(th + 0.5 * dt * k2)
@@ -128,7 +132,7 @@ def sim(N=128, M=1000, T=1.0, L=1.0, gamma=1.0, U=1.0, Pe=1024,
         th = th + dt * (1.0 / 6.0) * (k1 + 2.0 * k2 + 2.0 * k3 + k4)
         time += dt
 
-        if np.mod(i, save_th_every) == 0 or i == total_steps - 1:
+        if np.mod(i, save_th_every) == 0:
 
             hist_th.append(th)
             hist_th_time.append(time)
@@ -145,7 +149,7 @@ def sim(N=128, M=1000, T=1.0, L=1.0, gamma=1.0, U=1.0, Pe=1024,
                 vt.plot(u)
                 plt.show()
 
-        if np.mod(i, save_u_every) == 0 or i == total_steps - 1:
+        if np.mod(i, save_u_every) == 0:
             u = u_lit(th)
             hist_u.append(u)
[…]

### 2018-03-10 test/test_tools.py

@@ -345,6 +345,15 @@ def test_that_l2norm_of_vector_with_siny_for_xcomponent_equals_sqrt_of_half_of_L
     assert np.isclose(vt.l2norm(u), (0.5 * L ** 2)**0.5)
 
 
+def test_that_is_incompressible_projection():
+    N = 128
+    L = 2 * np.pi
+    vt = VectorTool(N, L)
+    u = np.random.random((2, N, N))
+    u = vt.dealias(vt.div_free_proj(u))
+    assert vt.is_incompressible(u)
+
+
 def test_that_is_incompressible_function_returns_true_for_cellular_flow():
     N = 128
     L = 2 * np.pi
@@ -354,6 +363,7 @@ def test_that_is_incompressible_function_returns_true_for_cellular_flow():
         np.sin((2.0 * np.pi / L) * vt.X[1])
     u[1] = np.cos((2.0 * np.pi / L) * vt.X[0]) * \
         np.cos((2.0 * np.pi / L) * vt.X[1])
+
     assert vt.is_incompressible(u)
 
 

### 2018-03-11 flux_pbs.sh
updated main function of lit.py script

@@ -1,52 +1,0 @@
-# !/bin/sh
-#### PBS preamble
-
-#PBS -N lit_enstrophy
-
-# Your email:
-#PBS -M  cmiless@umich.edu
-#PBS -m a
-#PBS -V
-
-# Change the number of cores (ppn=1), amount of memory, and walltime:
-#PBS -l procs=1,pmem=8000mb,walltime=24:00:00
-
-# Change "example_flux" to the name of your Flux allocation:
-#PBS -A lsa_flux
-#PBS -q flux
-#PBS -l qos=flux
-
-# End PBS preamble
-
-
-#  Show list of CPUs you ran on, if you're running under PBS
-if [ -n "$PBS_NODEFILE" ]; then cat $PBS_NODEFILE; fi
-
-#  Change to the directory you submitted from
-if [ -n "$PBS_O_WORKDIR" ]; then cd $PBS_O_WORKDIR; fi
-
-#  Put your job commands here:
-
-description=("sim_number = $PBS_ARRAYID")
-echo $description
-
-Pe_list=(128.0 256.0 512.0 1024.0 2048.0 4096.0 8192.0 16384.0)
-params=()
-count=1
-
-for Pe in ${Pe_list[@]}
-do
-      if [ "$count" = "$PBS_ARRAYID" ]
-      then
-         description=("Pe=$Pe")
-         arguments=("$Pe ")
-         python lit.py $arguments -> log-$description.txt
-      fi
-      count=`expr $count + 1`
-done
-
-if [ "$PBS_ARRAYID" = 9 ]
-then
-    description=("Pe=inf")
-   python lit.py "inf" -> log-$description.txt
-fi

### 2018-03-11 lit.py

@@ -251,21 +251,39 @@ def plot_norms(time, scalar_hist, N, L, high_quality=False, graph='log'):
 
 if __name__ == "__main__":
 
-    arg = sys.argv[1]
-    if arg == 'inf':
-        Pe = np.inf
-    else:
-        Pe = float(arg)
+    # PLEASE READ BEFORE RUNNING ON FLUX SERVER!
+    #
+    # Transfer this script lit.py , tools.py, and flux_pbs_enstrophy.sh (or flux_pbs_energy.sh)
+    # to flux.
+    #
+    # This is specifically built to interface with the pbs scrpts to work on
+    # univeristy of Michigan's flux server. Make sure to use the following command
+    # `qsub -t 1-27 flux_pbs_enstrophy.sh' where 27 is chosen since it is the (Length
+    # of Pe_list[=9]) times (number of trials per Peclet[=3]). Similarly
+    # for the energy constraint run `qsub -t 1-33 flux_pbs_energy.sh'
 
-    L = 1.0
+    sim_num = int(sys.argv[1])
+    constraint = str(sys.argv[2])
+    T = float(sys.argv[3])
+
+    print(sim_num)
+
+    if constraint == "enstrophy":
+        Pe_list = [128.0, 256.0, 512.0, 1024.0,
+                   2048.0, 4096.0, 8192.0, 16384.0, np.inf]
+    elif constraint == "energy":
+        Pe_list = [1.0, 2.0, 4.0, 8.0, 16.0, 32.0,
+                   64.0, 128.0, 256.0, 512.0, np.inf]
+
+    Pe = Pe_list[(sim_num - 1) // 3]
     kappa = 1.0 / Pe
-    constraint = "enstrophy"
+
+    # THESE PARAMETERS SHOULD NOT BE CHANGE!
+    L = 1.0
     U = 1.0
-    # T = 1.0
-
     gamma = 1.0
-    T = 0.1
 
+    # Determine N and dt_cfl
     if constraint == "enstrophy":
         if Pe == np.inf:
             N = 512
@@ -296,33 +314,37 @@ if __name__ == "__main__":
     print('N = ', N)
     print('dt CFL = ', dt_cfl)
 
+    # Determine M_list given dt_cfl
     # Run 3 different simulations with 2 and 4 times as many time num_steps
     # This will be used to calculate convergence metrics.
     M0 = round(T / dt_cfl)  # approx number of time steps according to CFL
[…]
